### 2021-03-10 publications/The_tool_intro/paper.tex
init tool paper

\documentclass[sigconf]{acmart}

\usepackage{comment}

\AtBeginDocument{%
	\providecommand\BibTeX{{%
			\normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
%%\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
%%  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}
%%\acmPrice{15.00}
%%\acmISBN{978-1-4503-XXXX-X/18/06}

\begin{document}

	\title{TODO}

	\author{}
	\email{}
	\orcid{}
	\author{}
	\authornotemark[]
	\email{}
	\affiliation{%
		\institution{}
		\streetaddress{}
		\city{}
		\state{}
		\country{}
		\postcode{}
	}

	\begin{abstract}
		TODO
	\end{abstract}

	%%
	%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
	%% Please copy and paste the code instead of the example below.
	%% TODO

	\keywords{TODO}

	\maketitle

	\section{Introduction}

	\section{Motivation}

	\section{Evaluation}

	\section{Related Work}

	\section{Conclusion}

	\section{Future Work}

\end{document}
\endinput

### 2021-03-10 publications/The_tool_intro/paper.tex
plan
tool intro : P4 example

@@
 
-\usepackage{comment}
+\usepackage{comment, graphicx, algorithm, algorithmic, listings}
 
@@
 	\section{Introduction}
+	% P4 (max 1-1.5 hasáb) - példa (később használandó a többihez) - Máté
+
+\begin{table*}
+\begin{tabular}{|p{8.4cm}|p{8.4cm}|}
+\hline
+\begin{lstlisting}[basicstyle=\scriptsize]
+header ethernet_t {
+    macAddr_t dstAddr;
+    macAddr_t srcAddr;
+    bit<16>   etherType; }
+
+header ipv4_t {
+    bit<8>    ttl;
+    ip4Addr_t srcAddr;
+    ip4Addr_t dstAddr;... }
+
+struct headers {
+    ethernet_t   ethernet;
+    ipv4_t       ipv4; }
+
+parser MyParser(...) {
+    state start { transition parse_ethernet; }
+    state parse_ethernet {
+        packet.extract(hdr.ethernet);
+        transition select(hdr.ethernet.etherType) {
+            TYPE_IPV4: parse_ipv4;
+            default: accept; } }
+    state parse_ipv4 {
+        packet.extract(hdr.ipv4);
+        transition accept; } }
+\end{lstlisting}
+&
+\begin{lstlisting}[basicstyle=\scriptsize]
+control MyIngress(...) {
+   apply {
+        if (hdr.ipv4.isValid()) {
+            ipv4_lpm.apply(); }
+   }         
+   action drop() {
+        mark_to_drop(standard_metadata);
+    }    
+    action ipv4_forward(macAddr_t dstAddr, egressSpec_t port) {
+        standard_metadata.egress_spec = port;
+        hdr.ethernet.srcAddr = hdr.ethernet.dstAddr;
+        hdr.ethernet.dstAddr = dstAddr;
+        hdr.ipv4.ttl = hdr.ipv4.ttl - 1;
+    }    
+    table ipv4_lpm {
+        key = {  hdr.ipv4.dstAddr: lpm;  }
+        actions = {
+            ipv4_forward;
+            drop;
+            NoAction;}
+        ... }   
+}
+control MyDeparser(packet_out packet, in headers hdr) {
+    apply {
+        packet.emit(hdr.ethernet);
+        packet.emit(hdr.ipv4);}
+}
+\end{lstlisting}\\
+\hline
+\end{tabular}
+\caption{P4 example}
+  \label{code:P4}
+\end{table*}
+
+	\section{Related Work}
+	% kb 1.5 hasáb
+	% felhasznált eszközök  - 
+	% egyéb toolok - Vera,  - Gabi
+	% Akár gremlin/gráf alapú dolgok, ami nem p4 (akár refactorerl) - mindenki
 
 	\section{Motivation}
+	% max 1 hasáb - lehet intorba megy - Máté
+	% p4-re vannak elemzések kéne fejlesztés segítő eszköz
+	% ehhez egységes keretrendszer - vannak már ilyesmik related workben
+
+	\section{Analysis framework}
+	\subsection{Representation - Architecture} % 4 hasáb - Dániel
+	% belső gráf, a koncepció
+	% elemzések
+	% app megvalósítás
+
+	\subsection{Experts} % 1 hasáb - Dániel
+	% kisebb gráf ábra
+	\subsection{Testing} % 1 hasáb - Gabi
+	% külön modul
+	% elvi részei jelenlenek meg
+	% ilyen olyan teszt, messziről melyik hogy
 
@@
 
-	\section{Related Work}
+	% scalability measurements  talán 1 hasáb
+	% esetleg 1-2 plre hogy futott le - sor alapján? mini mérés
 
-	\section{Conclusion}
+	% indítási információk - mindegyiknél /visualisation-nél
+	% egyedi elemzések mérése
+	\subsection{Visualization} % 0.5 hasáb
+	\subsection{Verification} % 1 hasáb - Gabi
+	\subsection{Cost analysis} % 1 hasáb - Dániel
 
-	\section{Future Work}
+	\section{Conclusion and Future Work} % 1 hasáb - Máté
 

### 2021-03-10 publications/The_tool_intro/paper.tex
tool_intro:P4 example

@@
 \begin{table*}
-\begin{tabular}{|p{8.4cm}|p{8.4cm}|}
+\begin{tabular}{|p{3.3cm}|p{5.9cm}|p{7.7cm}|}
 \hline
@@
 
+\end{lstlisting}
+&
+\begin{lstlisting}[basicstyle=\scriptsize]
 parser MyParser(...) {
@@
     transition accept; } }
-\end{lstlisting}
-&
-\begin{lstlisting}[basicstyle=\scriptsize]
 control MyIngress(...) {
@@
   }    
+\end{lstlisting}
+&
+\begin{lstlisting}[basicstyle=\scriptsize]
   action ipv4_forward(macAddr_t dstAddr, egressSpec_t port) {

### 2021-03-11 publications/The_tool_intro/paper.tex
pub: added 2 architecture figures

@@
 	\section{Analysis framework}
+
 	\subsection{Representation - Architecture} % 4 hasáb - Dániel
@@
 
+  \begin{figure}
+    \includegraphics[width=0.18\textwidth]{figures/arch-top.pdf}
+    \caption{TODO}\label{fig:arch-top}
+  \end{figure}
+
+  \begin{itemize}
+    \item Figure \ref{fig:arch-top} 
+    \item User extracts information (including metrics, object codes, verified properties) from the code using applications (corresp.
+backends).
+Applications provide services by utilizing the code knowledge stored in the knowledge graph by the analysers of the infrastructure layer (corresp.
+frontend).
+The collaboration of the application and the analysers is orchestrated by a controller module.
+  \end{itemize}
+
 	\subsection{Experts} % 1 hasáb - Dániel
 	% kisebb gráf ábra
+
+  \begin{figure}
+    \includegraphics[width=0.3\textwidth]{figures/arch-deps.pdf}
+    \caption{TODO}\label{fig:arch-deps}
+  \end{figure}
+
+  \begin{itemize}
+    \item Figure \ref{fig:arch-deps} 
+    \item More granular.
+    \item Analysers depend on each other. Applications only depend on one or more analysers.
+    \item Controller manages dependencies.
+  \end{itemize}
+
 	\subsection{Testing} % 1 hasáb - Gabi

### 2021-03-12 publications/The_tool_intro/paper.tex
tool_intro:P4 example

@@
 \usepackage{comment, graphicx, algorithm, algorithmic, listings}
+
+\lstdefinelanguage{P4}{
+  showlines=true,
+  morecomment=[f]{//},
+  keepspaces=true,
+  basicstyle=\scriptsize\ttfamily,
+  emphstyle=\itshape,
+  emph={},
+  commentstyle=\color{red},
+  keywordstyle=\color{blue},
+  morekeywords={typedef, header, extern, struct, parser, state, transition, in, out, inout, select, default, control, action, table, apply, if, switch}
+}
 
@@
 	% P4 (max 1-1.5 hasáb) - példa (később használandó a többihez) - Máté
-
-\begin{table*}
-\begin{tabular}{|p{3.3cm}|p{5.9cm}|p{7.7cm}|}
-\hline
-\begin{lstlisting}[basicstyle=\scriptsize]
-header ethernet_t {
-  macAddr_t dstAddr;
-  macAddr_t srcAddr;
-  bit<16>   etherType; }
-
-header ipv4_t {
-  bit<8>    ttl;
-  ip4Addr_t srcAddr;
-  ip4Addr_t dstAddr;... }
-
-struct headers {
-  ethernet_t   ethernet;
-  ipv4_t       ipv4; }
-
-\end{lstlisting}
-&
-\begin{lstlisting}[basicstyle=\scriptsize]
-parser MyParser(...) {
-  state start { transition parse_ethernet; }
-  state parse_ethernet {
-    packet.extract(hdr.ethernet);
-    transition select(hdr.ethernet.etherType) {
-      TYPE_IPV4: parse_ipv4;
-      default: accept; } }
-  state parse_ipv4 {
-    packet.extract(hdr.ipv4);
-    transition accept; } }
-control MyIngress(...) {
-  apply {
-    if (hdr.ipv4.isValid()) {
-           ipv4_lpm.apply(); }
-  }         
-  action drop() {
-    mark_to_drop(standard_metadata);
-  }    
-\end{lstlisting}
-&
-\begin{lstlisting}[basicstyle=\scriptsize]
-  action ipv4_forward(macAddr_t dstAddr, egressSpec_t port) {
-    standard_metadata.egress_spec = port;
-    hdr.ethernet.srcAddr = hdr.ethernet.dstAddr;
-    hdr.ethernet.dstAddr = dstAddr;
-    hdr.ipv4.ttl = hdr.ipv4.ttl - 1;
-  }    
-  table ipv4_lpm {
-    key = {  hdr.ipv4.dstAddr: lpm;  }
-    actions = {
-      ipv4_forward;
-      drop;
-      NoAction;}
-    ... }   
-}
-control MyDeparser(packet_out packet, in headers hdr) {
-  apply {
-    packet.emit(hdr.ethernet);
-    packet.emit(hdr.ipv4);}
-}
-\end{lstlisting}\\
-\hline
-\end{tabular}
-\caption{P4 example}
-  \label{code:P4}
-\end{table*}
 
@@
 
+\begin{figure*}
+\begin{tabular}{|p{3.3cm}|p{5.9cm}|p{7.7cm}|}
+\hline
+\begin{lstlisting}[language=P4]
+// Definitions
+typedef bit<9>  egSpec_t;
+typedef bit<48> macAddr_t;
+typedef bit<32> ip4Addr_t;
+
+// Headers
+header ethernet_t {
+  macAddr_t dstAddr;
+  macAddr_t srcAddr;
+  bit<16>   etherType; }
+
+header ipv4_t {
+  bit<8>    ttl;
+  ip4Addr_t srcAddr;
+  ip4Addr_t dstAddr;... }
+
+struct headers {
+  ethernet_t   ethernet;
+  ipv4_t       ipv4; }
+
+\end{lstlisting}
+&
+\begin{lstlisting}[language=P4]
+// Parser
+parser MyParser(...) {
+  state start { transition parse_ethernet; }
+  state parse_ethernet {
+    packet.extract(hdr.ethernet);
+    transition select(hdr.ethernet.etherType) {
+      TYPE_IPV4: parse_ipv4;
+      default: accept; } }
+  state parse_ipv4 {
+    packet.extract(hdr.ipv4);
+    transition accept; } }
+
+// Control    
+control MyIngress(...) {
+  apply {
+    if (hdr.ipv4.isValid()) {
+           ipv4_lpm.apply(); }
+  }         
+  action drop() {
+    mark_to_drop(standard_metadata);
+  }    
+\end{lstlisting}
+&
+\begin{lstlisting}[language=P4]
+  action ipv4_forward(macAddr_t dstAddr, egSpec_t port) {
+    standard_metadata.egress_spec = port;
+    hdr.ethernet.srcAddr = hdr.ethernet.dstAddr;
+    hdr.ethernet.dstAddr = dstAddr;
+    hdr.ipv4.ttl = hdr.ipv4.ttl - 1;
+  }    
+  table ipv4_lpm {
+    key = {  hdr.ipv4.dstAddr: lpm;  }
+    actions = {
+      ipv4_forward;
+      drop;
+      NoAction;}
+    ... }   
+}
+
+//Deparser
+control MyDeparser(packet_out packet, in headers hdr) {
+  apply {
+    packet.emit(hdr.ethernet);
+    packet.emit(hdr.ipv4);}
+}
+\end{lstlisting}\\
+\hline
+\end{tabular}
+\caption{P4 example}
+  \label{code:P4}
+\end{figure*}
+
 \end{document}

### 2021-03-15 publications/The_tool_intro/paper.tex
tool_intro: adding a reference
pub: added 2 columns on architecture principles

@@
 	% P4 (max 1-1.5 hasáb) - példa (később használandó a többihez) - Máté
+	P4 \cite{p4paper} is a high level, domain-specific programming language. It is developed mainly for
+describing the data plane layer of packet processing algorithms of different network
+devices (e.g. switches, routers) in a protocol and target independent way.
 
@@
 
+\clearpage
+
 	\section{Analysis framework}
+
+Traditional compilers are designed around passess: the frontend passes parse source code into an intermediate representation (IR), midend passes transforms and adds new information to the IR, and the backend passes create target-specific object code from the IR~\cite{trad-compilers}.
+Modular compilers like P4C improve this design by structuring the passess into a library: backends assemble their own frontends and midends from a catalogue of passes provided by the compiler.
+Moreover, P4C allows getting information from older states of the IR, as each transformation passes return an immutable IR instance.
+Even here, the three-fold separation of frontend-midend-backend have to remain: in order satisfy midend-dependencies, and subsequently, backend-dependencies, the backend must sequentially execute the frontend, the midend, and finally its own passes.
+
+One goal of the experiment we present here is to relax the three-fold structure and allow passes to reuse (depend on) each other's functionally arbitrarily, and without burdening the compiler programmer with manually finding the right sequence in which to execute these dependencies.
 
@@
 
-  \begin{itemize}
-    \item Figure \ref{fig:arch-top} 
-    \item User extracts information (including metrics, object codes, verified properties) from the code using applications (corresp.
-backends).
-Applications provide services by utilizing the code knowledge stored in the knowledge graph by the analysers of the infrastructure layer (corresp.
-frontend).
-The collaboration of the application and the analysers is orchestrated by a controller module.
-  \end{itemize}
+Besides proposing a more relaxed structure of analysis passes, we had three additional goals in sight: support for different applications through uniform APIs, ease of extensibility, and data-driven programming.
 
-	\subsection{Experts} % 1 hasáb - Dániel
-	% kisebb gráf ábra
+By \textit{supporting different applications} (or backends, in compiler parlance), we mean providing a comfortable way to to implement different end-users services, by reusing the same static code analysis operations.
+See Section~\ref{fig:apps} for a few examples of applications built on top of the <NAME>.
+In systems with uniform APIs, programmers have to learn only one paradigm to maintain, extend or otherwise alter the system (e.g.
+in case of P4C, visitors and passes are the main concepts of such a uniform API).
+
+Figure~\ref{fig:arch-top} depicts how the architecture of <NAME> realizes uniform APIs by relying on a graph database. 
+Superficially, applications provide services to the user, by using the services provided by the infrastructurei (see Section~\ref{fig:infra}).
+In reality, both the infrastructure and applications operate on a large shared graph that collects all our knowledge about the program code.
+The graph is also exposed to the user to enable custom features (e.g.
+to attach external loggers, visualizers, and validators).
+The information in the knowledge graph is accessed using graph queries written in Gremlin (see Section \ref{sec:gremlin}).
+The impliciation is that each of users, application developers, and infrastructure developers are using one, uniform data structure, and are accessing it using the same mechanism.
+The seamless collaboration of all these components is managed by the controller component.
 
@@
 
-  \begin{itemize}
-    \item Figure \ref{fig:arch-deps} 
-    \item More granular.
-    \item Analysers depend on each other. Applications only depend on one or more analysers.
-    \item Controller manages dependencies.
-  \end{itemize}
+Our second design goal, \textit{ease of extensibility} is illustrated by Figure~\ref{fig:arch-deps}, that elaborates the application and infrastructure layers. 
+This arrangement was inspired by declarative build systems and the blackboard pattern used in distributed MI.
+
+The infrastructure consists of a set of interdependent analyser componenents (or passes, in compiler parlance): higher-level analysers can only be executed when lower-level analysers already inserted the necessary knowledge into the graph.
+To achieve this, analyser components register their needs and provided services to the controller component, and the controller figures out the topological order in which to initiate the analysers.
+Applications provide a user interface (e.g.
+command line interface) through which their services can be accessed, and similarly to analysers, applications also depend on a subset of the analysers in the infrastructure.
+But unlike analysers, application are expected to only read (never modify) the graph, and consequently, applications have no dependers.
+In this arrangement, the controller guarantees that when the user executes a work-intensive application, only the minimally necessary components will be performed.
+Moreover, when developers introduce new features, this arrangement enables them to think declaratively: instead of thinking about where to insert their feature inside a sequence of operations, they only have to think about their dependencies, i.
+e.
+what kind of analysers could help them.
+
+With this, we arrive to our third design goal, \textit{data-driven programming}.
+Thanks to the uniform graph API and the controller-managed dependecy resolution, programmers are forced to think in terms of data instead of code: they have to look at what code knowledge is in the graph already, figure out what data they want to insert, and possibly find existing analysers that makes writing queries  easier for them.
+The information in the graph is regulated by a well-defined graph schema, and the graph topology is regulated by the well-defined requirements and services of the analysers.
+Moreover, since the graph instance is detached from the code analysis framework, the programmers can access it by external tools for visualizing, monitoring and validating purposes.
+Like this, programmers can almost completely avoid understanding the existing code base, and only have to look at and interact with the data in the graph.
+
+	\subsection{Experts} % 1 hasáb - Dániel
+	% kisebb gráf ábra
 
@@
 
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{tool}
+
 \end{document}

### 2021-03-16 publications/The_tool_intro/paper.tex
tool_intro:short P4 description

@@
 	% P4 (max 1-1.5 hasáb) - példa (később használandó a többihez) - Máté
-	P4 \cite{p4paper} is a high level, domain-specific programming language. It is developed mainly for
+	P4~\cite{p4paper} is a high level, domain-specific programming language. It is developed mainly for
 describing the data plane layer of packet processing algorithms of different network
-devices (e.g. switches, routers) in a protocol and target independent way.
+devices (e.g.
+switches, routers) in a protocol and target independent way.
+Figure~\ref{code:P4} illustrates a P4 program.
+The program first defines the applied header structure, than the parser part describes how the fields of the defined headers will be set from the input bit stream (input packet).
+Controller part can modify values of headers' fields and metadatas by applying lookup tables.
+The dataplane program describes the structure of the tables, the key fields based on that lookups will be executed and the possible results of the lookups, namely the applicable actions.
+However concrete data of the tables (which actions will be executed with wich parameters for which key values) are defined by the controlplane program, therefore it will not appear in P4.
+Finally the deparse part defines how the output bitstream (output packet) will be created from the headers.
 

### 2021-03-16 publications/The_tool_intro/paper.tex
add description of testing

--- 2021-03-15 publications/The_tool_intro/paper.tex
@@
 	\subsection{Testing} % 1 hasáb - Gabi
+	There are two main goals with the testing: to test if the analyzes work well; and because it is a quite new tool, it will go through a lot of changes, therefore the possible spoils of the analyses during changes need to be detected.
+This version of the tool contains unit tests and integration tests to check the functional correctness.
+
+	With the unit tests, our main goal is to check if the analyzes work well.
+Unit tests need to be fast, therefore they work with the smallest part of the analyses ie.
+their functions.
+One function usually define one query of the graph, which insert new edges into it, therefore in these cases, the tests check if the right edges are added to the graph.
+Using actual P4 source, to test these functions, would be too costly, therefore we define the most simple graphs --, which contains only those edges and vertices, which are necessary for the query -- to check the function.
+
+	While unit tests need to be fast, integration tests can be slower, so we can use P4 files as the inputs to test the analyzes.
+When one analysis needs to be tested, it uses the P4 file, and executes every analysis, that it is based on and the tests will check the result of this running.
+The tests are predefined, therefore we use a file to store the information of the tested sources and analysis -- which file tests which analyzes with which test classes.
+
+	There are two approaches to run these tests.
+One of them executes all of the defined tests -- i.e.
+it goes through all of the P4 sources and executes the necessary analyzes and tests the their results -- which is useful to test the whole program and identify regression errors.
+The other focuses only one analysis and it is useful, when someone actually develop that analysis.
+This approach run only those tests which are relevant for the analysis.
+
+	The architecture gives opportunity to insert the test as an application, which depends on all of the tested analyzes, but these are built into the maven.
+(TODO - ide még jöhetne talán részletessebben)
+
+	% külön modul
+	% elvi részei jelenlenek meg
+	% ilyen olyan teszt, messziről melyik hogy
 	% külön modul

### 2021-03-16 publications/The_tool_intro/paper.tex
add description of testing
pub: added 2 columns on compiler

@@
   morekeywords={typedef, header, extern, struct, parser, state, transition, in, out, inout, select, default, control, action, table, apply, if, switch}
+}
+
+\lstdefinelanguage{asm}{
+  showlines=true,
+  morecomment=[l]{//},
+  keepspaces=true,
+  basicstyle=\scriptsize\ttfamily,
+  emphstyle=\itshape,
+  emph={},
+  commentstyle=\color{red},
+  keywordstyle=\color{blue},
+  morekeywords={load, const, invoke, ifeq, pop, add, return, code, data}
 }
@@
 
+  %% p4c is a factory. this tool is a laboratory.
+
 \clearpage
@@
 
-Traditional compilers are designed around passess: the frontend passes parse source code into an intermediate representation (IR), midend passes transforms and adds new information to the IR, and the backend passes create target-specific object code from the IR~\cite{trad-compilers}.
-Modular compilers like P4C improve this design by structuring the passess into a library: backends assemble their own frontends and midends from a catalogue of passes provided by the compiler.
+Traditional compilers are designed around passes: the frontend passes parse source code into an intermediate representation (IR), midend passes transforms and adds new information to the IR, and the backend passes create target-specific object code from the IR~\cite{trad-compilers}.
+Modular compilers like P4C improve this design by structuring the passes into a library: backends assemble their own frontends and midends from a catalogue of passes provided by the compiler.
 Moreover, P4C allows getting information from older states of the IR, as each transformation passes return an immutable IR instance.
@@
 Figure~\ref{fig:arch-top} depicts how the architecture of <NAME> realizes uniform APIs by relying on a graph database. 
-Superficially, applications provide services to the user, by using the services provided by the infrastructurei (see Section~\ref{fig:infra}).
+Superficially, applications provide services to the user, by using the services provided by the infrastructure (see Section~\ref{fig:infra}).
 In reality, both the infrastructure and applications operate on a large shared graph that collects all our knowledge about the program code.
@@
 The information in the knowledge graph is accessed using graph queries written in Gremlin (see Section \ref{sec:gremlin}).
-The impliciation is that each of users, application developers, and infrastructure developers are using one, uniform data structure, and are accessing it using the same mechanism.
+The implication is that each of users, application developers, and infrastructure developers are using one, uniform data structure, and are accessing it using the same mechanism.
 The seamless collaboration of all these components is managed by the controller component.
@@
 
-The infrastructure consists of a set of interdependent analyser componenents (or passes, in compiler parlance): higher-level analysers can only be executed when lower-level analysers already inserted the necessary knowledge into the graph.
+The infrastructure consists of a set of interdependent analyser components (or passes, in compiler parlance): higher-level analysers can only be executed when lower-level analysers already inserted the necessary knowledge into the graph.
 To achieve this, analyser components register their needs and provided services to the controller component, and the controller figures out the topological order in which to initiate the analysers.
@@
 command line interface) through which their services can be accessed, and similarly to analysers, applications also depend on a subset of the analysers in the infrastructure.
-But unlike analysers, application are expected to only read (never modify) the graph, and consequently, applications have no dependers.
+But unlike analysers, application are expected to only read (never modify) the graph, and consequently, applications have no dependents.
 In this arrangement, the controller guarantees that when the user executes a work-intensive application, only the minimally necessary components will be performed.
-Moreover, when developers introduce new features, this arrangement enables them to think declaratively: instead of thinking about where to insert their feature inside a sequence of operations, they only have to think about their dependencies, i.
-e.
+Moreover, when developers introduce new features, this arrangement enables them to think declaratively: instead of thinking about where to insert their feature inside a sequence of operations, they only have to think about their dependencies, i.e.
 what kind of analysers could help them.
@@
 With this, we arrive to our third design goal, \textit{data-driven programming}.
-Thanks to the uniform graph API and the controller-managed dependecy resolution, programmers are forced to think in terms of data instead of code: they have to look at what code knowledge is in the graph already, figure out what data they want to insert, and possibly find existing analysers that makes writing queries  easier for them.
+Thanks to the uniform graph API and the controller-managed dependency resolution, programmers are forced to think in terms of data instead of code: they have to look at what code knowledge is in the graph already, figure out what data they want to insert, and possibly find existing analysers that makes writing queries  easier for them.
 The information in the graph is regulated by a well-defined graph schema, and the graph topology is regulated by the well-defined requirements and services of the analysers.
@@
 
-	\section{Evaluation}
+  \section{Evaluation} % ~ case studies?
 
@@
 	\subsection{Verification} % 1 hasáb - Gabi
-	\subsection{Cost analysis} % 1 hasáb - Dániel
+
+  \clearpage
+  \subsection{Compiler} % 1 hasáb - Dániel
+  In related research~\cite{cscs18,ocs20}, we work on a static cost analysis tool for P4: the tool expects as input a P4 program source code together with execution environment parameters, and outputs various metrics (e.g.
+execution time, energy efficiency) without actually running the P4 program.
+
+  In the current paper, we will not go into details on how the cost analysis tool calculates these metrics, but the principle is that we decompose the P4 program into primitive instructions whose expected cost is constant and already known.
+Implementations of P4 externals such as extern calls and lookup tables (e.g.
+\texttt{packet.extract} and \texttt{ipv4\_lpm} and in Figure~\ref{code:P4}) can also be passed to the tool in the form of these primitive instructions with known costs.
+
+  From this, it follows that part of the static cost analysis problem reduces to a compilation-and-linking problem.
+As an experiment, we implemented a compiler to solve this problem as an application in <NAME>.
+The main reason we chose <NAME>, instead of the much more mature P4C compiler framework was that at first we did not know what kind of representation or code we will need to output: the control and extensibility provided by <NAME> and Gremlin queries gave us tools to experiment and create quick, recyclable prototypes to help us arrive at a final vision.
+While P4C's safety mechanisms (e.g.
+C++ static type system) support developing stable software, in case of prototyping and experimentation these same mechanisms are unused, or possibly even slowing down development.
+
+  Our current target representation for cost analysis is a sequential stack machine with an instruction set similar to JVM bytecode.
+Figure~\ref{code:stack} depicts the compiler output of \texttt{MyIngress} in Figure~\ref{code:P4}.
+In the figure all values (bits and sizes) are represented as integers (a requirement by our cost analysis approach).
+Both \texttt{isValid} and \texttt{ipv4\_lpm} have external implementation that had to be linked with the calls.
+While most P4 targets will not support stack machines, we chose this representation as it is relatively easy to generate, and relatively straightforward to implement.
+We also believe that as long as we do not count the cost of maintaining the stack, we can still make good cost estimations.
+
+  The compiler is built on the control flow analyser in <NAME>: we traverse the CFG, and process each node by traversing the syntax tree under the node.
+We also use the call graph to find which label to jump to when a function is called.
+Thus, much of the compiler state can be delegated to the persistent knowledge graph, and only very specific data (e.g.
+instruction labels) and linking requires program state outside the graph.
+
+  \begin{figure}
+  \begin{lstlisting}[language=asm]
+data:
+  ...
+  headers = 149 
+  headers.ethernet = 149   // size 114
+  ...
+  headers.ipv4 = 263 
+  headers.ipv4.valid = 263 
+  headers.ipv4.size = 264 
+  headers.ipv4.srcAddr = 265 
+  headers.ipv4.dstAddr = 297
+  ...
+code:
+  ...
+  // call isValid(hdr.ipv4) on line 144
+  214:  load 0	      // 0: local address of hdr
+  215:  const 114     // 114: size of hdr.ethernet
+  216:  add           // address of hdr.ipv4
+  217:  invoke 144 1		 
+  // test isValid return value
+  218:  ifeq 224		 
+  // call ipv4_lpm(hdr) on line 38
+  219:  load 0        // 0: local address of hdr
+  222:  invoke 38 1		 
+  223:  pop
+  // terminate with status OK
+  224:  const 0		 
+  225:  return 
+\end{lstlisting}
+\caption{Stack machine code of \texttt{MyIngress}}
+  \label{code:stack}
+\end{figure}
 
@@
 // Control    
-control MyIngress(...) {
+control MyIngress(in headers hdr, ...) {
   apply {

### 2021-03-17 publications/The_tool_intro/paper.tex
tool_intro: some introduction

--- 2021-03-16 publications/The_tool_intro/paper.tex
@@
 	\section{Introduction}
+	  Optimization, verification and refactoring are important tasks of a software development process.
+All of them can be effectively supported by static functional and non-functional (e.g.
+execution time estimation) analysis.
+These analysis can be especially interesting in the case of languages having uncommon language constructs or language structures e.g.
+in the case of some domain specific languages.
+
 	% P4 (max 1-1.5 hasáb) - példa (később használandó a többihez) - Máté
-	P4 \cite{p4paper} is a high level, domain-specific programming language. It is developed mainly for
+	P4~\cite{p4paper} is a high level, domain-specific programming language. It is developed mainly for
 describing the data plane layer of packet processing algorithms of different network
-devices (e.g. switches, routers) in a protocol and target independent way.
+devices (e.g.
+switches, routers) in a protocol and target independent way.
+Figure~\ref{code:P4} illustrates a P4 program.
+The program first defines the applied header structure, than the parser part describes how the fields of the defined headers will be set from the input bit stream (input packet).
+Controller part can modify values of fields of headers and metadata by applying lookup tables.
+The data plane program describes the structure of the tables, the key fields based on that lookups will be executed and the possible results of the lookups, namely the applicable actions.
+However concrete data of the tables (which actions will be executed with which parameters for which key values) are defined by the control plane program, therefore it will not appear in P4.
+Finally the deparse part defines how the output bit stream (output packet) will be created from the headers.
+
+	The paper describes an analysis framework for P4.
+The framework makes possible development of different P4 related analysis methods in a generic and modular way.
+It uses an internal graph representation where the results of the methods are also represented as part of the graph (mainly by adding new edges to the graph).
+In this way the methods can use each other's results as well.
 

### 2021-03-17 publications/The_tool_intro/paper.tex

--- 2021-03-16 publications/The_tool_intro/paper.tex
@@
 	\section{Introduction}
+	  Optimization, verification and refactoring are important tasks of a software development process.
+All of them can be effectively supported by static functional and non-functional (e.g.
+execution time estimation) analysis.
+These analysis can be especially interesting in the case of languages having uncommon language constructs or language structures e.g.
+in the case of some domain specific languages.
+
 	% P4 (max 1-1.5 hasáb) - példa (később használandó a többihez) - Máté
@@
 The program first defines the applied header structure, than the parser part describes how the fields of the defined headers will be set from the input bit stream (input packet).
-Controller part can modify values of headers' fields and metadatas by applying lookup tables.
-The dataplane program describes the structure of the tables, the key fields based on that lookups will be executed and the possible results of the lookups, namely the applicable actions.
-However concrete data of the tables (which actions will be executed with wich parameters for which key values) are defined by the controlplane program, therefore it will not appear in P4.
-Finally the deparse part defines how the output bitstream (output packet) will be created from the headers.
+Controller part can modify values of fields of headers and metadata by applying lookup tables.
+The data plane program describes the structure of the tables, the key fields based on that lookups will be executed and the possible results of the lookups, namely the applicable actions.
+However concrete data of the tables (which actions will be executed with which parameters for which key values) are defined by the control plane program, therefore it will not appear in P4.
+Finally the deparse part defines how the output bit stream (output packet) will be created from the headers.
+
+	The paper describes an analysis framework for P4.
+The framework makes possible development of different P4 related analysis methods in a generic and modular way.
+It uses an internal graph representation where the results of the methods are also represented as part of the graph (mainly by adding new edges to the graph).
+In this way the methods can use each other's results as well.
 

### 2021-03-18 publications/The_tool_intro/paper.tex
pub: added 1 column and figure on experts. added 0.5 column on visualization.

@@
 	% kisebb gráf ábra
+  As we see earlier in Figure~\ref{fig:arch-deps}, the heavy-lifting in <NAME> is done by various code analyser components, each adding new information about the P4 code to the knowledge graph using what is already there.
+We now introduce a few analyser modules using an example: Figure~\ref{fig:output} depicts a small subset of the knowledge graph taken after we executed control flow analysis, call analysis, and call sites analysis on the P4 code in Figure~\ref{code:P4} (specifically the \texttt{MyIngress} control).
+  First, the contoller finds the topological order of their dependencies, and then starts executing them in order.
+In this case, the first dependency executed is the parser, parsing the P4 code and filling the knowledge graph with the syntax tree nodes and edges.
+
+  Each analyser components adds new edges as an overlay graph.
+These overlays (domains) are separated by the \texttt{dom} edge-attributes: for example \texttt{CFG} is the domain introduced by the control flow analysis, and \texttt{CALL} is the domain of the call analysis, \texttt{SITES} is that of call site analysis.
+The \texttt{role} edge-attribute describes edge semantics inside their domain.
+For example, \texttt{calls} in \texttt{CALL} links a procedure to those procedures that it calls (e.g.
+\texttt{MyIngress} control calling \texttt{ipv4\_lpm} table lookup).
+On the other hand, \texttt{calls} in \texttt{SITES} links call statements (the \textit{direct application} of table \texttt{ipv4\_lpm}) to the called procedure (table \texttt{ipv4\_lpm}).
+
+  At the same time, the \texttt{CFG} domain contains \texttt{flow}, \texttt{entry}, and \texttt{return} edges (among others) to denote the flow of control between various nodes of the syntax tree, and to identify entry and exit nodes.
+For example, by following these edges, you can see how control flows from the \texttt{MyIngress} entry point through the conditional, terminating on the call of \texttt{ipv4\_lpm}.
+(For more information on how we implemented control flow analysis using Gremlin, see~\cite{ocs20}.) The figure also partially includes domains of other analysers, such as \texttt{SYMBOL}.
+This analysers creates the graph-equivalent of a symbol table by identifying which declaration declares which name, and links usages of this name in the scope of the declaration to the declaration.
+
+  \begin{figure}
+    \includegraphics[width=0.45\textwidth]{figures/output.pdf}
+    \caption{TODO}\label{fig:output}
+  \end{figure}
 
@@
 	\subsection{Visualization} % 0.5 hasáb
+
+  Since its function is the easiest to understand, the first application we introduce is graph visualiation.
+This application expects a list of analyser component names, executes them, and then, prints a subgraph of the knowledge graph containing only the domains of the analysers in the list.
+For example, to print the full version of the graph in Figure~\ref{fig:output}, we should run the following command:
+
+  \begin{lstlisting}[language=bash, basicstyle=\scriptsize]
+  $ <NAME> draw -A ControlFlow SymbolTable CallGraph CallSites AST
+\end{lstlisting}
+
+The subcommand \texttt{draw} tells <NAME> to run the visualizer, while \texttt{-A} is a flag (defined by the visualizer UI) expects the analyser names that will be passed to the visulalizer application.
+
+A possibly interesting implementation detail here is that the visualizer technically depends on \textit{all} the analysers defined in <NAME>, since it must be able to visualize anything the user may pass.
+Yet, we still managed to avoid executing those that are not requested by user (and not dependencies of the requested ones): we implemented dependency resolution in the controller using Java dependency injection (DI), and DI offers lazy initializion of the dependencies.
+This way we can filter the analysers and only initialize those that were requested by the user.
+
 	\subsection{Verification} % 1 hasáb - Gabi
 
-  \clearpage
   \subsection{Compiler} % 1 hasáb - Dániel

### 2021-03-19 publications/The_tool_intro/paper.tex
pub: add 0.5 column and figure on verification. add some related work

@@
   morekeywords={load, const, invoke, ifeq, pop, add, return, code, data}
+}
+
+\lstdefinelanguage{cond}{
+	showlines=true,
+	morecomment=[l]{//},
+	keepspaces=true,
+	basicstyle=\scriptsize\ttfamily,
+	emphstyle=\itshape,
+	emph={},
+	commentstyle=\color{red},
+	keywordstyle=\color{blue},
+	morekeywords={Pre, Post, valid, invalid}
 }
@@
 	% Akár gremlin/gráf alapú dolgok, ami nem p4 (akár refactorerl) - mindenki
+
+	\subsection{Used tools}
+
+	\subsection{Similar tools}
+
+	%verification
+
+	Our solution is a general tool which contains several analyzes.	There are different analysis specific tools, which concentrate the error checking of P4 programs.
+
+	Some of them are created for the first main version of the P4 - the P4$_\text{14}$.
+For example Assert-P4 \cite{Assert-P4} and Vera \cite{Vera} ask annotated P4 source from the developer and with symbolic execution they check if the predefined properties are correct during the program, although Vera can also detect common errors without annotations.
+P4V \cite{P4V} creates a formula, which describe the proper behavior of the program and checks the satisfiability of it with SMT solver.
+
+	There are other tools, which can analyze P4$_\text{16}$ programs too.
+BF4 \cite{bf4} is created as a p4c backend, which can not only detect error possibilities, but it is able to repair them by adding new keys to the table and modify the table contents.
 
@@
   \subsection{Verification} % 1 hasáb - Gabi
+  Verification is a possible extension of the tool, which is added to it as an application.
+The main focus is to detect errors and suspicious cases, which can be caused by the usage of invalid header or uninitialized fields.
+The goal of this detection is to report these usages for the developer to avoid undefined behaviour in the programs.
+
+  There are different approaches for the verification of the P4 programs.
+There are tools, which uses symbolic execution \cite{vera}, or SMT solver \cite{p4v, bf4}.
+The reason we insert the verification into this tool is that we would like to create a universal framework to help the P4 developers in their work and have an assistant analysis, which helps in error detection.
+
+  The approach of the checking is defined in our previous paper \cite{cscs2020}, but shortly, it calculates the pre-and post-condition of the different blocks -- i.e the control apply functions, the tables and actions --, the parser and the deparser of the program and based on their results it can detect improper usage of the fields and headers.
+Three types of cases can be detected: when there are some error cases in a block; when there is any inconsistency between the blocks; and when the need of the parser-deparser is inconsistent with the need of the control function.
+
+  In Figure \ref{code:cond}, there is an example condition for the MyIngress.
+We can see 4 pairs of conditions, because it has 4 possible execution paths - there are three when the condition is true, and the table executes one of the possible actions i.e.
+$\mathit{ipv4\_forward}$, $\mathit{drop}$ or $\mathit{NoAction}$, and one when the condition is false.
+
+  \begin{figure}
+  	\begin{lstlisting}[language=cond]
+  	MyIngress:
+  	[
+  	// true condition and ipv4_forward
+  	  (Pre: 
+  	     valid:   [ipv4, ipv4.dstAddr, ipv4.ttl,
+  	               ethernet, ethernet.dstAddr],
+  	     invalid: [drop],
+  	   Post: 
+  	     valid:   [ipv4, ipv4.dstAddr, ipv4.ttl,
+  	               ethernet, ethernet.dstAddr],
+  	     invalid: [drop]),
+  	// true condition and drop
+  	  (Pre: 
+  	     valid:   [ipv4, ipv4.dstAddr],
+  	     invalid: [drop],
+  	   Post: 
+  	     valid:   [drop, ipv4, ipv4.dstAddr],
+  	     invalid: []),
+  	// true condition and NoAction
+  	  (Pre: 
+  	     valid:   [ipv4, ipv4.dstAddr],
+  	     invalid: [ipv4, ipv4.dstAddr, drop],
+  	   Post: 
+  	     valid:   [ipv4, ipv4.dstAddr],
+  	     invalid: [ipv4, ipv4.dstAddr, drop]),
+   	// false condition
+   	  (Pre: 
+   	     valid:   [ipv4, ipv4.dstAddr],
+   	     invalid: [ipv4, ipv4.dstAddr, drop],
+   	   Post: 
+   	     valid:   [ipv4, ipv4.dstAddr],
+   	     invalid: [ipv4, ipv4.dstAddr, drop]), 
+   	]
+  	\end{lstlisting}
+  	\caption{Conditions of \texttt{MyIngress}}
+  	\label{code:cond}
+  \end{figure}
+
+  This calculation is built into the tool as an application, which uses the call-graph and the control-flow graph analyzes of the experts.
+The method can combine these two graphs, and while traversing them, it calculates the condition pair for the vertices of the call graph, while getting the information for it from the control flow graph.
 

### 2021-03-21 publications/The_tool_intro/paper.tex
pub: typos, paragraph on gremlin, list of gremlin-based static analysis tools

@@
 
+  In the tool architecture described in Section~\ref{sec:rep}, we use a Gremlin graph database as storage backend (knowledge graph).
+Gremlin is a compositional query language and API that is implemented by many large-scale graph databases.
+This makes it possible to change graph implementations with almost no modification to the <NAME> code base at all.
+In earlier work~\cite{icai20}, we also profiled a few graph backends for control flow traverals.
+  Another consequence is that analysers have to be implemented as graph query workflows.
+By coarsely granularizing queries, most of the work can be delegated to the database, and with this, the choice of the workflow language (e.g.
+Java) can become negligible.
+In earlier work~\cite{macs20}, we experimented with implementing a whole control flow analysis as a single graph query: while having advantages, it can also hinder code maintainability as queries are often more difficult to read and modify.
+
 	\subsection{Similar tools}
@@
 BF4 \cite{bf4} is created as a p4c backend, which can not only detect error possibilities, but it is able to repair them by adding new keys to the table and modify the table contents.
+
+  %graph-based
+  % - refactorerl
+
+  %gremlin-based
+  % - An Efficient and Scalable Platform for Java Source Code Analysis Using Overlaid Graph Representations: https://core.ac.uk/download/pdf/323304005.pdf
+  % - Graph-based Vulnerability Detection via Extracting Features from Sliced Code: https://qrs20.techconf.org/QRSC2020_FULL/pdfs/QRS-C2020-4QOuHkY3M10ZUl1MoEzYvg/891500a038/891500a038.pdf
+  % - Application of Graph Databases for Static Code Analysis of Web-Applications: http://ceur-ws.org/Vol-2590/short30.pdf
+  % - Efficient and Flexible Discovery of PHP Application Vulnerabilities: https://fabs.codeminers.org/papers/2017b-eurosp.pdf
+  % -  Modeling and Discovering Vulnerabilities with Code Property Graphs: https://fabs.codeminers.org/papers/2014-ieeesp.pdf , slides: http://mlsec.org/joern/docs/2014-inbot.pdf
+  % - Reverse Engineering State and Strategy Design Patterns using Static Code Analysis: https://thesai.org/Downloads/Volume9No1/Paper_78-Reverse_Engineering_State_and_Strategy_Design_Patterns.pdf
 
@@
 Modular compilers like P4C improve this design by structuring the passes into a library: backends assemble their own frontends and midends from a catalogue of passes provided by the compiler.
-Moreover, P4C allows getting information from older states of the IR, as each transformation passes return an immutable IR instance.
+Moreover, P4C allows getting information from older states of the IR, as each transformation pass returns an immutable IR instance.
 Even here, the three-fold separation of frontend-midend-backend have to remain: in order satisfy midend-dependencies, and subsequently, backend-dependencies, the backend must sequentially execute the frontend, the midend, and finally its own passes.
@@
 
-	\subsection{Representation - Architecture} % 4 hasáb - Dániel
+\subsection{Representation - Architecture}\label{sec:rep} % 4 hasáb - Dániel
 	% belső gráf, a koncepció
@@
 The graph is also exposed to the user to enable custom features (e.g.
-to attach external loggers, visualizers, and validators).
+to attach external loggers, visualisers, and validators).
 The information in the knowledge graph is accessed using graph queries written in Gremlin (see Section \ref{sec:gremlin}).
-The implication is that each of users, application developers, and infrastructure developers are using one, uniform data structure, and are accessing it using the same mechanism.
+The implication is that users, application developers, and infrastructure developers are using one, uniform data structure, and are accessing it using the same mechanism.
 The seamless collaboration of all these components is managed by the controller component.
@@
 The information in the graph is regulated by a well-defined graph schema, and the graph topology is regulated by the well-defined requirements and services of the analysers.
-Moreover, since the graph instance is detached from the code analysis framework, the programmers can access it by external tools for visualizing, monitoring and validating purposes.
+Moreover, since the graph instance is detached from the code analysis framework, the programmers can access it by external tools for visualising, monitoring and validating purposes.
 Like this, programmers can almost completely avoid understanding the existing code base, and only have to look at and interact with the data in the graph.
@@
 We now introduce a few analyser modules using an example: Figure~\ref{fig:output} depicts a small subset of the knowledge graph taken after we executed control flow analysis, call analysis, and call sites analysis on the P4 code in Figure~\ref{code:P4} (specifically the \texttt{MyIngress} control).
-  First, the contoller finds the topological order of their dependencies, and then starts executing them in order.
+  First, the controller finds the topological order of their dependencies, and then starts executing them in order.
 In this case, the first dependency executed is the parser, parsing the P4 code and filling the knowledge graph with the syntax tree nodes and edges.
@@
 For example, by following these edges, you can see how control flows from the \texttt{MyIngress} entry point through the conditional, terminating on the call of \texttt{ipv4\_lpm}.
-(For more information on how we implemented control flow analysis using Gremlin, see~\cite{ocs20}.) The figure also partially includes domains of other analysers, such as \texttt{SYMBOL}.
+(For more information on how we implemented control flow analysis using Gremlin, see~\cite{macs20}.) The figure also partially includes domains of other analysers, such as \texttt{SYMBOL}.
 This analysers creates the graph-equivalent of a symbol table by identifying which declaration declares which name, and links usages of this name in the scope of the declaration to the declaration.
@@
 	% egyedi elemzések mérése
-	\subsection{Visualization} % 0.5 hasáb
+	\subsection{Visualisation} % 0.5 hasáb
 
-  Since its function is the easiest to understand, the first application we introduce is graph visualiation.
+  Since its function is the easiest to understand, the first application we introduce is graph visualisation.
 This application expects a list of analyser component names, executes them, and then, prints a subgraph of the knowledge graph containing only the domains of the analysers in the list.
@@
 
-  The subcommand \texttt{draw} tells <NAME> to run the visualizer, while \texttt{-A} is a flag (defined by the visualizer UI) expects the analyser names that will be passed to the visulalizer application.
+  The subcommand \texttt{draw} tells <NAME> to run the visualiser, while \texttt{-A} is a flag (defined by the visualiser UI) expects the analyser names that will be passed to the visualiser application.
 
-  A possibly interesting implementation detail here is that the visualizer technically depends on \textit{all} the analysers defined in <NAME>, since it must be able to visualize anything the user may pass.
-Yet, we still managed to avoid executing those that are not requested by user (and not dependencies of the requested ones): we implemented dependency resolution in the controller using Java dependency injection (DI), and DI offers lazy initializion of the dependencies.
+  A possibly interesting implementation detail here is that the visualiser technically depends on \textit{all} the analysers defined in <NAME>, since it must be able to visualise anything the user may pass.
+Yet, we still managed to avoid executing those that are not requested by the user (and not dependencies of the requested ones): we implemented dependency resolution in the controller using Java dependency injection (DI), and DI offers lazy initialization of the dependencies.
 This way we can filter the analysers and only initialize those that were requested by the user.
@@
 
-  The compiler is built on the control flow analyser in <NAME>: we traverse the CFG, and process each node by traversing the syntax tree under the node.
+  The compiler is built on top of the control flow analyser in <NAME>: we traverse the CFG, and process each node by traversing the syntax tree under the node.
 We also use the call graph to find which label to jump to when a function is called.

### 2021-03-22 publications/The_tool_intro/paper.tex
tool_intro:some related work

@@
 
-	Our solution is a general tool which contains several analyzes.	There are different analysis specific tools, which concentrate the error checking of P4 programs.
-
-	Some of them are created for the first main version of the P4 - the P4$_\text{14}$.
+	Considering related work there are many research applying specific analysis technics for P4.
+Most of them concentrate on error checking of P4 programs.
 For example Assert-P4 \cite{Assert-P4} and Vera \cite{Vera} ask annotated P4 source from the developer and with symbolic execution they check if the predefined properties are correct during the program, although Vera can also detect common errors without annotations.
 P4V \cite{P4V} creates a formula, which describe the proper behavior of the program and checks the satisfiability of it with SMT solver.
+These tools are created for an earlier version of P4, namely P4$_\text{14}$.
+There are also verification tools, which can manage the newer version (P4$_\text{16}$) too.
+BF4 \cite{bf4} is created as a p4c backend, which can not only detect error possibilities, but it is able to repair them by adding new keys to the table and modify the table contents.
+An other tool p4-data-flow \cite{p4dataflow} uses data flow analysis to detect potential bugs in P4 switch codes.
+	Some other tools uses analysis methods for different pruposes. For example p4pktgen \cite{p4pktgen} uses symbolic execution for automatically generating test cases.
 
-	There are other tools, which can analyze P4$_\text{16}$ programs too.
-BF4 \cite{bf4} is created as a p4c backend, which can not only detect error possibilities, but it is able to repair them by adding new keys to the table and modify the table contents.
+	Our solution is a general tool which contains several analyzes.
 

### 2021-03-22 publications/The_tool_intro/paper.tex
pub: add bib

@@
 Most of them concentrate on error checking of P4 programs.
-For example Assert-P4 \cite{Assert-P4} and Vera \cite{Vera} ask annotated P4 source from the developer and with symbolic execution they check if the predefined properties are correct during the program, although Vera can also detect common errors without annotations.
-P4V \cite{P4V} creates a formula, which describe the proper behavior of the program and checks the satisfiability of it with SMT solver.
+For example Assert-P4 \cite{assertp4} and Vera \cite{vera} ask annotated P4 source from the developer and with symbolic execution they check if the predefined properties are correct during the program, although Vera can also detect common errors without annotations.
+P4V \cite{p4v} creates a formula, which describe the proper behavior of the program and checks the satisfiability of it with SMT solver.
 These tools are created for an earlier version of P4, namely P4$_\text{14}$.
@@
 
-  The approach of the checking is defined in our previous paper \cite{cscs2020}, but shortly, it calculates the pre-and post-condition of the different blocks -- i.e the control apply functions, the tables and actions --, the parser and the deparser of the program and based on their results it can detect improper usage of the fields and headers.
+  The approach of the checking is defined in our previous paper \cite{ownCheck}, but shortly, it calculates the pre-and post-condition of the different blocks -- i.e the control apply functions, the tables and actions --, the parser and the deparser of the program and based on their results it can detect improper usage of the fields and headers.
 Three types of cases can be detected: when there are some error cases in a block; when there is any inconsistency between the blocks; and when the need of the parser-deparser is inconsistent with the need of the control function.

### 2021-03-22 publications/The_tool_intro/paper.tex
pub: add P4RL

@@
 For example Assert-P4 \cite{assertp4} and Vera \cite{vera} ask annotated P4 source from the developer and with symbolic execution they check if the predefined properties are correct during the program, although Vera can also detect common errors without annotations.
-P4V \cite{p4v} creates a formula, which describe the proper behavior of the program and checks the satisfiability of it with SMT solver.
+P4V \cite{p4v} creates a formula, which describes the proper behavior of the program and checks the satisfiability of it with SMT solver.
 These tools are created for an earlier version of P4, namely P4$_\text{14}$.
@@
 An other tool p4-data-flow \cite{p4dataflow} uses data flow analysis to detect potential bugs in P4 switch codes.
-	Some other tools uses analysis methods for different pruposes. For example p4pktgen \cite{p4pktgen} uses symbolic execution for automatically generating test cases.
+	These tools use static analysis, but there are other approaches too.
+P4RL \cite{p4rl} works with the programs at runtime and its verification is based on fuzzing and reinforcement learning techniques.
+	Some other tools uses analysis methods for different purposes. For example p4pktgen \cite{p4pktgen} uses symbolic execution for automatically generating test cases.
 

### 2021-03-22 publications/The_tool_intro/paper.tex
tool_intro: some reference

--- 2021-03-22 publications/The_tool_intro/paper.tex
@@
 
+\begin{figure*}
+\begin{tabular}{|p{3.3cm}|p{5.9cm}|p{7.7cm}|}
+\hline
+\begin{lstlisting}[language=P4]
+// Definitions
+typedef bit<9>  egSpec_t;
+typedef bit<48> macAddr_t;
+typedef bit<32> ip4Addr_t;
+
+// Headers
+header ethernet_t {
+  macAddr_t dstAddr;
+  macAddr_t srcAddr;
+  bit<16>   etherType; }
+
+header ipv4_t {
+  bit<8>    ttl;
+  ip4Addr_t srcAddr;
+  ip4Addr_t dstAddr;... }
+
+struct headers {
+  ethernet_t   ethernet;
+  ipv4_t       ipv4; }
+
+\end{lstlisting}
+&
+\begin{lstlisting}[language=P4]
+// Parser
+parser MyParser(...) {
+  state start { transition parse_ethernet; }
+  state parse_ethernet {
+    packet.extract(hdr.ethernet);
+    transition select(hdr.ethernet.etherType) {
+      TYPE_IPV4: parse_ipv4;
+      default: accept; } }
+  state parse_ipv4 {
+    packet.extract(hdr.ipv4);
+    transition accept; } }
+
+// Control    
+control MyIngress(in headers hdr, ...) {
+  apply {
+    if (hdr.ipv4.isValid()) {
+           ipv4_lpm.apply(); }
+  }         
+  action drop() {
+    mark_to_drop(standard_metadata);
+  }    
+\end{lstlisting}
+&
+\begin{lstlisting}[language=P4]
+  action ipv4_forward(macAddr_t dstAddr, egSpec_t port) {
+    standard_metadata.egress_spec = port;
+    hdr.ethernet.srcAddr = hdr.ethernet.dstAddr;
+    hdr.ethernet.dstAddr = dstAddr;
+    hdr.ipv4.ttl = hdr.ipv4.ttl - 1;
+  }    
+  table ipv4_lpm {
+    key = {  hdr.ipv4.dstAddr: lpm;  }
+    actions = {
+      ipv4_forward;
+      drop;
+      NoAction;}
+    ... }   
+}
+
+//Deparser
+control MyDeparser(packet_out packet, in headers hdr) {
+  apply {
+    packet.emit(hdr.ethernet);
+    packet.emit(hdr.ipv4);}
+}
+\end{lstlisting}\\
+\hline
+\end{tabular}
+\caption{P4 example}
+  \label{code:P4}
+\end{figure*}
+
 	\section{Related Work}
@@
 An other tool p4-data-flow \cite{p4dataflow} uses data flow analysis to detect potential bugs in P4 switch codes.
-	Some other tools uses analysis methods for different pruposes. For example p4pktgen \cite{p4pktgen} uses symbolic execution for automatically generating test cases.
+	Some other tools uses analysis methods for different pruposes.
+For example p4pktgen \cite{p4pktgen} uses symbolic execution for automatically generating test cases.
+Flightplan \cite{flightplan} can splits a P4 program into a set of cooperating P4 programs and maps them to run as a distributed system formed of several, possibly heterogeneous, dataplanes.
+During this process they use several analysis technics, for example to gather variables whose values must be transfer between dataplanes.
 
@@
   %% p4c is a factory. this tool is a laboratory.
-
-\clearpage
 
@@
 
-\begin{figure*}
-\begin{tabular}{|p{3.3cm}|p{5.9cm}|p{7.7cm}|}
-\hline
-\begin{lstlisting}[language=P4]
-// Definitions
-typedef bit<9>  egSpec_t;
-typedef bit<48> macAddr_t;
-typedef bit<32> ip4Addr_t;
-
-// Headers
-header ethernet_t {
-  macAddr_t dstAddr;
-  macAddr_t srcAddr;
-  bit<16>   etherType; }
-
-header ipv4_t {
-  bit<8>    ttl;
-  ip4Addr_t srcAddr;
-  ip4Addr_t dstAddr;... }
-
-struct headers {
-  ethernet_t   ethernet;
-  ipv4_t       ipv4; }
-
-\end{lstlisting}
-&
-\begin{lstlisting}[language=P4]
-// Parser
-parser MyParser(...) {
-  state start { transition parse_ethernet; }
-  state parse_ethernet {
-    packet.extract(hdr.ethernet);
-    transition select(hdr.ethernet.etherType) {
-      TYPE_IPV4: parse_ipv4;
-      default: accept; } }
-  state parse_ipv4 {
-    packet.extract(hdr.ipv4);
-    transition accept; } }
-
-// Control    
-control MyIngress(in headers hdr, ...) {
-  apply {
-    if (hdr.ipv4.isValid()) {
-           ipv4_lpm.apply(); }
-  }         
-  action drop() {
-    mark_to_drop(standard_metadata);
-  }    
-\end{lstlisting}
-&
-\begin{lstlisting}[language=P4]
-  action ipv4_forward(macAddr_t dstAddr, egSpec_t port) {
-    standard_metadata.egress_spec = port;
-    hdr.ethernet.srcAddr = hdr.ethernet.dstAddr;
-    hdr.ethernet.dstAddr = dstAddr;
-    hdr.ipv4.ttl = hdr.ipv4.ttl - 1;
-  }    
-  table ipv4_lpm {
-    key = {  hdr.ipv4.dstAddr: lpm;  }
-    actions = {
-      ipv4_forward;
-      drop;
-      NoAction;}
-    ... }   
-}
-
-//Deparser
-control MyDeparser(packet_out packet, in headers hdr) {
-  apply {
-    packet.emit(hdr.ethernet);
-    packet.emit(hdr.ipv4);}
-}
-\end{lstlisting}\\
-\hline
-\end{tabular}
-\caption{P4 example}
-  \label{code:P4}
-\end{figure*}
-
 \bibliographystyle{ACM-Reference-Format}

### 2021-03-22 publications/The_tool_intro/paper.tex

--- 2021-03-22 publications/The_tool_intro/paper.tex
@@
 P4RL \cite{p4rl} works with the programs at runtime and its verification is based on fuzzing and reinforcement learning techniques.
-	Some other tools uses analysis methods for different purposes. For example p4pktgen \cite{p4pktgen} uses symbolic execution for automatically generating test cases.
+	Some other tools uses analysis methods for different purposes.
+For example p4pktgen \cite{p4pktgen} uses symbolic execution for automatically generating test cases.
+Flightplan \cite{flightplan} can splits a P4 program into a set of cooperating P4 programs and maps them to run as a distributed system formed of several, possibly heterogeneous, dataplanes.
+During this process they use several analysis technics, for example to gather variables whose values must be transfer between dataplanes.
 

### 2021-03-22 publications/The_tool_intro/paper.tex
pub: added some conclusion and future work

@@
 	Our solution is a general tool which contains several analyzes.
+
+	The approach of the graph-based static analysis of programs is well-known. It is used wide ranged for example with Java \cite{9064792},
 
@@
 
+	  The goal of this paper is to introduce our analysis framework for P4 programs, which is based on a huge graph representation of the program.
+Analysis can be easily inserted into the tool, as an expert, which calculates the proper side information from the main syntax tree, and also stores this new information in it.
+
+	So far, we have three main applications, which use some subgraph -- experts --, but we plan to increase these numbers and extend them.
+Two near future plans are the dependency graph and the def-use graph from which we could give some more useful information for the developers about their P4 source.
+The dependency graph will contain the data and control dependencies between the statements, the def-use graph will show which fields are defined and used in which statements.
+Based on these analyzes we will be able to see more connection between the statements.
+
+	% talán még cost-analysis? slicing? refactor? error correction?
+
+	Our major purpose to create a tool, which can facilitate and support the work of  P4 developers.
+
 \bibliographystyle{ACM-Reference-Format}

### 2021-03-22 publications/The_tool_intro/paper.tex
pub: added some changes in verification

@@
 
-  There are different approaches for the verification of the P4 programs.
-There are tools, which uses symbolic execution \cite{vera}, or SMT solver \cite{p4v, bf4}.
-The reason we insert the verification into this tool is that we would like to create a universal framework to help the P4 developers in their work and have an assistant analysis, which helps in error detection.
-
   The approach of the checking is defined in our previous paper \cite{ownCheck}, but shortly, it calculates the pre-and post-condition of the different blocks -- i.e the control apply functions, the tables and actions --, the parser and the deparser of the program and based on their results it can detect improper usage of the fields and headers.
@@
   In Figure \ref{code:cond}, there is an example condition for the MyIngress.
-We can see 4 pairs of conditions, because it has 4 possible execution paths - there are three when the condition is true, and the table executes one of the possible actions i.e.
-$\mathit{ipv4\_forward}$, $\mathit{drop}$ or $\mathit{NoAction}$, and one when the condition is false.
+We can see 4 pairs of conditions, because it has 4 possible execution paths - there are three when the condition of the branch is true, and the table executes one of the possible actions i.e.
+$\mathit{ipv4\_forward}$, $\mathit{drop}$ or $\mathit{NoAction}$, and one when the condition of the branch is false.
 
@@
 
-  This calculation is built into the tool as an application, which uses the call-graph and the control-flow graph analyzes of the experts.
-The method can combine these two graphs, and while traversing them, it calculates the condition pair for the vertices of the call graph, while getting the information for it from the control flow graph.
+   This calculation is built into the tool as an application.
+It uses two experts: the call graph and control-flow graph.
+While traversing through the call graph it can reach calls of tables and actions.
+When it reaches a call, it starts to traverse through the proper subgraph of the control-flow graph and calculates the conditions of the actual block.
+Every condition is stored in the graph as a property of the called vertex of the call graph.
+   The implementation gets and saves every information about the program with Gremlin queries.
 

### 2021-03-22 publications/The_tool_intro/paper.tex
tool_intro: minor changes

@@
 \usepackage{comment, graphicx, algorithm, algorithmic, listings}
+\usepackage[utf8]{inputenc}
 
@@
 
-	\title{TODO}
+	\title{<NAME> - an analyser framework for P4}
 
@@
 An other tool p4-data-flow \cite{p4dataflow} uses data flow analysis to detect potential bugs in P4 switch codes.
-	These tools use static analysis, but there are other approaches too.
-P4RL \cite{p4rl} works with the programs at runtime and its verification is based on fuzzing and reinforcement learning techniques.
+
 	Some other tools uses analysis methods for different purposes.
@@
 For example, to print the full version of the graph in Figure~\ref{fig:output}, we should run the following command:
-
   \begin{lstlisting}[language=bash, basicstyle=\scriptsize]
@@
 \end{lstlisting}
-
   The subcommand \texttt{draw} tells <NAME> to run the visualiser, while \texttt{-A} is a flag (defined by the visualiser UI) expects the analyser names that will be passed to the visualiser application.

### 2021-03-22 publications/The_tool_intro/paper.tex
tool_intro:some motivation

@@
 
-\usepackage{comment, graphicx, algorithm, algorithmic, listings}
+\usepackage{comment, graphicx, algorithm, algorithmic, listings, multicol}
 \usepackage[utf8]{inputenc}
@@
 In this way the methods can use each other's results as well.
+The proposed tool makes also possible to create rapid, prototype implementation of different analysis concepts using a common toolset.
 
@@
 	\section{Related Work}
+	\label{sec:related}
 	% kb 1.5 hasáb
@@
 
-	Our solution is a general tool which contains several analyzes.
+	Comparing these approches this paper presents a generic framework make possible to implement several analyses methods which can use each other's results as well.
 
@@
   %% p4c is a factory. this tool is a laboratory.
+
+P4 is a relatively new, domain specific language having some uncommon language elements (for example match-action tables).
+The language makes possible the description of the data plane layer of packet processing algorithms.
+However for a real execution also a corresponding control plane layer is needed, which part is more or less a black hole while we consider only the P4 source code.
+Because of these testing, verification and generally functional and non-functional analysis of P4 programs are non trivial tasks sometimes requiring language specific techniques.
+
+Section~\ref{sec:related} introduces several applications using different analysis methods for P4.
+The authors also have some earlier results for determining potentially erroneous code parts~\cite{ownCheck} and for predicting execution cost~\cite{LukacsOcs} of P4 programs.
+These methods usually require different analysis techniques, however these techniques often can have interleaving parts (for example creating an abstract syntax tree or a control flow graph).
+
+This paper presents a framework allows the implementation of different analysis methods using a common basis.
+The framework applies an extensible integral graph representation where the results of the different analysis methods are represented also as part of the graph.
+This makes possible execution of different methods in a hierarchical order where methods can use the results (or some part of the results) of previously applied methods.
+
+The framework supports rapid implementation of new analysis methods applicable for P4 language in a way where results of the methods will be easily reusable.
 

### 2021-03-22 publications/The_tool_intro/paper.tex
tool_intro:some motivation

@@
 	\begin{abstract}
-		TODO
+		There are many important tasks in a conventional software development process which can be supported by different analysis techniques. P4 is a high level domain specific language for
+describing the data plane layer of packet processing algorithms. It has several uncommon language elements and concepts often make analysis of P4 programs a laborious task. 
+The paper presents <NAME>, a generic analysis framework for P4 makes possible development of different P4 related analysis methods in a generic and modular way.
+The framework uses an integral graph representation which contains the results of applied analysis methods too.
+This way the framework supports rapid implementation of new analysis methods in a way where the results will be also easily reusable by other methods.
+
 	\end{abstract}
@@
   \subsection{Compiler} % 1 hasáb - Dániel
-  In related research~\cite{cscs18,ocs20}, we work on a static cost analysis tool for P4: the tool expects as input a P4 program source code together with execution environment parameters, and outputs various metrics (e.g.
+  In related research~\cite{cscs18,LukacsOcs}, we work on a static cost analysis tool for P4: the tool expects as input a P4 program source code together with execution environment parameters, and outputs various metrics (e.g.
 execution time, energy efficiency) without actually running the P4 program.

### 2021-03-22 publications/The_tool_intro/paper.tex
pub: added code line numbers and updated output figure (line nums, size)

--- 2021-03-22 publications/The_tool_intro/paper.tex
@@
 \begin{figure*}
-\begin{tabular}{|p{3.3cm}|p{5.9cm}|p{7.7cm}|}
+\begin{tabular}{|p{3.75cm}|p{6.5cm}|p{6.5cm}|}
 \hline
-\begin{lstlisting}[language=P4]
+{\begin{lstlisting}[language=P4,numbers=left,firstnumber=1,xleftmargin=2.5em]
 // Definitions
@@
   macAddr_t srcAddr;
-  bit<16>   etherType; }
+  bit<16>   etherType; 
+}
 
@@
   ip4Addr_t srcAddr;
-  ip4Addr_t dstAddr;... }
+  ip4Addr_t dstAddr;... 
+}
 
@@
   ethernet_t   ethernet;
-  ipv4_t       ipv4; }
+  ipv4_t       ipv4; 
+}
 
-\end{lstlisting}
+\end{lstlisting}}
 &
-\begin{lstlisting}[language=P4]
+{\begin{lstlisting}[language=P4,numbers=left,firstnumber=24,xleftmargin=2.5em]
 // Parser
@@
     packet.extract(hdr.ipv4);
-    transition accept; } }
+    transition accept; } 
+}
 
@@
     if (hdr.ipv4.isValid()) {
-           ipv4_lpm.apply(); }
+           ipv4_lpm.apply(); 
+    }
   }         
@@
   }    
-\end{lstlisting}
+\end{lstlisting}}
 &
-\begin{lstlisting}[language=P4]
-  action ipv4_forward(macAddr_t dstAddr, egSpec_t port) {
+{\begin{lstlisting}[language=P4,numbers=left,firstnumber=47,xleftmargin=2.5em]
+  action ipv4_forward(macAddr_t dstAddr, 
+                      egSpec_t port) {
     standard_metadata.egress_spec = port;
@@
 //Deparser
-control MyDeparser(packet_out packet, in headers hdr) {
+control MyDeparser(packet_out packet, 
+                   in headers hdr) {
   apply {
@@
 }
-\end{lstlisting}\\
+\end{lstlisting}}\\
 \hline

### 2021-03-22 publications/The_tool_intro/paper.tex
pub: moved gremlin part to S4.1, fixed cites (macs20 still missing) and refs, added related work (referl, java, c), fixes in deps figure, added filename to visualisation command

@@
 
-	\subsection{Used tools}
-
-  In the tool architecture described in Section~\ref{sec:rep}, we use a Gremlin graph database as storage backend (knowledge graph).
-Gremlin is a compositional query language and API that is implemented by many large-scale graph databases.
-This makes it possible to change graph implementations with almost no modification to the <NAME> code base at all.
-In earlier work~\cite{icai20}, we also profiled a few graph backends for control flow traverals.
-  Another consequence is that analysers have to be implemented as graph query workflows.
-By coarsely granularizing queries, most of the work can be delegated to the database, and with this, the choice of the workflow language (e.g.
-Java) can become negligible.
-In earlier work~\cite{macs20}, we experimented with implementing a whole control flow analysis as a single graph query: while having advantages, it can also hinder code maintainability as queries are often more difficult to read and modify.
-
 	\subsection{Similar tools}
@@
 
-	Comparing these approches this paper presents a generic framework make possible to implement several analyses methods which can use each other's results as well.
+	Comparing these approaches this paper presents a generic framework make possible to implement several analyses methods which can use each other's results as well.
 
-	The approach of the graph-based static analysis of programs is well-known. It is used wide ranged for example with Java \cite{9064792},
+  A major inspiration for this work was RefactorErl~\cite{referl}, a static analysis tool for Erlang.
+RefactorErl stores program information in a graph called the Semantic Program Graph using relation databases, and hosts in own query language for exploring the stored information.
+Many features in our work -- such as using graph databases and their built-in query languages instead of in-house solutions -- can be considered to be the streamlining of best practices found in RefactorErl.
+
+  Recently, other works also leveraged graph databases for static analysis purposes.
+ProgQuery \cite{java-static} is a similar static analysis tool for Java, built on Neo4j and its Cypher query language.
+The authors emphasize that using Neo4j yielded substantial improvements in analysis time and memory usage.
+
+  The expressive power of Gremlin is proved in another recent work~\cite{yamaguchi}: the authors store C code information in Neo4j, and define recurring vulnerability patterns as Gremlin queries.
+Using this apporach, the authors discovered 18 previously unknown vulnerabilities in the Linux kernel.
 
@@
 
-Traditional compilers are designed around passes: the frontend passes parse source code into an intermediate representation (IR), midend passes transforms and adds new information to the IR, and the backend passes create target-specific object code from the IR~\cite{trad-compilers}.
-Modular compilers like P4C improve this design by structuring the passes into a library: backends assemble their own frontends and midends from a catalogue of passes provided by the compiler.
+Traditional compilers are designed around passes: the frontend passes parse source code into an intermediate representation (IR), midend passes transforms and adds new information to the IR, and the backend passes create target-specific object code from the IR.
+Modular compilers like P4C~\cite{p4c} improve this design by structuring the passes into a library: backends assemble their own frontends and midends from a catalogue of passes provided by the compiler.
 Moreover, P4C allows getting information from older states of the IR, as each transformation pass returns an immutable IR instance.
@@
 By \textit{supporting different applications} (or backends, in compiler parlance), we mean providing a comfortable way to to implement different end-users services, by reusing the same static code analysis operations.
-See Section~\ref{fig:apps} for a few examples of applications built on top of the <NAME>.
+See Section~\ref{sec:apps} for a few examples of applications built on top of the <NAME>.
 In systems with uniform APIs, programmers have to learn only one paradigm to maintain, extend or otherwise alter the system (e.g.
@@
 Figure~\ref{fig:arch-top} depicts how the architecture of <NAME> realizes uniform APIs by relying on a graph database. 
-Superficially, applications provide services to the user, by using the services provided by the infrastructure (see Section~\ref{fig:infra}).
+Superficially, applications provide services to the user, by using the services provided by the infrastructure (see Section~\ref{sec:infra}).
 In reality, both the infrastructure and applications operate on a large shared graph that collects all our knowledge about the program code.
@@
 to attach external loggers, visualisers, and validators).
-The information in the knowledge graph is accessed using graph queries written in Gremlin (see Section \ref{sec:gremlin}).
+The information in the knowledge graph is accessed using graph queries written in Gremlin.
 The implication is that users, application developers, and infrastructure developers are using one, uniform data structure, and are accessing it using the same mechanism.
@@
 
-	\subsection{Experts} % 1 hasáb - Dániel
+\paragraph{Gremlin API}
+In the tool architecture described in this section, we use a Gremlin graph database as storage backend (knowledge graph).
+Gremlin is a compositional query language and API that is implemented by many large-scale graph databases.
+This makes it possible to change graph implementations with almost no modification to the <NAME> code base.
+In earlier work~\cite{icai20}, we also profiled a few graph backends for control flow traverals, and verified that -- apart from the initial overhead -- in-memory graph databases have comparable performance to built-in memory manipulation.
+
+  Another consequence is that analysers have to be implemented as graph query workflows.
+By coarsely granularizing queries, most of the work can be delegated to the database, and with this, the choice of the workflow language (e.g.
+Java) can become negligible.
+In earlier work~\cite{macs20}, we experimented with implementing a whole control flow analysis as a single graph query: while having advantages, it can also hinder code maintainability as queries are often more difficult to read and modify.
+
+  \subsection{Infrastructure}\label{sec:infra} % 1 hasáb - Dániel
 	% kisebb gráf ábra
@@
 
-  \section{Evaluation} % ~ case studies?
+  \section{Case studies}\label{sec:apps} % ~ case studies?
 
@@
 	% egyedi elemzések mérése
+
+  In this section, we illustrate the viability of the platform by showcasing a few applications we are currently building on top of <NAME> in related research.
+
 	\subsection{Visualisation} % 0.5 hasáb
 
-  Since its function is the easiest to understand, the first application we introduce is graph visualisation.
+  Since it is the easiest to understand, the first application we introduce is graph visualisation.
 This application expects a list of analyser component names, executes them, and then, prints a subgraph of the knowledge graph containing only the domains of the analysers in the list.
-For example, to print the full version of the graph in Figure~\ref{fig:output}, we should run the following command:
-  \begin{lstlisting}[language=bash, basicstyle=\scriptsize]
-  $ <NAME> draw -A ControlFlow SymbolTable CallGraph CallSites AST
+For example, to print the full version of the graph in Figure~\ref{fig:output}, we should execute <NAME> with the following arguments:
+  \begin{lstlisting}[language=bash, basicstyle=\footnotesize]
+$ <NAME> draw example.p4 -A CFG SYMBOL CALL SITES AST 
 \end{lstlisting}
-  The subcommand \texttt{draw} tells <NAME> to run the visualiser, while \texttt{-A} is a flag (defined by the visualiser UI) expects the analyser names that will be passed to the visualiser application.
+The subcommand \texttt{draw} tells <NAME> to run the visualiser on the file \texttt{example.p4}, while \texttt{-A} is a flag (defined by the visualiser UI) expects the analyser names that will be passed to the visualiser application.
 

### 2021-03-22 publications/The_tool_intro/paper.tex
pub: removed macs20 citations

@@
 Java) can become negligible.
-In earlier work~\cite{macs20}, we experimented with implementing a whole control flow analysis as a single graph query: while having advantages, it can also hinder code maintainability as queries are often more difficult to read and modify.
+(Although in our experience large queries can hinder code maintainability as these are often more difficult to read and modify.)
+% In earlier work~\cite{macs20}, we experimented with implementing a whole control flow analysis as a single graph query: while having advantages, it can also hinder code maintainability as queries are often more difficult to read and modify.
 
@@
 For example, by following these edges, you can see how control flows from the \texttt{MyIngress} entry point through the conditional, terminating on the call of \texttt{ipv4\_lpm}.
-(For more information on how we implemented control flow analysis using Gremlin, see~\cite{macs20}.) The figure also partially includes domains of other analysers, such as \texttt{SYMBOL}.
+% (For more information on how we implemented control flow analysis using Gremlin, see~\cite{macs20}.) 
+The figure also partially includes domains of other analysers, such as \texttt{SYMBOL}.
 This analysers creates the graph-equivalent of a symbol table by identifying which declaration declares which name, and links usages of this name in the scope of the declaration to the declaration.

### 2021-03-23 publications/The_tool_intro/paper.tex
pub: add conclusion and modify verification

@@
 
-	\subsection{Similar tools}
-
 	%verification
@@
 
-	\subsection{Testing} % 1 hasáb - Gabi
-	There are two main goals with the testing: to test if the analyzes work well; and because it is a quite new tool, it will go through a lot of changes, therefore the possible spoils of the analyses during changes need to be detected.
+	\subsection{Testing}
+	There are two main goals with the testing: to test if the analysers work well; and because it is a quite new tool, it will go through a lot of changes, therefore the possible spoils of the analysers during changes need to be detected.
 This version of the tool contains unit tests and integration tests to check the functional correctness.
 
-	With the unit tests, our main goal is to check if the analyzes work well.
-Unit tests need to be fast, therefore they work with the smallest part of the analyses ie.
+	With the unit tests, our main goal is to check if the analysers work well.
+Unit tests need to be fast, therefore they work with smallest part of the analysers ie.
 their functions.
@@
 
-	While unit tests need to be fast, integration tests can be slower, so we can use P4 files as the inputs to test the analyzes.
-When one analysis needs to be tested, it uses the P4 file, and executes every analysis, that it is based on and the tests will check the result of this running.
-The tests are predefined, therefore we use a file to store the information of the tested sources and analysis -- which file tests which analyzes with which test classes.
+	While unit tests need to be fast, integration tests can be slower, so we can use P4 files as the inputs to test the analysers.
+When one analyser needs to be tested, it uses the P4 file, and executes every analyser, that it is based on and the tests will check the result of this running.
+The tests are predefined, therefore we use a file to store the information of the tested sources and analyser -- which file tests which analysers and with which test classes.
 
@@
 One of them executes all of the defined tests -- i.e.
-it goes through all of the P4 sources and executes the necessary analyzes and tests the their results -- which is useful to test the whole program and identify regression errors.
-The other focuses only one analysis and it is useful, when someone actually develop that analysis.
-This approach run only those tests which are relevant for the analysis.
+it goes through all of the P4 sources and executes the necessary analysers and tests the their results -- which is useful to test the whole program and identify regression errors.
+The other focuses only one analyser and it is useful, when someone actually develop that analyser.
+This approach run only those tests which are relevant for the analyser.
 
-	The architecture gives opportunity to insert the test as an application, which depends on all of the tested analyzes, but these are built into the maven.
-(TODO - ide még jöhetne talán részletessebben)
-
-	% külön modul
-	% elvi részei jelenlenek meg
-	% ilyen olyan teszt, messziről melyik hogy
-	% külön modul
-	% elvi részei jelenlenek meg
-	% ilyen olyan teszt, messziről melyik hogy
+	The architecture gives opportunity to insert the test as an application, which depends on all of the tested analysers, because it needs to test every analyser of the tool.
 
@@
 
-  The approach of the checking is defined in our previous paper \cite{ownCheck}, but shortly, it calculates the pre-and post-condition of the different blocks -- i.e the control apply functions, the tables and actions --, the parser and the deparser of the program and based on their results it can detect improper usage of the fields and headers.
+  The approach of the checking is defined in our previous paper \cite{ownCheck}, but shortly, it calculates the pre-and post-condition of the different blocks -- i.e the control apply functions, the tables and actions --, the parser and the deparser of the program, and based on these condition pairs it can detect improper usage of the fields and headers.
 Three types of cases can be detected: when there are some error cases in a block; when there is any inconsistency between the blocks; and when the need of the parser-deparser is inconsistent with the need of the control function.
@@
   In Figure \ref{code:cond}, there is an example condition for the MyIngress.
-We can see 4 pairs of conditions, because it has 4 possible execution paths - there are three when the condition of the branch is true, and the table executes one of the possible actions i.e.
-$\mathit{ipv4\_forward}$, $\mathit{drop}$ or $\mathit{NoAction}$, and one when the condition of the branch is false.
+We can see 4 pairs of conditions because it has 4 possible execution paths - there are three where the condition of the branch is true, and the table executes one of the possible actions i.e.
+$\mathit{ipv4\_forward}$, $\mathit{drop}$ or $\mathit{NoAction}$, and one where the condition of the branch is false.
 
@@
    This calculation is built into the tool as an application.
-It uses two experts: the call graph and control-flow graph.
-While traversing through the call graph it can reach calls of tables and actions.
-When it reaches a call, it starts to traverse through the proper subgraph of the control-flow graph and calculates the conditions of the actual block.
-Every condition is stored in the graph as a property of the called vertex of the call graph.
+It uses two experts: the call graph and the control-flow graph.
+While traversing backwards in the call graph it can reach actions and tables, which are called.
+Whenever it reaches a vertex like these, it starts to traverse through the proper subgraph of the control-flow graph and calculates the conditions of the actual block.
+Every condition is stored in the graph as a property of the called vertex of the call graph, therefore when the method reaches the actual call in the control-flow graph - for example a table is called in a control function - it can use the conditions of the called block, which have already been calculated.
+
    The implementation gets and saves every information about the program with Gremlin queries.
@@
 
-	\section{Conclusion and Future Work} % 1 hasáb - Máté
+	\section{Conclusion and Future Work}
 
-	  The goal of this paper is to introduce our analysis framework for P4 programs, which is based on a huge graph representation of the program.
-Analysis can be easily inserted into the tool, as an expert, which calculates the proper side information from the main syntax tree, and also stores this new information in it.
+	The goal of this paper is to introduce our static analysis framework for P4 programs, which uses a graph representation of the checked program.
+The tool is modular, therefore it can be extended with analysers to increase the possibilities of the program analysis.
+All of the analysers are based on the syntax tree of the examined P4 source and they extend it with new edges while creating new subgraphs -- like control-flow or call graph -- or new labels to store the calculated information.
 
 	So far, we have three main applications, which use some subgraph -- experts --, but we plan to increase these numbers and extend them.
-Two near future plans are the dependency graph and the def-use graph from which we could give some more useful information for the developers about their P4 source.
+As an example, two near-future plans are the dependency graph and the def-use graph from which we could give some more useful information for the developers about their P4 source.
 The dependency graph will contain the data and control dependencies between the statements, the def-use graph will show which fields are defined and used in which statements.
-Based on these analyzes we will be able to see more connection between the statements.
+Based on these analyses we will be able to see more connection between the statements.
 
-	% talán még cost-analysis? slicing? refactor? error correction?
-
-	Our major purpose to create a tool, which can facilitate and support the work of  P4 developers.
+	Our major purpose to create a tool, which can facilitate and support the work of  P4 developers while making the possibility to experiment with these programs.
+Its modular structure gives the opportunity for the user to avoid the usage of several tools for different analyses, although it makes the possibility to have all information in one place.
 

### 2021-03-23 publications/The_tool_intro/paper.tex
tool_intro:adding authors and acks

@@
 
-	\author{}
-	\email{}
+	\author{Dániel Lukács}
+	\email{dlukács@inf.elte.hu}
+	\orcid{0000-0001-9738-1134}
+	\affiliation{%
+		\institution{ELTE, Eötvös Loránd University, Faculty of Informatics}
+        \country{Hungary}
+        \city{Budapest}
+	}
+
+	\author{Gabriella Tóth}
+	\email{kistoth@inf.elte.hu}
 	\orcid{}
-	\author{}
-	\authornotemark[]
-	\email{}
 	\affiliation{%
-		\institution{}
-		\streetaddress{}
-		\city{}
-		\state{}
-		\country{}
-		\postcode{}
+		\institution{ELTE, Eötvös Loránd University, Faculty of Informatics}
+        \country{Hungary}
+        \city{Budapest}
+	}
+
+	\author{Máté Tejfel}
+	\email{matej@inf.elte.hu}
+	\orcid{0000-0001-8982-1398}
+	\affiliation{%
+		\institution{ELTE, Eötvös Loránd University, Faculty of Informatics}
+        \country{Hungary}
+        \city{Budapest}
 	}
@@
 
-	\keywords{TODO}
+	\keywords{P4 language, static analysis, analysis framework}
 
@@
 
+\begin{acks}
+The research has been supported by the European Union, co-financed by the European Social Fund 
+(EFOP-3.6.3-VEKOP-16-2017-00002). M. Tejfel also thanks the support of the project
+"Application Domain Specific Highly Reliable IT Solutions" implemented with the support of the NRDI Fund
+of Hungary, financed under the Thematic Excellence Programme TKP2020-NKA-06 (National Challenges Subprogramme) funding scheme.
+\end{acks}
+
 \bibliographystyle{ACM-Reference-Format}

### 2021-03-23 publications/The_tool_intro/paper.tex
pub: add orcid
pub: 6 page, captions

@@
 	\section{Analysis framework}
-
 Traditional compilers are designed around passes: the frontend passes parse source code into an intermediate representation (IR), midend passes transforms and adds new information to the IR, and the backend passes create target-specific object code from the IR.
-Modular compilers like P4C~\cite{p4c} improve this design by structuring the passes into a library: backends assemble their own frontends and midends from a catalogue of passes provided by the compiler.
+Modular compilers like the P4 reference compiler P4C\footnote{\url{https://github.com/p4lang/p4c}} improve this design by structuring the passes into a library: backends assemble their own frontends and midends from a catalogue of passes provided by the compiler.
 Moreover, P4C allows getting information from older states of the IR, as each transformation pass returns an immutable IR instance.
@@
 
-\subsection{Representation - Architecture}\label{sec:rep} % 4 hasáb - Dániel
+\clearpage
+
+\subsection{Tool architecture}\label{sec:rep} % 4 hasáb - Dániel
 	% belső gráf, a koncepció
@@
     \includegraphics[width=0.18\textwidth]{figures/arch-top.pdf}
-    \caption{TODO}\label{fig:arch-top}
+    \caption{High-level view of the tool architecture}\label{fig:arch-top}
   \end{figure}
@@
     \includegraphics[width=0.3\textwidth]{figures/arch-deps.pdf}
-    \caption{TODO}\label{fig:arch-deps}
+    \caption{Expanded view of the architecture layers}\label{fig:arch-deps}
   \end{figure}
@@
   \begin{figure}
-    \includegraphics[width=0.45\textwidth]{figures/output.pdf}
-    \caption{TODO}\label{fig:output}
+    \includegraphics[width=0.42\textwidth]{figures/output.pdf}
+    \caption{Knowledge graph excerpt of the Figure~\ref{code:P4} code}\label{fig:output}
   \end{figure}

### 2021-03-23 publications/The_tool_intro/paper.tex
pub: change conclusion

@@
 	\email{kistoth@inf.elte.hu}
-	\orcid{}
+	\orcid{0000-0001-9657-7231}
 	\affiliation{%
@@
 
+	Our major purpose to create a tool, which can facilitate and support the work of  P4 developers while making the possibility to experiment with these programs.
+Its modular structure gives the opportunity for the user to avoid the usage of several tools for different analyses, although it makes the possibility to have all information in one place.
+
 	The goal of this paper is to introduce our static analysis framework for P4 programs, which uses a graph representation of the checked program.
-The tool is modular, therefore it can be extended with analysers to increase the possibilities of the program analysis.
 All of the analysers are based on the syntax tree of the examined P4 source and they extend it with new edges while creating new subgraphs -- like control-flow or call graph -- or new labels to store the calculated information.
 
-	So far, we have three main applications, which use some subgraph -- experts --, but we plan to increase these numbers and extend them.
-As an example, two near-future plans are the dependency graph and the def-use graph from which we could give some more useful information for the developers about their P4 source.
-The dependency graph will contain the data and control dependencies between the statements, the def-use graph will show which fields are defined and used in which statements.
-Based on these analyses we will be able to see more connection between the statements.
-
-	Our major purpose to create a tool, which can facilitate and support the work of  P4 developers while making the possibility to experiment with these programs.
-Its modular structure gives the opportunity for the user to avoid the usage of several tools for different analyses, although it makes the possibility to have all information in one place.
+	In the future, we would like to extend the tool with new analyses to give some other useful information for the developers about their P4 source.
+Our nearest idea is to supplement it with the dependency graph and def-use graph with which we will be able to give report, which are based on the connection between the statements.
 

### 2021-03-23 publications/The_tool_intro/paper.tex
pub: add name

@@
 
-	\title{<NAME> - an analyser framework for P4}
+	\title{P4Query - an analyser framework for P4}
 
@@
 describing the data plane layer of packet processing algorithms. It has several uncommon language elements and concepts often make analysis of P4 programs a laborious task. 
-The paper presents <NAME>, a generic analysis framework for P4 makes possible development of different P4 related analysis methods in a generic and modular way.
+The paper presents P4Query, a generic analysis framework for P4 makes possible development of different P4 related analysis methods in a generic and modular way.
 The framework uses an integral graph representation which contains the results of applied analysis methods too.
@@
 By \textit{supporting different applications} (or backends, in compiler parlance), we mean providing a comfortable way to to implement different end-users services, by reusing the same static code analysis operations.
-See Section~\ref{sec:apps} for a few examples of applications built on top of the <NAME>.
+See Section~\ref{sec:apps} for a few examples of applications built on top of the P4Query.
 In systems with uniform APIs, programmers have to learn only one paradigm to maintain, extend or otherwise alter the system (e.g.
@@
 
-Figure~\ref{fig:arch-top} depicts how the architecture of <NAME> realizes uniform APIs by relying on a graph database. 
+Figure~\ref{fig:arch-top} depicts how the architecture of P4Query realizes uniform APIs by relying on a graph database. 
 Superficially, applications provide services to the user, by using the services provided by the infrastructure (see Section~\ref{sec:infra}).
@@
 Gremlin is a compositional query language and API that is implemented by many large-scale graph databases.
-This makes it possible to change graph implementations with almost no modification to the <NAME> code base.
+This makes it possible to change graph implementations with almost no modification to the P4Query code base.
 In earlier work~\cite{icai20}, we also profiled a few graph backends for control flow traverals, and verified that -- apart from the initial overhead -- in-memory graph databases have comparable performance to built-in memory manipulation.
@@
 	% kisebb gráf ábra
-  As we see earlier in Figure~\ref{fig:arch-deps}, the heavy-lifting in <NAME> is done by various code analyser components, each adding new information about the P4 code to the knowledge graph using what is already there.
+  As we see earlier in Figure~\ref{fig:arch-deps}, the heavy-lifting in P4Query is done by various code analyser components, each adding new information about the P4 code to the knowledge graph using what is already there.
 We now introduce a few analyser modules using an example: Figure~\ref{fig:output} depicts a small subset of the knowledge graph taken after we executed control flow analysis, call analysis, and call sites analysis on the P4 code in Figure~\ref{code:P4} (specifically the \texttt{MyIngress} control).
@@
 
-  In this section, we illustrate the viability of the platform by showcasing a few applications we are currently building on top of <NAME> in related research.
+  In this section, we illustrate the viability of the platform by showcasing a few applications we are currently building on top of P4Query in related research.
 
@@
 This application expects a list of analyser component names, executes them, and then, prints a subgraph of the knowledge graph containing only the domains of the analysers in the list.
-For example, to print the full version of the graph in Figure~\ref{fig:output}, we should execute <NAME> with the following arguments:
+For example, to print the full version of the graph in Figure~\ref{fig:output}, we should execute P4Query with the following arguments:
   \begin{lstlisting}[language=bash, basicstyle=\footnotesize]
-$ <NAME> draw example.p4 -A CFG SYMBOL CALL SITES AST 
+$ p4query draw example.p4 -A CFG SYMBOL CALL SITES AST 
 \end{lstlisting}
-The subcommand \texttt{draw} tells <NAME> to run the visualiser on the file \texttt{example.p4}, while \texttt{-A} is a flag (defined by the visualiser UI) expects the analyser names that will be passed to the visualiser application.
+The subcommand \texttt{draw} tells P4Query to run the visualiser on the file \texttt{example.p4}, while \texttt{-A} is a flag (defined by the visualiser UI) expects the analyser names that will be passed to the visualiser application.
 
-  A possibly interesting implementation detail here is that the visualiser technically depends on \textit{all} the analysers defined in <NAME>, since it must be able to visualise anything the user may pass.
+  A possibly interesting implementation detail here is that the visualiser technically depends on \textit{all} the analysers defined in P4Query, since it must be able to visualise anything the user may pass.
 Yet, we still managed to avoid executing those that are not requested by the user (and not dependencies of the requested ones): we implemented dependency resolution in the controller using Java dependency injection (DI), and DI offers lazy initialization of the dependencies.
@@
   From this, it follows that part of the static cost analysis problem reduces to a compilation-and-linking problem.
-As an experiment, we implemented a compiler to solve this problem as an application in <NAME>.
-The main reason we chose <NAME>, instead of the much more mature P4C compiler framework was that at first we did not know what kind of representation or code we will need to output: the control and extensibility provided by <NAME> and Gremlin queries gave us tools to experiment and create quick, recyclable prototypes to help us arrive at a final vision.
+As an experiment, we implemented a compiler to solve this problem as an application in P4Query.
+The main reason we chose P4Query, instead of the much more mature P4C compiler framework was that at first we did not know what kind of representation or code we will need to output: the control and extensibility provided by P4Query and Gremlin queries gave us tools to experiment and create quick, recyclable prototypes to help us arrive at a final vision.
 While P4C's safety mechanisms (e.g.
@@
 
-  The compiler is built on top of the control flow analyser in <NAME>: we traverse the CFG, and process each node by traversing the syntax tree under the node.
+  The compiler is built on top of the control flow analyser in P4Query: we traverse the CFG, and process each node by traversing the syntax tree under the node.
 We also use the call graph to find which label to jump to when a function is called.

### 2021-03-23 publications/The_tool_intro/paper.tex
tool_intro:adding github link
pub: conclusion

@@
 
-	The paper describes an analysis framework for P4.
+	The paper describes an analysis framework for P4~\footnote{The code is available from: \url{https://github.com/P4ELTE/P4Query}}.
 The framework makes possible development of different P4 related analysis methods in a generic and modular way.
@@
 
-	The goal of this paper is to introduce our static analysis framework for P4 programs, which uses a graph representation of the checked program.
+	The framework uses a graph representation of the investigated program.
 All of the analysers are based on the syntax tree of the examined P4 source and they extend it with new edges while creating new subgraphs -- like control-flow or call graph -- or new labels to store the calculated information.

### 2021-03-23 broker/src/main/java/p4analyser/broker/App.java
v1a: refactored broker (broke tests/BaseIT)

@@ -26,90 +26,103 @@ import java.util.Collection;
 import java.util.HashMap;
 import java.util.Map;
 import java.util.Set;
-import java.util.concurrent.ExecutionException;
-import java.util.concurrent.TimeoutException;
 import java.util.stream.Collectors;
 
-import com.beust.jcommander.JCommander;
 import com.thoughtworks.xstream.XStream;
 
 import org.codejargon.feather.Feather;
 import org.codejargon.feather.Key;
 import org.reflections.Reflections;
-import org.reflections.ReflectionsException;
 import org.reflections.scanners.MethodAnnotationsScanner;
 
-import p4analyser.ontology.Status;
-import p4analyser.ontology.analyses.AbstractSyntaxTree;
-import p4analyser.ontology.analyses.ControlFlow;
+import p4analyser.ontology.IllegalUserInputException;
 import p4analyser.ontology.providers.AppUI;
 import p4analyser.ontology.providers.Application;
 
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
 
-import org.apache.commons.configuration.Configuration;
-import org.apache.commons.configuration.ConfigurationException;
-import org.apache.commons.configuration.PropertiesConfiguration;
-
 public class App {
 
-    // private static final List<Class<? extends Annotation>> analyses =
-    // Arrays.asList(SyntaxTree.class);
+    // used for default includes and input file
+    public static final String CORE_P4_PATH = "core.p4";
+    public static final String V1MODEL_P4_PATH = "v1model.p4";
+    public static final String BASIC_P4_PATH = "basic.p4";
 
+    // used for implementation discovery
     private static final String EXPERTS_PACKAGE = "p4analyser.experts";
     private static final String APPLICATIONS_PACKAGE = "p4analyser.applications";
     private static final String ANALYSES_PACKAGE = "p4analyser.ontology.analyses";
 
     // TODO a white list would be better
-    // NOTE: before you extend this list with your class, check out the --readonly option
+    // NOTE: before you extend this list with your class, check out the --readonly
+    // option
     private static final Collection<Class<?>> DO_NOT_SERIALIZE = Arrays.asList(GraphTraversalSource.class);
 
-    private static final ClassLoader loader = Thread.currentThread().getContextClassLoader();
-    private static String GREMLIN_CLIENT_CONF_PATH;
+    private final Map<Class<? extends Annotation>, Object> analysers;
[…]

### 2021-03-23 broker/src/main/java/p4analyser/broker/CLIArgsProvider.java

@@ -1,26 +1,138 @@
 package p4analyser.broker;
 
+import java.io.File;
+import java.io.IOException;
+import java.nio.file.Paths;
+import java.util.Map;
+
 import javax.inject.Singleton;
+
+import com.beust.jcommander.JCommander;
 
 import org.codejargon.feather.Provides;
 
+import p4analyser.ontology.IllegalUserInputException;
 import p4analyser.ontology.providers.AppUI;
+import p4analyser.ontology.providers.Application;
 import p4analyser.ontology.providers.CLIArgs;
 
 public class CLIArgsProvider {
 
-    public final AppUI args;
 
-    public CLIArgsProvider(AppUI args) {
-        this.args = args;
+    private final Application invokedApp;
+    private String usage;
+    private String commandName;
+
+    CLIArgsProvider(String[] args, Map<String, Application> appRegistry, String defaultP4File) throws IllegalUserInputException, IOException{
+
+        parseArgs(args, appRegistry);
+
+        if (commandName == null) {
+            throw new IllegalArgumentException(
+                    "Please, provide a command argument." + System.lineSeparator() + usage);
+        }
+
+        this.invokedApp = appRegistry.get(commandName);
+
+        AppUI ui = invokedApp.getUI();
+
+        if (ui.help) {
+            throw new IllegalUserInputException(usage);
+        }
+
+        String actualP4FilePath = ensureP4FileOrDefault(ui.p4FilePath, defaultP4File);
+
+        String actualDbPath = null;
+        if (ui.databaseLocation != null) {
+            if(ui.reset && ui.readonly){
+               throw new IllegalUserInputException(
+                        "--reset and -- readonly are conflicting options, use at most one.");
+            }
+
+            actualDbPath = 
+                ensurePersistingDirectoryExists(ui.databaseLocation, actualP4FilePath);
+        }
+
+        ui.init(actualDbPath, actualP4FilePath);
     }
 
-    
+    private void parseArgs(String[] args, Map<String, Application> appRegistry) {
+        JCommander.Builder jcb = JCommander.newBuilder();
+
+        for (Application app : appRegistry.values()) {
+            AppUI cmd = app.getUI();
+            String cmdName = cmd.getCommandName();
+            String[] aliases = cmd.getCommandNameAliases();
+
+            jcb.addCommand(cmdName, cmd, aliases);
+        }
+
+        JCommander jc = jcb.build();
+        jc.parse(args);
+
+        StringBuilder sb = new StringBuilder();
[…]

### 2021-03-23 broker/src/main/java/p4analyser/broker/LocalGremlinServer.java

@@ -174,4 +174,30 @@ public class LocalGremlinServer {
         return f.getAbsolutePath();
     }
 
+// NOTE AnonymousTraversal accepts method parameters so this configuration file is not used currently. Leaving this here for future reference.
+//    
+//   import org.apache.commons.configuration.Configuration;
+//   import org.apache.commons.configuration.ConfigurationException;
+//   import org.apache.commons.configuration.PropertiesConfiguration;
+
+//   private static Configuration updateClientConfig() {
+//     GREMLIN_CLIENT_CONF_PATH = contentsToTempFile(
+//         loader.getResourceAsStream("conf/remote-graph.properties"), "conf/remote-graph.properties");
+//       Configuration c;
+//       try {
+//           c = new PropertiesConfiguration(GREMLIN_CLIENT_CONF_PATH);
+//       } catch (ConfigurationException e) {
+//           throw new IllegalStateException(
+//                   String.format(
+//                       "Error parsing Gremlin client file at %s:", 
+//                       GREMLIN_CLIENT_CONF_PATH),
+//                   e);
+//       }
+//
+//    // NOTE Unlike with YAML, we can use "classpath:" notation in .properties files, so it turned out we don't need this:
+//    private static String GREMLIN_CLIENT_CONF_PATH;
+//    // c.setProperty("gremlin.remote.driver.clusterFile", GREMLIN_CLIENT_CONF_CLUSTERFILE_PATH);
+//
+//       return c;
+//   }
 }

### 2021-03-23 broker/src/main/java/p4analyser/broker/LocalGremlinServerException.java

@@ -5,6 +5,7 @@
 package p4analyser.broker;
 
 public class LocalGremlinServerException extends Exception {
+    private static final long serialVersionUID = 1L;
 
     public LocalGremlinServerException(String message) {
         super(message);

### 2021-03-23 ontology/src/main/java/p4analyser/ontology/IllegalUserInputException.java

@@ -1,0 +1,19 @@
+package p4analyser.ontology;
+
+public class IllegalUserInputException extends Exception {
+   private boolean error;
+
+   public IllegalUserInputException(Throwable t){
+      super(t);
+   }
+
+   public IllegalUserInputException(String msg){
+        super(msg);
+        this.error = error;
+   }
+
+   public boolean isError() {
+      return error;
+   }
+    
+}

### 2021-03-23 ontology/src/main/java/p4analyser/ontology/providers/AppUI.java

@@ -12,8 +12,12 @@ import com.beust.jcommander.ParameterException;
 
 public abstract class AppUI {
 
+    private String actualDbLocation;
+    private String actualP4FilePath;
+
     abstract public String getCommandName(); 
     abstract public String[] getCommandNameAliases(); 
+
 
     @Parameter(description = "<location of P4 file to be analysed>" /* , required = true  */)
     public String p4FilePath;
@@ -33,6 +37,23 @@ public abstract class AppUI {
 
     @Parameter(names="--misc", description = "(For developers) Arbitrary list of strings that can be read by some of the analysers for development and testing purposes." /* , required = true  */)
     public List<String> misc;
+
+    public void init(String actualDatabaseLocation, String actualP4FilePath){
+        this.actualDbLocation = actualDatabaseLocation;
+        this.actualP4FilePath = actualP4FilePath;
+    }
+
+    public String getActualDbLocation() {
+        if(actualDbLocation == null && databaseLocation != null)
+            throw new IllegalAccessError(AppUI.class + " should have been initialized, and with non-null values.");
+        return actualDbLocation;
+    }
+
+    public String getActualP4FilePath() {
+        if(actualP4FilePath == null)
+            throw new IllegalAccessError(AppUI.class + " should have been initialized, and with non-null values.");
+        return actualP4FilePath;
+    }
 
     public static class OptionCannotBeValueValidator implements IParameterValidator {
         public void validate(String name, String value)

### 2021-03-26 publications/The_tool_intro/paper.tex
pub: title
pub: removed accent from email
tool_intro: some typo

@@
 
-	\title{P4Query - an analyser framework for P4}
+	\title{P4Query: Static Analyser Framework for P4}
 
 	\author{Dániel Lukács}
-	\email{dlukács@inf.elte.hu}
+	\email{dlukacs@inf.elte.hu}
 	\orcid{0000-0001-9738-1134}
@@
   The expressive power of Gremlin is proved in another recent work~\cite{yamaguchi}: the authors store C code information in Neo4j, and define recurring vulnerability patterns as Gremlin queries.
-Using this apporach, the authors discovered 18 previously unknown vulnerabilities in the Linux kernel.
+Using this approach, the authors discovered 18 previously unknown vulnerabilities in the Linux kernel.
 
@@
 This makes it possible to change graph implementations with almost no modification to the P4Query code base.
-In earlier work~\cite{icai20}, we also profiled a few graph backends for control flow traverals, and verified that -- apart from the initial overhead -- in-memory graph databases have comparable performance to built-in memory manipulation.
+In earlier work~\cite{icai20}, we also profiled a few graph backends for control flow traversals, and verified that -- apart from the initial overhead -- in-memory graph databases have comparable performance to built-in memory manipulation.
 

### 2021-03-26 publications/The_tool_intro/paper.tex
too_intro: some minor changes

@@
 The paper presents P4Query, a generic analysis framework for P4 makes possible development of different P4 related analysis methods in a generic and modular way.
-The framework uses an integral graph representation which contains the results of applied analysis methods too.
-This way the framework supports rapid implementation of new analysis methods in a way where the results will be also easily reusable by other methods.
+The framework uses an internal graph representation which contains the abstract syntax tree of the analysed program and the results of applied analysis methods too.
+The framework supports rapid implementation of new analysis methods in a way where the results will be also easily reusable by other methods.
 
@@
 
-	Comparing these approaches this paper presents a generic framework make possible to implement several analyses methods which can use each other's results as well.
-
+	Comparing these approaches this paper presents a generic framework make possible to implement several analyses methods using a common basis.
 A major inspiration for this work was RefactorErl~\cite{referl}, a static analysis tool for Erlang.
@@
 
+  For the manipulation of the internal graph representation we use the Gremlin language.
 The expressive power of Gremlin is proved in another recent work~\cite{yamaguchi}: the authors store C code information in Neo4j, and define recurring vulnerability patterns as Gremlin queries.
@@
 However for a real execution also a corresponding control plane layer is needed, which part is more or less a black hole while we consider only the P4 source code.
-Because of these testing, verification and generally functional and non-functional analysis of P4 programs are non trivial tasks sometimes requiring language specific techniques.
+Because of these testing, verification and generally functional and non-functional analysis of P4 programs are non trivial tasks which sometimes require language specific techniques.
 
@@
 This paper presents a framework allows the implementation of different analysis methods using a common basis.
-The framework applies an extensible integral graph representation where the results of the different analysis methods are represented also as part of the graph.
+The framework applies an extensible internal graph representation where the results of the different analysis methods are represented also as part of the graph.
 This makes possible execution of different methods in a hierarchical order where methods can use the results (or some part of the results) of previously applied methods.
@@
 One goal of the experiment we present here is to relax the three-fold structure and allow passes to reuse (depend on) each other's functionally arbitrarily, and without burdening the compiler programmer with manually finding the right sequence in which to execute these dependencies.
-
-\clearpage
 

### 2021-03-27 publications/The_tool_intro/paper.tex
tool_intro: minor changes

@@
 
-By \textit{supporting different applications} (or backends, in compiler parlance), we mean providing a comfortable way to to implement different end-users services, by reusing the same static code analysis operations.
+By \textit{supporting different applications} (or backends, in compiler parlance), we mean providing a comfortable way to implement different end-users services, by reusing the same static code analysis operations.
 See Section~\ref{sec:apps} for a few examples of applications built on top of the P4Query.
@@
 Our second design goal, \textit{ease of extensibility} is illustrated by Figure~\ref{fig:arch-deps}, that elaborates the application and infrastructure layers. 
-This arrangement was inspired by declarative build systems and the blackboard pattern used in distributed MI.
+This arrangement was inspired by declarative build systems and the blackboard pattern used in distributed AI.
 

### 2021-03-28 publications/The_tool_intro/paper.tex
pub: typos

@@
 		There are many important tasks in a conventional software development process which can be supported by different analysis techniques. P4 is a high level domain specific language for
-describing the data plane layer of packet processing algorithms. It has several uncommon language elements and concepts often make analysis of P4 programs a laborious task. 
-The paper presents P4Query, a generic analysis framework for P4 makes possible development of different P4 related analysis methods in a generic and modular way.
+    describing the data plane layer of packet processing algorithms. It has several uncommon language elements and concepts that often make analysis of P4 programs a laborious task. 
+    The paper presents P4Query, a generic analysis framework for P4 that makes it possible to develop different P4 related analysis methods in a generic and modular way.
 The framework uses an internal graph representation which contains the abstract syntax tree of the analysed program and the results of applied analysis methods too.
@@
 execution time estimation) analysis.
-These analysis can be especially interesting in the case of languages having uncommon language constructs or language structures e.g.
+These analyses can be especially interesting in the case of languages having uncommon language constructs or language structures e.g.
 in the case of some domain specific languages.
@@
 Figure~\ref{code:P4} illustrates a P4 program.
-The program first defines the applied header structure, than the parser part describes how the fields of the defined headers will be set from the input bit stream (input packet).
-Controller part can modify values of fields of headers and metadata by applying lookup tables.
-The data plane program describes the structure of the tables, the key fields based on that lookups will be executed and the possible results of the lookups, namely the applicable actions.
+The program first defines the applied header structure, than the \texttt{parser} part describes how the fields of the defined headers will be set from the input bit stream (input packet).
+\texttt{control} parts can modify values of fields of headers and metadata by applying lookup tables.
+The data plane program describes the structure of the tables, the key fields on which lookups will be executed and the possible results of the lookups, namely the applicable actions.
 However concrete data of the tables (which actions will be executed with which parameters for which key values) are defined by the control plane program, therefore it will not appear in P4.
@@
 The paper describes an analysis framework for P4~\footnote{The code is available from: \url{https://github.com/P4ELTE/P4Query}}.
-The framework makes possible development of different P4 related analysis methods in a generic and modular way.
+The framework makes it possible to develop different P4 related analysis methods in a generic and modular way.
 It uses an internal graph representation where the results of the methods are also represented as part of the graph (mainly by adding new edges to the graph).
 In this way the methods can use each other's results as well.
-The proposed tool makes also possible to create rapid, prototype implementation of different analysis concepts using a common toolset.
+The proposed tool also makes it possible to create rapid, prototype implementation of different analysis concepts using a common tool set.
 
@@
 
-	Considering related work there are many research applying specific analysis technics for P4.
+  There is already much research on applying specific analysis techniques for P4.
 Most of them concentrate on error checking of P4 programs.
@@
 BF4 \cite{bf4} is created as a p4c backend, which can not only detect error possibilities, but it is able to repair them by adding new keys to the table and modify the table contents.
-An other tool p4-data-flow \cite{p4dataflow} uses data flow analysis to detect potential bugs in P4 switch codes.
+Another tool, p4-data-flow \cite{p4dataflow} uses data flow analysis to detect potential bugs in P4 switch codes.
 
-	Some other tools uses analysis methods for different purposes.
-For example p4pktgen \cite{p4pktgen} uses symbolic execution for automatically generating test cases.
-Flightplan \cite{flightplan} can splits a P4 program into a set of cooperating P4 programs and maps them to run as a distributed system formed of several, possibly heterogeneous, dataplanes.
-During this process they use several analysis technics, for example to gather variables whose values must be transfer between dataplanes.
+  Some other tools use analysis methods for different purposes.
+For example, p4pktgen \cite{p4pktgen} uses symbolic execution for automatically generating test cases.
+Flightplan \cite{flightplan} can split a P4 program into a set of cooperating P4 programs and maps them to run as a distributed system formed of several, possibly heterogeneous, dataplanes.
+During this process they use several analysis techniques, for example to gather variables whose values must be transferred between data planes.
 
-	Comparing these approaches this paper presents a generic framework make possible to implement several analyses methods using a common basis.
+  Comparing these approaches this paper presents a generic framework to make it possible to implement several analyses methods using a common basis.
 A major inspiration for this work was RefactorErl~\cite{referl}, a static analysis tool for Erlang.
-RefactorErl stores program information in a graph called the Semantic Program Graph using relation databases, and hosts in own query language for exploring the stored information.
-Many features in our work -- such as using graph databases and their built-in query languages instead of in-house solutions -- can be considered to be the streamlining of best practices found in RefactorErl.
+RefactorErl stores program information in a graph called the Semantic Program Graph using relational databases, and hosts its own query language for exploring the stored information.
+Many features in our work -- such as using graph databases and graph query languages instead of in-house solutions -- can be considered to be the streamlining of best practices found in RefactorErl.
 
@@
 ProgQuery \cite{java-static} is a similar static analysis tool for Java, built on Neo4j and its Cypher query language.
-The authors emphasize that using Neo4j yielded substantial improvements in analysis time and memory usage.
+The authors emphasise that using Neo4j yielded substantial improvements in analysis time and memory usage.
+In fact, the name of our own tool was patterned after ProgQuery.
 
-  For the manipulation of the internal graph representation we use the Gremlin language.
+  One design goal of our tool is to welcome Gremlin-based static analysis applications for P4.
 The expressive power of Gremlin is proved in another recent work~\cite{yamaguchi}: the authors store C code information in Neo4j, and define recurring vulnerability patterns as Gremlin queries.
 Using this approach, the authors discovered 18 previously unknown vulnerabilities in the Linux kernel.
-
   %graph-based
@@
   % - Reverse Engineering State and Strategy Design Patterns using Static Code Analysis: https://thesai.org/Downloads/Volume9No1/Paper_78-Reverse_Engineering_State_and_Strategy_Design_Patterns.pdf
-
 	\section{Motivation}
@@
 	% ehhez egységes keretrendszer - vannak már ilyesmik related workben
-
+  %
   %% p4c is a factory. this tool is a laboratory. 
-
+  %
 P4 is a relatively new, domain specific language having some uncommon language elements (for example match-action tables).
@@
 
-Section~\ref{sec:related} introduces several applications using different analysis methods for P4.
+Section~\ref{sec:apps} introduces several applications using different analysis methods for P4.
 The authors also have some earlier results for determining potentially erroneous code parts~\cite{ownCheck} and for predicting execution cost~\cite{LukacsOcs} of P4 programs.
@@
 
-This paper presents a framework allows the implementation of different analysis methods using a common basis.
+This paper presents a framework that allows the implementation of different analysis methods using a common basis.
 The framework applies an extensible internal graph representation where the results of the different analysis methods are represented also as part of the graph.
-This makes possible execution of different methods in a hierarchical order where methods can use the results (or some part of the results) of previously applied methods.
-
+This makes it possible to execute different methods in a hierarchical order where methods can use the results (or some part of the results) of previously applied methods.
 The framework supports rapid implementation of new analysis methods applicable for P4 language in a way where results of the methods will be easily reusable.
@@
 	\section{Analysis framework}
-Traditional compilers are designed around passes: the frontend passes parse source code into an intermediate representation (IR), midend passes transforms and adds new information to the IR, and the backend passes create target-specific object code from the IR.
+Traditional compilers are designed around passes: the frontend passes parse source code into an intermediate representation (IR), midend passes transform and add new information to the IR, and the backend passes create target-specific object code from the IR.
 Modular compilers like the P4 reference compiler P4C\footnote{\url{https://github.com/p4lang/p4c}} improve this design by structuring the passes into a library: backends assemble their own frontends and midends from a catalogue of passes provided by the compiler.
@@
 
-Figure~\ref{fig:arch-top} depicts how the architecture of P4Query realizes uniform APIs by relying on a graph database. 
+Figure~\ref{fig:arch-top} depicts how the architecture of P4Query realises uniform APIs by relying on a graph database. 
 Superficially, applications provide services to the user, by using the services provided by the infrastructure (see Section~\ref{sec:infra}).
@@
   Another consequence is that analysers have to be implemented as graph query workflows.
-By coarsely granularizing queries, most of the work can be delegated to the database, and with this, the choice of the workflow language (e.g.
+By coarsely granularising queries, most of the work can be delegated to the database, and with this, the choice of the workflow language (e.g.
 Java) can become negligible.
@@
 % In earlier work~\cite{macs20}, we experimented with implementing a whole control flow analysis as a single graph query: while having advantages, it can also hinder code maintainability as queries are often more difficult to read and modify.
-
   \subsection{Infrastructure}\label{sec:infra} % 1 hasáb - Dániel
@@
 This application expects a list of analyser component names, executes them, and then, prints a subgraph of the knowledge graph containing only the domains of the analysers in the list.
-For example, to print the full version of the graph in Figure~\ref{fig:output}, we should execute P4Query with the following arguments:
+For example, to print the full version of the graph in Figure~\ref{fig:output}, we would execute P4Query with the following arguments:
   \begin{lstlisting}[language=bash, basicstyle=\footnotesize]
@@
 Yet, we still managed to avoid executing those that are not requested by the user (and not dependencies of the requested ones): we implemented dependency resolution in the controller using Java dependency injection (DI), and DI offers lazy initialization of the dependencies.
-This way we can filter the analysers and only initialize those that were requested by the user.
+This way we can filter the analysers and only initialise those that were requested by the user.
 
@@
   Verification is a possible extension of the tool, which is added to it as an application.
-The main focus is to detect errors and suspicious cases, which can be caused by the usage of invalid header or uninitialized fields.
+The main focus is to detect errors and suspicious cases, which can be caused by the usage of invalid header or uninitialised fields.
 The goal of this detection is to report these usages for the developer to avoid undefined behaviour in the programs.
 
-  The approach of the checking is defined in our previous paper \cite{ownCheck}, but shortly, it calculates the pre-and post-condition of the different blocks -- i.e the control apply functions, the tables and actions --, the parser and the deparser of the program, and based on these condition pairs it can detect improper usage of the fields and headers.
-Three types of cases can be detected: when there are some error cases in a block; when there is any inconsistency between the blocks; and when the need of the parser-deparser is inconsistent with the need of the control function.
+  The approach of the checking is defined in our previous paper \cite{ownCheck}, but in short, it calculates the pre- and post-condition of the various blocks -- i.e the control apply functions, the tables and actions --, the parser and the deparser of the program.
+Based on these condition pairs it can detect improper usage of the fields and headers.
+Three types of cases can be detected: when there are some error cases in a block; when there is any inconsistency between the blocks; and when the need of the parser and deparser is inconsistent with the need of the control function.
 
@@
   This calculation is built into the tool as an application.
-It uses two experts: the call graph and the control-flow graph.
+It uses two analysers: the call graph and the control flow graph.
 While traversing backwards in the call graph it can reach actions and tables, which are called.
-Whenever it reaches a vertex like these, it starts to traverse through the proper subgraph of the control-flow graph and calculates the conditions of the actual block.
-Every condition is stored in the graph as a property of the called vertex of the call graph, therefore when the method reaches the actual call in the control-flow graph - for example a table is called in a control function - it can use the conditions of the called block, which have already been calculated.
+Whenever it reaches a vertex like these, it starts to traverse through the proper subgraph of the control flow graph and calculates the conditions of the actual block.
+Every condition is stored in the graph as a property of the called vertex of the call graph, therefore when the method reaches the actual call in the control flow graph -- for example when a table is called in a control function -- it can use the conditions of the called block, which have already been calculated.
 
@@
 
-	Our major purpose to create a tool, which can facilitate and support the work of  P4 developers while making the possibility to experiment with these programs.
-Its modular structure gives the opportunity for the user to avoid the usage of several tools for different analyses, although it makes the possibility to have all information in one place.
+  Our major purpose was to create a tool, which can facilitate and support the work of P4 developers while making the possibility to experiment with these programs.
+Its modular structure gives the opportunity for the user to avoid the usage of several tools for different analyses, as it makes it possible to have all information in one place.
 
 	The framework uses a graph representation of the investigated program.
-All of the analysers are based on the syntax tree of the examined P4 source and they extend it with new edges while creating new subgraphs -- like control-flow or call graph -- or new labels to store the calculated information.
+All of the analysers are based on the syntax tree of the examined P4 source and they extend it with new edges while creating new subgraphs -- like control flow or call graph -- or new labels to store the calculated information.
 
@@
 Our nearest idea is to supplement it with the dependency graph and def-use graph with which we will be able to give report, which are based on the connection between the statements.
+
+%% future work: like in traditional compilers, parallelizing analysers. graph is shared data. 
+%% On one hand, the architecture supports parallelization by requiring analysers to explicitly state their dependencies and provided services, enabling us to easily select which analyers to execute parallely (the independent ones).
+On the other hand, the architecture does not conceptualise the *effects* caused by analysers.
+An analyser can alter the graph in such a way that causes some other -- theoretically indepedent -- analyser to take an unexpected route, leading to wrong results.
+Such an implementation error will be catched by the tests in sequential execution, but not necessarily in parallel execution.
+
+%% stricter type system
 

### 2021-03-29 blackboard/src/main/java/p4query/blackboard/App.java
v1a: removed unused imports, removed unused dependencies

@@ -18,11 +18,8 @@ package p4query.blackboard;
 
 import java.io.File;
 import java.io.IOException;
-import java.nio.file.Files;
-import java.nio.file.Path;
 import java.nio.file.Paths;
 import java.util.concurrent.ExecutionException;
-import java.util.concurrent.TimeUnit;
 import java.util.concurrent.TimeoutException;
 
 import com.beust.jcommander.JCommander;

### 2021-03-29 broker/src/main/java/p4query/broker/P4FileService.java

@@ -17,7 +17,6 @@
 package p4query.broker;
 
 import java.io.File;
-import java.io.IOException;
 
 import org.codejargon.feather.Provides;
 

### 2021-03-29 experts-aliases/src/main/java/p4query/experts/aliases/Aliases.java

@@ -16,10 +16,6 @@
  */
 package p4query.experts.aliases;
 
-import org.apache.tinkerpop.gremlin.driver.remote.DriverRemoteConnection;
-import org.apache.tinkerpop.gremlin.process.traversal.AnonymousTraversalSource;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
-
 import java.util.Collections;
 import java.util.List;
 import java.util.Map;
@@ -28,6 +24,7 @@ import javax.inject.Singleton;
 
 import org.apache.tinkerpop.gremlin.process.traversal.Order;
 import org.apache.tinkerpop.gremlin.process.traversal.P;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
 import org.apache.tinkerpop.gremlin.process.traversal.step.TraversalOptionParent.Pick;
 import org.apache.tinkerpop.gremlin.structure.Vertex;

### 2021-03-29 experts-call-sites/src/main/java/p4query/experts/callsites/CallSitesImpl.java

@@ -16,17 +16,12 @@
  */
 package p4query.experts.callsites;
 
-import java.util.Collections;
 import java.util.List;
-import java.util.Map;
 
 import javax.inject.Singleton;
 
-import org.apache.tinkerpop.gremlin.process.traversal.Order;
-import org.apache.tinkerpop.gremlin.process.traversal.P;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
-import org.apache.tinkerpop.gremlin.process.traversal.step.TraversalOptionParent.Pick;
 import org.apache.tinkerpop.gremlin.structure.Edge;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
 import org.codejargon.feather.Provides;

### 2021-03-29 experts-control-flow/src/main/java/p4query/experts/controlflow/GremlinLatex.java

@@ -16,53 +16,52 @@
  */
 package p4query.experts.controlflow;
 
-import java.util.List;
-import java.util.Map;
-import java.util.Map.Entry;
-import java.util.function.Function;
-import java.util.function.Supplier;
-
-import javax.lang.model.util.ElementScanner6;
-
-import org.apache.tinkerpop.gremlin.process.traversal.P;
-import org.apache.tinkerpop.gremlin.process.traversal.Pop;
-import org.apache.tinkerpop.gremlin.process.traversal.Step;
-import org.apache.tinkerpop.gremlin.process.traversal.Traversal;
-import org.apache.tinkerpop.gremlin.process.traversal.Traversal.Admin;
-import org.apache.tinkerpop.gremlin.process.traversal.lambda.ElementValueTraversal;
-import org.apache.tinkerpop.gremlin.process.traversal.lambda.TokenTraversal;
-import org.apache.tinkerpop.gremlin.process.traversal.step.ComparatorHolder;
-import org.apache.tinkerpop.gremlin.process.traversal.step.filter.HasStep;
-import org.apache.tinkerpop.gremlin.process.traversal.step.filter.NoneStep;
-import org.apache.tinkerpop.gremlin.process.traversal.step.filter.TailGlobalStep;
-import org.apache.tinkerpop.gremlin.process.traversal.step.filter.WherePredicateStep;
-import org.apache.tinkerpop.gremlin.process.traversal.step.filter.RangeGlobalStep.RangeBiOperator;
-import org.apache.tinkerpop.gremlin.process.traversal.step.map.AddEdgeStep;
-import org.apache.tinkerpop.gremlin.process.traversal.step.map.AddVertexStep;
-import org.apache.tinkerpop.gremlin.process.traversal.step.map.CoalesceStep;
-import org.apache.tinkerpop.gremlin.process.traversal.step.map.CountGlobalStep;
-import org.apache.tinkerpop.gremlin.process.traversal.step.map.EdgeVertexStep;
-import org.apache.tinkerpop.gremlin.process.traversal.step.map.FoldStep;
-import org.apache.tinkerpop.gremlin.process.traversal.step.map.LambdaFlatMapStep;
-import org.apache.tinkerpop.gremlin.process.traversal.step.map.LambdaMapStep;
-import org.apache.tinkerpop.gremlin.process.traversal.step.map.OrderGlobalStep;
[…]

### 2021-03-29 experts-nr-task4/src/main/java/p4query/applications/App.java

@@ -1,27 +1,20 @@
 package p4query.applications;
 
-import com.beust.jcommander.Parameter;
-import com.beust.jcommander.Parameters;
-
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversal;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
-import org.apache.tinkerpop.gremlin.structure.Vertex;
-import org.codejargon.feather.Provides;
-
 import java.io.File;
 import java.util.Map;
 
 import javax.inject.Inject;
 import javax.inject.Provider;
-import javax.inject.Singleton;
 
-import p4query.ontology.providers.Application;
-import p4query.ontology.providers.AppUI;
-import p4query.ontology.providers.P4FileProvider.InputP4File;
-import p4query.ontology.analyses.SyntaxTree;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
+
 import p4query.ontology.Dom;
 import p4query.ontology.Status;
+import p4query.ontology.analyses.SyntaxTree;
+import p4query.ontology.providers.AppUI;
+import p4query.ontology.providers.Application;
+import p4query.ontology.providers.P4FileProvider.InputP4File;
 
 public class App implements Application {
 

### 2021-03-29 experts-nr-task4/src/test/java/p4query/applications/AppTest.java

@@ -1,17 +1,11 @@
 package p4query.applications;
 
-import static org.junit.Assert.assertEquals;
-import static org.junit.Assert.assertTrue;
-
 import java.util.List;
-import java.util.Map;
 
-import org.junit.Test;
-
-import org.apache.tinkerpop.gremlin.tinkergraph.structure.TinkerGraph;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversal;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
+import org.apache.tinkerpop.gremlin.tinkergraph.structure.TinkerGraph;
+import org.junit.Test;
 
 import p4query.ontology.Dom;
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/SMCompiler.java

@@ -22,28 +22,16 @@ import java.io.PrintStream;
 import java.nio.file.Files;
 import java.nio.file.Paths;
 import java.nio.file.StandardCopyOption;
-import java.util.Collection;
-import java.util.Collections;
-import java.util.HashMap;
-import java.util.Iterator;
-import java.util.LinkedList;
-import java.util.List;
-import java.util.Map;
 
 import javax.inject.Inject;
 
 import com.beust.jcommander.Parameter;
 
-import org.apache.tinkerpop.gremlin.process.traversal.Order;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
-import org.apache.tinkerpop.gremlin.structure.Vertex;
 
 import p4query.applications.smc.hir.Program;
 import p4query.applications.smc.lir.StackProgram;
-import p4query.ontology.Dom;
 import p4query.ontology.Status;
-import p4query.ontology.analyses.CallGraph;
 import p4query.ontology.analyses.CallSites;
 import p4query.ontology.analyses.ControlFlow;
 import p4query.ontology.providers.AppUI;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/Definition.java

@@ -18,7 +18,6 @@ package p4query.applications.smc.hir;
 
 import java.util.LinkedHashMap;
 import java.util.List;
-import java.util.Map;
 
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/GlobalMemoryLayout.java

@@ -17,16 +17,12 @@
 package p4query.applications.smc.hir;
 
 import java.util.Arrays;
-import java.util.HashMap;
-import java.util.HashSet;
 import java.util.LinkedHashMap;
 import java.util.LinkedList;
 import java.util.List;
 import java.util.Map;
 
-import p4query.applications.smc.hir.exprs.P4StorageReference;
 import p4query.applications.smc.hir.typing.Composite;
-import p4query.applications.smc.hir.typing.GlobalStruct;
 import p4query.applications.smc.hir.typing.IRType;
 
 // NOTE in P4 structs declaration also initializes, so struct types and struct names are the same

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/InstructionLayout.java

@@ -16,7 +16,6 @@
  */
 package p4query.applications.smc.hir;
 
-import java.io.PrintStream;
 import java.util.HashMap;
 import java.util.Iterator;
 import java.util.LinkedHashMap;
@@ -26,14 +25,11 @@ import java.util.Map;
 
 import org.apache.tinkerpop.gremlin.structure.Vertex;
 
-import groovyjarjarantlr.collections.Stack;
-import p4query.applications.smc.hir.iset.Instruction;
+import p4query.applications.smc.lir.LabelledStackInstruction;
 import p4query.applications.smc.lir.iset.Comment;
-import p4query.applications.smc.lir.iset.Exit;
 import p4query.applications.smc.lir.iset.InterProcJumping;
 import p4query.applications.smc.lir.iset.IntraProcJumping;
 import p4query.applications.smc.lir.iset.ProbabilisticInstruction;
-import p4query.applications.smc.lir.LabelledStackInstruction;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.applications.smc.lir.typing.Label;
 import p4query.applications.smc.lir.typing.UnresolvedInstructionLabel;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/InstructionList.java

@@ -31,7 +31,6 @@ import org.apache.tinkerpop.gremlin.structure.Edge;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
 
 import p4query.applications.smc.hir.iset.Instruction;
-import p4query.applications.smc.hir.iset.ProcedureDone;
 import p4query.applications.smc.hir.typing.IRType;
 import p4query.ontology.Dom;
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/LocalMemoryLayout.java

@@ -16,16 +16,12 @@
  */
 package p4query.applications.smc.hir;
 
-import java.util.Collections;
-import java.util.HashMap;
 import java.util.LinkedHashMap;
 import java.util.LinkedList;
 import java.util.List;
 import java.util.Map;
 
-import p4query.applications.smc.hir.typing.ExternDataType;
 import p4query.applications.smc.hir.typing.IRType;
-import p4query.applications.smc.hir.typing.Struct;
 
 // note: this is somewhat different from GlobalMemoryLayout, because two parameters may have the same name
 //

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/ProcedureDefinition.java

@@ -17,7 +17,6 @@
 package p4query.applications.smc.hir;
 
 import java.util.Collections;
-import java.util.HashMap;
 import java.util.LinkedHashMap;
 import java.util.LinkedList;
 import java.util.List;
@@ -27,9 +26,7 @@ import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSo
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
 
-import p4query.applications.smc.hir.exprs.CustomStorageReference;
 import p4query.applications.smc.hir.iset.Instruction;
-import p4query.applications.smc.hir.iset.ProcedureDone;
 import p4query.applications.smc.hir.typing.IRType;
 import p4query.applications.smc.hir.typing.LocalStruct;
 import p4query.applications.smc.lir.iset.Comment;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/Program.java

@@ -18,15 +18,9 @@ package p4query.applications.smc.hir;
 
 import java.util.Arrays;
 import java.util.Collections;
-import java.util.HashMap;
-import java.util.LinkedHashMap;
 import java.util.LinkedList;
 import java.util.List;
-import java.util.Map;
-import java.util.stream.Collectors;
 
-import org.apache.tinkerpop.gremlin.process.computer.MessageScope.Global;
-import org.apache.tinkerpop.gremlin.process.traversal.Order;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
@@ -35,32 +29,27 @@ import p4query.applications.smc.hir.externs.IsValid;
 import p4query.applications.smc.hir.externs.MarkToDrop;
 import p4query.applications.smc.hir.externs.MemCmp;
 import p4query.applications.smc.hir.externs.MemCpy;
-import p4query.applications.smc.hir.externs.PacketOut;
-import p4query.applications.smc.hir.externs.PacketInExtract;
 import p4query.applications.smc.hir.externs.PacketIn;
+import p4query.applications.smc.hir.externs.PacketInExtract;
+import p4query.applications.smc.hir.externs.PacketOut;
 import p4query.applications.smc.hir.externs.PacketOutEmit;
 import p4query.applications.smc.hir.externs.ReceivePacket;
 import p4query.applications.smc.hir.externs.Subtract;
 import p4query.applications.smc.hir.externs.TableIpv4Lpm;
 import p4query.applications.smc.hir.externs.UpdateChecksum;
 import p4query.applications.smc.hir.externs.V1ModelMain;
-import p4query.applications.smc.hir.iset.Instruction;
-import p4query.applications.smc.hir.typing.BaseType;
 import p4query.applications.smc.hir.typing.GlobalStruct;
 import p4query.applications.smc.hir.typing.IRType;
 import p4query.applications.smc.hir.typing.Struct;
 import p4query.applications.smc.lir.StackProgram;
-import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.Const;
 import p4query.applications.smc.lir.iset.Exit;
-import p4query.applications.smc.lir.iset.IntraProcJumping;
[…]

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/exprs/ArithmeticExpression.java

@@ -28,20 +28,15 @@ import org.apache.tinkerpop.gremlin.structure.Vertex;
 import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.LocalMemoryLayout;
-import p4query.applications.smc.hir.ProcedureDefinition;
 import p4query.applications.smc.hir.typing.IRType;
 import p4query.applications.smc.hir.typing.IRType.SingletonFactory;
 import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.Const;
 import p4query.applications.smc.lir.iset.Invoke;
-import p4query.applications.smc.lir.iset.Load;
 import p4query.applications.smc.lir.iset.Pop;
 import p4query.applications.smc.lir.iset.StackInstruction;
-import p4query.applications.smc.lir.iset.Store;
-import p4query.applications.smc.lir.typing.LocalAddress;
 import p4query.applications.smc.lir.typing.Size;
 import p4query.applications.smc.lir.typing.UnresolvedNameLabel;
-import p4query.applications.smc.lir.typing.UnresolvedVertexLabel;
 import p4query.ontology.Dom;
 
 public class ArithmeticExpression implements Expression {

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/exprs/CustomStorageReference.java

@@ -17,10 +17,8 @@
 package p4query.applications.smc.hir.exprs;
 
 import java.util.Arrays;
-import java.util.LinkedList;
 import java.util.List;
 
-import p4query.applications.smc.hir.ProcedureDefinition;
 import p4query.applications.smc.hir.typing.IRType;
 
 public class CustomStorageReference extends StorageReference {

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/exprs/Expression.java

@@ -21,12 +21,10 @@ import java.util.List;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
-import org.apache.tinkerpop.gremlin.structure.io.Storage;
 
 import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.LocalMemoryLayout;
-import p4query.applications.smc.hir.ProcedureDefinition;
 import p4query.applications.smc.hir.typing.IRType;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.ontology.Dom;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/exprs/LiteralExpression.java

@@ -16,7 +16,6 @@
  */
 package p4query.applications.smc.hir.exprs;
 
-import java.util.LinkedList;
 import java.util.List;
 import java.util.Map;
 
@@ -27,12 +26,8 @@ import org.apache.tinkerpop.gremlin.structure.Vertex;
 import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.LocalMemoryLayout;
-import p4query.applications.smc.hir.ProcedureDefinition;
 import p4query.applications.smc.hir.typing.IRType;
-import p4query.applications.smc.lir.iset.Load;
 import p4query.applications.smc.lir.iset.StackInstruction;
-import p4query.applications.smc.lir.iset.Store;
-import p4query.applications.smc.lir.typing.LocalAddress;
 import p4query.ontology.Dom;
 
 public class LiteralExpression implements Expression {

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/exprs/P4StorageReference.java

@@ -31,9 +31,6 @@ import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSo
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
 
-import p4query.applications.smc.hir.GlobalMemoryLayout;
-import p4query.applications.smc.hir.LocalMemoryLayout;
-import p4query.applications.smc.hir.ProcedureDefinition;
 import p4query.applications.smc.hir.typing.Composite;
 import p4query.applications.smc.hir.typing.IRType;
 import p4query.ontology.Dom;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/exprs/ProcedureCallExpression.java

@@ -29,7 +29,6 @@ import org.apache.tinkerpop.gremlin.structure.Vertex;
 import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.LocalMemoryLayout;
-import p4query.applications.smc.hir.ProcedureDefinition;
 import p4query.applications.smc.hir.typing.IRType;
 import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.Invoke;
@@ -37,7 +36,6 @@ import p4query.applications.smc.lir.iset.Pop;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.applications.smc.lir.typing.Size;
 import p4query.applications.smc.lir.typing.UnresolvedNameLabel;
-import p4query.applications.smc.lir.typing.UnresolvedVertexLabel;
 import p4query.ontology.Dom;
 
 public class ProcedureCallExpression implements Expression {

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/exprs/SelectKeyExpression.java

@@ -28,7 +28,6 @@ import org.apache.tinkerpop.gremlin.structure.Vertex;
 import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.LocalMemoryLayout;
-import p4query.applications.smc.hir.ProcedureDefinition;
 import p4query.applications.smc.hir.iset.SelectHead;
 import p4query.applications.smc.hir.typing.IRType;
 import p4query.applications.smc.hir.typing.IRType.SingletonFactory;
@@ -37,10 +36,7 @@ import p4query.applications.smc.lir.iset.Const;
 import p4query.applications.smc.lir.iset.IfEq;
 import p4query.applications.smc.lir.iset.Invoke;
 import p4query.applications.smc.lir.iset.Pop;
-import p4query.applications.smc.lir.iset.Add;
 import p4query.applications.smc.lir.iset.StackInstruction;
-import p4query.applications.smc.lir.iset.Store;
-import p4query.applications.smc.lir.typing.LocalAddress;
 import p4query.applications.smc.lir.typing.Size;
 import p4query.applications.smc.lir.typing.UnresolvedNameLabel;
 import p4query.applications.smc.lir.typing.UnresolvedVertexLabel;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/externs/ExternDefinition.java

@@ -16,13 +16,9 @@
  */
 package p4query.applications.smc.hir.externs;
 
-import java.util.List;
-
 import p4query.applications.smc.hir.Definition;
-import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.typing.IRType;
 import p4query.applications.smc.hir.typing.LocalStruct;
-import p4query.applications.smc.lir.iset.StackInstruction;
 
 public abstract class ExternDefinition implements Definition {
     protected String name;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/externs/IsValid.java

@@ -19,15 +19,11 @@ package p4query.applications.smc.hir.externs;
 import java.util.LinkedList;
 import java.util.List;
 
-import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.InstructionLayout;
-import p4query.applications.smc.hir.iset.ProcedureDone;
 import p4query.applications.smc.hir.typing.LocalStruct;
 import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.Const;
-import p4query.applications.smc.lir.iset.GetField;
-import p4query.applications.smc.lir.iset.Load;
 import p4query.applications.smc.lir.iset.Return;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.applications.smc.lir.typing.Int;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/externs/MarkToDrop.java

@@ -19,25 +19,17 @@ package p4query.applications.smc.hir.externs;
 import java.util.LinkedList;
 import java.util.List;
 
-import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.InstructionLayout;
 import p4query.applications.smc.hir.InstructionLayout.Builder;
 import p4query.applications.smc.hir.typing.LocalStruct;
-import p4query.applications.smc.lir.iset.Add;
 import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.Const;
-import p4query.applications.smc.lir.iset.GetField;
-import p4query.applications.smc.lir.iset.Invoke;
-import p4query.applications.smc.lir.iset.Load;
-import p4query.applications.smc.lir.iset.Pop;
-import p4query.applications.smc.lir.iset.PutField;
 import p4query.applications.smc.lir.iset.Return;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.applications.smc.lir.typing.Int;
 import p4query.applications.smc.lir.typing.LocalAddress;
 import p4query.applications.smc.lir.typing.Size;
-import p4query.applications.smc.lir.typing.UnresolvedNameLabel;
 
 public class MarkToDrop extends ExternDefinition {
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/externs/MemCmp.java

@@ -19,25 +19,16 @@ package p4query.applications.smc.hir.externs;
 import java.util.LinkedList;
 import java.util.List;
 
-import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.InstructionLayout;
 import p4query.applications.smc.hir.InstructionLayout.Builder;
-import p4query.applications.smc.hir.typing.LocalStruct;
-import p4query.applications.smc.lir.iset.Add;
 import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.Const;
-import p4query.applications.smc.lir.iset.GetField;
-import p4query.applications.smc.lir.iset.Invoke;
-import p4query.applications.smc.lir.iset.Load;
-import p4query.applications.smc.lir.iset.Pop;
-import p4query.applications.smc.lir.iset.PutField;
 import p4query.applications.smc.lir.iset.Return;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.applications.smc.lir.typing.Int;
 import p4query.applications.smc.lir.typing.LocalAddress;
 import p4query.applications.smc.lir.typing.Size;
-import p4query.applications.smc.lir.typing.UnresolvedNameLabel;
 
 public class MemCmp extends ExternDefinition {
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/externs/MemCpy.java

@@ -19,25 +19,16 @@ package p4query.applications.smc.hir.externs;
 import java.util.LinkedList;
 import java.util.List;
 
-import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.InstructionLayout;
 import p4query.applications.smc.hir.InstructionLayout.Builder;
-import p4query.applications.smc.hir.typing.LocalStruct;
-import p4query.applications.smc.lir.iset.Add;
 import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.Const;
-import p4query.applications.smc.lir.iset.GetField;
-import p4query.applications.smc.lir.iset.Invoke;
-import p4query.applications.smc.lir.iset.Load;
-import p4query.applications.smc.lir.iset.Pop;
-import p4query.applications.smc.lir.iset.PutField;
 import p4query.applications.smc.lir.iset.Return;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.applications.smc.lir.typing.Int;
 import p4query.applications.smc.lir.typing.LocalAddress;
 import p4query.applications.smc.lir.typing.Size;
-import p4query.applications.smc.lir.typing.UnresolvedNameLabel;
 
 public class MemCpy extends ExternDefinition {
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/externs/PacketInExtract.java

@@ -19,11 +19,9 @@ package p4query.applications.smc.hir.externs;
 import java.util.LinkedList;
 import java.util.List;
 
-import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.InstructionLayout;
 import p4query.applications.smc.hir.InstructionLayout.Builder;
-import p4query.applications.smc.hir.typing.LocalStruct;
 import p4query.applications.smc.lir.iset.Add;
 import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.Const;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/externs/PacketOut.java

@@ -18,11 +18,8 @@ package p4query.applications.smc.hir.externs;
 
 import java.util.LinkedHashMap;
 
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
-
 import p4query.applications.smc.hir.typing.Composite;
 import p4query.applications.smc.hir.typing.GenType;
-import p4query.applications.smc.hir.typing.GlobalStruct;
 import p4query.applications.smc.hir.typing.IRType;
 
 public class PacketOut implements Composite {

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/externs/PacketOutEmit.java

@@ -19,25 +19,16 @@ package p4query.applications.smc.hir.externs;
 import java.util.LinkedList;
 import java.util.List;
 
-import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.InstructionLayout;
 import p4query.applications.smc.hir.InstructionLayout.Builder;
-import p4query.applications.smc.hir.typing.LocalStruct;
-import p4query.applications.smc.lir.iset.Add;
 import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.Const;
-import p4query.applications.smc.lir.iset.GetField;
-import p4query.applications.smc.lir.iset.Invoke;
-import p4query.applications.smc.lir.iset.Load;
-import p4query.applications.smc.lir.iset.Pop;
-import p4query.applications.smc.lir.iset.PutField;
 import p4query.applications.smc.lir.iset.Return;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.applications.smc.lir.typing.Int;
 import p4query.applications.smc.lir.typing.LocalAddress;
 import p4query.applications.smc.lir.typing.Size;
-import p4query.applications.smc.lir.typing.UnresolvedNameLabel;
 
 public class PacketOutEmit extends ExternDefinition {
     private Builder instLayout;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/externs/ReceivePacket.java

@@ -19,25 +19,16 @@ package p4query.applications.smc.hir.externs;
 import java.util.LinkedList;
 import java.util.List;
 
-import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.InstructionLayout;
 import p4query.applications.smc.hir.InstructionLayout.Builder;
-import p4query.applications.smc.hir.typing.LocalStruct;
-import p4query.applications.smc.lir.iset.Add;
 import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.Const;
-import p4query.applications.smc.lir.iset.GetField;
-import p4query.applications.smc.lir.iset.Invoke;
-import p4query.applications.smc.lir.iset.Load;
-import p4query.applications.smc.lir.iset.Pop;
-import p4query.applications.smc.lir.iset.PutField;
 import p4query.applications.smc.lir.iset.Return;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.applications.smc.lir.typing.Int;
 import p4query.applications.smc.lir.typing.LocalAddress;
 import p4query.applications.smc.lir.typing.Size;
-import p4query.applications.smc.lir.typing.UnresolvedNameLabel;
 
 public class ReceivePacket extends ExternDefinition {
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/externs/Subtract.java

@@ -19,25 +19,16 @@ package p4query.applications.smc.hir.externs;
 import java.util.LinkedList;
 import java.util.List;
 
-import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.InstructionLayout;
 import p4query.applications.smc.hir.InstructionLayout.Builder;
-import p4query.applications.smc.hir.typing.LocalStruct;
-import p4query.applications.smc.lir.iset.Add;
 import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.Const;
-import p4query.applications.smc.lir.iset.GetField;
-import p4query.applications.smc.lir.iset.Invoke;
-import p4query.applications.smc.lir.iset.Load;
-import p4query.applications.smc.lir.iset.Pop;
-import p4query.applications.smc.lir.iset.PutField;
 import p4query.applications.smc.lir.iset.Return;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.applications.smc.lir.typing.Int;
 import p4query.applications.smc.lir.typing.LocalAddress;
 import p4query.applications.smc.lir.typing.Size;
-import p4query.applications.smc.lir.typing.UnresolvedNameLabel;
 
 public class Subtract extends ExternDefinition {
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/externs/TableIpv4Lpm.java

@@ -18,7 +18,6 @@ package p4query.applications.smc.hir.externs;
 
 import java.util.Collections;
 import java.util.HashMap;
-import java.util.HashSet;
 import java.util.LinkedHashMap;
 import java.util.LinkedHashSet;
 import java.util.LinkedList;
@@ -34,24 +33,18 @@ import org.apache.tinkerpop.gremlin.structure.Vertex;
 
 import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
-import p4query.applications.smc.hir.InstructionLayout;
-import p4query.applications.smc.hir.LocalMemoryLayout;
 import p4query.applications.smc.hir.InstructionLayout.Builder;
+import p4query.applications.smc.hir.LocalMemoryLayout;
 import p4query.applications.smc.hir.exprs.Expression;
-import p4query.applications.smc.hir.exprs.StorageReference;
 import p4query.applications.smc.hir.typing.IRType;
-import p4query.applications.smc.hir.typing.LocalStruct;
 import p4query.applications.smc.hir.typing.IRType.SingletonFactory;
-import p4query.applications.smc.lir.iset.Add;
 import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.Const;
-import p4query.applications.smc.lir.iset.GetField;
 import p4query.applications.smc.lir.iset.Goto;
 import p4query.applications.smc.lir.iset.Invoke;
 import p4query.applications.smc.lir.iset.Load;
 import p4query.applications.smc.lir.iset.Pop;
 import p4query.applications.smc.lir.iset.ProbabilisticInstruction;
-import p4query.applications.smc.lir.iset.PutField;
 import p4query.applications.smc.lir.iset.Return;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.applications.smc.lir.typing.GlobalAddress;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/externs/UpdateChecksum.java

@@ -19,25 +19,16 @@ package p4query.applications.smc.hir.externs;
 import java.util.LinkedList;
 import java.util.List;
 
-import p4query.applications.smc.hir.Definition;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.InstructionLayout;
 import p4query.applications.smc.hir.InstructionLayout.Builder;
-import p4query.applications.smc.hir.typing.LocalStruct;
-import p4query.applications.smc.lir.iset.Add;
 import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.Const;
-import p4query.applications.smc.lir.iset.GetField;
-import p4query.applications.smc.lir.iset.Invoke;
-import p4query.applications.smc.lir.iset.Load;
-import p4query.applications.smc.lir.iset.Pop;
-import p4query.applications.smc.lir.iset.PutField;
 import p4query.applications.smc.lir.iset.Return;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.applications.smc.lir.typing.Int;
 import p4query.applications.smc.lir.typing.LocalAddress;
 import p4query.applications.smc.lir.typing.Size;
-import p4query.applications.smc.lir.typing.UnresolvedNameLabel;
 
 public class UpdateChecksum extends ExternDefinition {
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/iset/Assignment.java

@@ -27,9 +27,7 @@ import org.apache.tinkerpop.gremlin.structure.Vertex;
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.LocalMemoryLayout;
 import p4query.applications.smc.hir.ProcedureDefinition;
-import p4query.applications.smc.hir.exprs.CustomStorageReference;
 import p4query.applications.smc.hir.exprs.Expression;
-import p4query.applications.smc.hir.exprs.P4StorageReference;
 import p4query.applications.smc.hir.exprs.StorageReference;
 import p4query.applications.smc.hir.typing.IRType;
 import p4query.applications.smc.lir.iset.Comment;
@@ -39,7 +37,6 @@ import p4query.applications.smc.lir.iset.Pop;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.applications.smc.lir.typing.Size;
 import p4query.applications.smc.lir.typing.UnresolvedNameLabel;
-import p4query.applications.smc.lir.typing.UnresolvedVertexLabel;
 import p4query.ontology.Dom;
 
 public class Assignment implements Instruction {

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/iset/Instruction.java

@@ -16,28 +16,18 @@
  */
 package p4query.applications.smc.hir.iset;
 
-import java.util.Arrays;
 import java.util.HashMap;
 import java.util.LinkedList;
 import java.util.List;
 import java.util.Map;
-import java.util.NoSuchElementException;
 
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
 
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.LocalMemoryLayout;
 import p4query.applications.smc.hir.ProcedureDefinition;
-import p4query.applications.smc.hir.exprs.ArithmeticExpression;
-import p4query.applications.smc.hir.exprs.Expression;
-import p4query.applications.smc.hir.exprs.LiteralExpression;
-import p4query.applications.smc.hir.exprs.P4StorageReference;
-import p4query.applications.smc.hir.exprs.CustomStorageReference;
-import p4query.applications.smc.hir.exprs.StorageReference;
 import p4query.applications.smc.hir.typing.IRType;
-import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.StackInstruction;
 import p4query.ontology.Dom;
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/iset/NoOp.java

@@ -16,7 +16,6 @@
  */
 package p4query.applications.smc.hir.iset;
 
-import java.util.Arrays;
 import java.util.LinkedList;
 import java.util.List;
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/iset/ProcedureCall.java

@@ -16,11 +16,9 @@
  */
 package p4query.applications.smc.hir.iset;
 
-import java.util.LinkedList;
 import java.util.List;
 
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
 
 import p4query.applications.smc.hir.typing.IRType;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/iset/SelectCase.java

@@ -18,24 +18,17 @@ package p4query.applications.smc.hir.iset;
 
 import java.util.LinkedList;
 import java.util.List;
-import java.util.Map;
-import java.util.NoSuchElementException;
 
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
 
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.LocalMemoryLayout;
 import p4query.applications.smc.hir.ProcedureDefinition;
 import p4query.applications.smc.hir.exprs.Expression;
-import p4query.applications.smc.hir.exprs.LiteralExpression;
 import p4query.applications.smc.hir.exprs.SelectKeyExpression;
 import p4query.applications.smc.hir.typing.IRType;
-import p4query.applications.smc.lir.iset.Comment;
-import p4query.applications.smc.lir.iset.IfEq;
 import p4query.applications.smc.lir.iset.StackInstruction;
-import p4query.ontology.Dom;
 
 public class SelectCase implements Instruction {
     private ProcedureDefinition procDef;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/typing/IRType.java

@@ -17,14 +17,12 @@
 package p4query.applications.smc.hir.typing;
 
 import java.util.HashMap;
-import java.util.LinkedList;
 import java.util.List;
 import java.util.Map;
 import java.util.stream.Collectors;
 
 import org.apache.tinkerpop.gremlin.process.traversal.Order;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
 
 import p4query.applications.smc.hir.exprs.Expression;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/typing/LocalStruct.java

@@ -17,15 +17,9 @@
 package p4query.applications.smc.hir.typing;
 
 import java.util.LinkedHashMap;
-import java.util.List;
 import java.util.Map;
 
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
-import org.apache.tinkerpop.gremlin.structure.Vertex;
-
 import p4query.applications.smc.hir.Definition;
-import p4query.applications.smc.hir.ProcedureDefinition;
 
 public class LocalStruct implements Composite {
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/hir/typing/Struct.java

@@ -16,7 +16,6 @@
  */
 package p4query.applications.smc.hir.typing;
 
-import java.util.HashMap;
 import java.util.LinkedHashMap;
 import java.util.List;
 import java.util.Map;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/LabelledStackInstruction.java

@@ -16,9 +16,6 @@
  */
 package p4query.applications.smc.lir;
 
-import java.io.PrintStream;
-
-import p4query.applications.smc.lir.iset.Exit;
 import p4query.applications.smc.lir.iset.StackInstruction;
 
 public class LabelledStackInstruction {

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/StackProgram.java

@@ -17,11 +17,9 @@
 package p4query.applications.smc.lir;
 
 import java.io.PrintStream;
-import java.util.LinkedList;
 
 import p4query.applications.smc.hir.GlobalMemoryLayout;
 import p4query.applications.smc.hir.InstructionLayout;
-import p4query.applications.smc.lir.iset.StackInstruction;
 
 public class StackProgram {
    private GlobalMemoryLayout global;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/Add.java

@@ -16,8 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
-
 public class Add implements StackInstruction {
 
     @Override

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/Comment.java

@@ -16,8 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
-
 public class Comment implements StackInstruction {
 
     private String comment;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/Const.java

@@ -16,8 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
-
 import p4query.applications.smc.lir.typing.IntegerBasedType;
 
 public class Const implements StackInstruction {

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/Exit.java

@@ -16,11 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
-
-import p4query.applications.smc.lir.typing.LocalAddress;
-import p4query.applications.smc.lir.typing.Size;
-
 public class Exit implements StackInstruction {
 
     public Exit() {

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/GetField.java

@@ -16,7 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
 
 public class GetField implements StackInstruction {
     @Override

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/IfEq.java

@@ -16,7 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
 
 import p4query.applications.smc.lir.typing.Label;
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/Invoke.java

@@ -16,7 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
 
 import p4query.applications.smc.lir.typing.Label;
 import p4query.applications.smc.lir.typing.Size;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/Load.java

@@ -16,7 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
 
 import p4query.applications.smc.lir.typing.LocalAddress;
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/Pop.java

@@ -16,7 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
 
 public class Pop implements StackInstruction {
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/ProbabilisticInstruction.java

@@ -16,8 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
-import java.math.BigDecimal;
 import java.util.LinkedHashMap;
 import java.util.LinkedList;
 import java.util.List;

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/PutField.java

@@ -16,8 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
-
 public class PutField implements StackInstruction {
     @Override
     public String toString() {

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/Return.java

@@ -16,8 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
-
 import p4query.applications.smc.lir.typing.LocalAddress;
 import p4query.applications.smc.lir.typing.Size;
 

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/StackInstruction.java

@@ -16,7 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
 
 public interface StackInstruction {
    String toHumanReadable();

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/iset/Store.java

@@ -16,8 +16,6 @@
  */
 package p4query.applications.smc.lir.iset;
 
-import java.io.PrintStream;
-
 import p4query.applications.smc.lir.typing.LocalAddress;
 
 public class Store implements StackInstruction {

### 2021-03-29 experts-smc/src/main/java/p4query/applications/smc/lir/typing/UnresolvedInstructionLabel.java

@@ -16,9 +16,6 @@
  */
 package p4query.applications.smc.lir.typing;
 
-import java.util.List;
-
-import p4query.applications.smc.lir.iset.Comment;
 import p4query.applications.smc.lir.iset.StackInstruction;
 
 public class UnresolvedInstructionLabel extends Label {

### 2021-03-29 experts-symbol-table/src/main/java/p4query/experts/symboltable/SymbolTableImpl.java

@@ -16,28 +16,6 @@
  */
 package p4query.experts.symboltable;
 
-import p4query.ontology.Dom;
-import p4query.ontology.Status;
-import p4query.ontology.analyses.AbstractSyntaxTree;
-import p4query.ontology.analyses.SymbolTable;
-import p4query.ontology.analyses.SyntaxTree;
-
-import org.apache.tinkerpop.gremlin.driver.remote.DriverRemoteConnection;
-import org.apache.tinkerpop.gremlin.process.traversal.AnonymousTraversalSource;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
-
-import org.apache.tinkerpop.gremlin.process.traversal.Operator;
-import org.apache.tinkerpop.gremlin.process.traversal.Order;
-import org.apache.tinkerpop.gremlin.process.traversal.P;
-import org.apache.tinkerpop.gremlin.process.traversal.step.TraversalOptionParent.Pick;
-import org.apache.tinkerpop.gremlin.structure.Edge;
-import org.apache.tinkerpop.gremlin.structure.Graph;
-import org.apache.tinkerpop.gremlin.structure.Vertex;
-import org.apache.tinkerpop.gremlin.util.function.Lambda;
-import org.codejargon.feather.Provides;
-import org.apache.tinkerpop.gremlin.process.traversal.step.util.BulkSet;
-
 import java.util.Collections;
 import java.util.HashMap;
 import java.util.Iterator;
@@ -46,6 +24,20 @@ import java.util.List;
 import java.util.Map;
 
 import javax.inject.Singleton;
+
+import org.apache.tinkerpop.gremlin.process.traversal.Order;
+import org.apache.tinkerpop.gremlin.process.traversal.P;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
+import org.apache.tinkerpop.gremlin.structure.Vertex;
+import org.apache.tinkerpop.gremlin.util.function.Lambda;
+import org.codejargon.feather.Provides;
+
+import p4query.ontology.Dom;
+import p4query.ontology.Status;
+import p4query.ontology.analyses.AbstractSyntaxTree;
+import p4query.ontology.analyses.SymbolTable;
[…]

### 2021-03-29 experts-syntax-tree/src/main/java/p4query/experts/syntaxtree/AntlrP4.java

@@ -16,19 +16,24 @@
  */
 package p4query.experts.syntaxtree;
 
+import java.io.File;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.List;
+
+import javax.inject.Singleton;
+import javax.xml.parsers.ParserConfigurationException;
+import javax.xml.transform.TransformerException;
+
 import org.anarres.cpp.CppReader;
 import org.anarres.cpp.Preprocessor;
 import org.antlr.v4.gui.TreeViewer;
-import org.antlr.v4.runtime.CharStream;
 import org.antlr.v4.runtime.CharStreams;
 import org.antlr.v4.runtime.CommonTokenStream;
 import org.antlr.v4.runtime.TokenStream;
 import org.antlr.v4.runtime.tree.ParseTree;
-
-import org.apache.tinkerpop.gremlin.process.traversal.Step;
-import org.apache.tinkerpop.gremlin.structure.Graph;
-import org.apache.tinkerpop.gremlin.structure.Vertex;
-import org.apache.tinkerpop.gremlin.tinkergraph.structure.TinkerGraph;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
 import org.codejargon.feather.Provides;
 
 import p4query.experts.syntaxtree.p4.P4Lexer;
@@ -38,24 +43,6 @@ import p4query.ontology.analyses.SyntaxTree;
 import p4query.ontology.providers.P4FileProvider.CoreP4File;
 import p4query.ontology.providers.P4FileProvider.InputP4File;
 import p4query.ontology.providers.P4FileProvider.V1ModelP4File;
-
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
-
-import java.io.File;
-import java.io.FileNotFoundException;
-import java.io.IOException;
-import java.io.PrintStream;
-import java.io.PrintWriter;
-import java.net.URL;
-import java.util.ArrayList;
-import java.util.Arrays;
-import java.util.List;
-import java.util.concurrent.ExecutorService;
-import java.util.concurrent.Executors;
-
-import javax.inject.Singleton;
-import javax.xml.parsers.ParserConfigurationException;
-import javax.xml.transform.TransformerException;
 
 public class AntlrP4 {
 

### 2021-03-29 experts-syntax-tree/src/main/java/p4query/experts/syntaxtree/TinkerGraphParseTree.java

@@ -16,29 +16,18 @@
  */
 package p4query.experts.syntaxtree;
 
-import java.util.ArrayList;
 import java.util.HashMap;
-import java.util.List;
 import java.util.Map;
 
 import org.antlr.v4.runtime.ParserRuleContext;
-import org.antlr.v4.runtime.RuleContext;
 import org.antlr.v4.runtime.Vocabulary;
 import org.antlr.v4.runtime.tree.ParseTree;
 import org.antlr.v4.runtime.tree.ParseTreeWalker;
-import org.antlr.v4.runtime.tree.RuleNode;
 import org.antlr.v4.runtime.tree.TerminalNode;
-import org.apache.tinkerpop.gremlin.process.traversal.Traverser;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversal;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
-import org.apache.tinkerpop.gremlin.structure.Graph;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
-import org.apache.tinkerpop.gremlin.tinkergraph.structure.TinkerGraph;
-import org.w3c.dom.Element;
 
 import p4query.experts.syntaxtree.p4.P4BaseListener;
-import p4query.experts.syntaxtree.p4.P4BaseVisitor;
-
 import p4query.ontology.Dom;
 
 public class TinkerGraphParseTree {

### 2021-03-29 experts-tz-task6/src/main/java/p4query/applications/App.java

@@ -1,19 +1,6 @@
 package p4query.applications;
 
-import com.beust.jcommander.Parameter;
-import com.beust.jcommander.Parameters;
-
-import org.apache.tinkerpop.gremlin.process.traversal.P;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
-import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
-import org.apache.tinkerpop.gremlin.structure.io.graphson.GraphSONMapper;
-import org.apache.tinkerpop.gremlin.structure.io.graphson.GraphSONVersion;
-import org.apache.tinkerpop.shaded.jackson.core.JsonProcessingException;
-import org.apache.tinkerpop.shaded.jackson.databind.ObjectMapper;
-import org.codejargon.feather.Provides;
-
 import java.io.File;
-import java.io.IOException;
 import java.util.ArrayList;
 import java.util.HashMap;
 import java.util.List;
@@ -21,14 +8,20 @@ import java.util.Map;
 
 import javax.inject.Inject;
 import javax.inject.Provider;
-import javax.inject.Singleton;
 
-import p4query.ontology.providers.Application;
-import p4query.ontology.providers.AppUI;
-import p4query.ontology.providers.P4FileProvider.InputP4File;
-import p4query.ontology.analyses.SyntaxTree;
+import org.apache.tinkerpop.gremlin.process.traversal.P;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
+import org.apache.tinkerpop.gremlin.structure.io.graphson.GraphSONMapper;
+import org.apache.tinkerpop.gremlin.structure.io.graphson.GraphSONVersion;
+import org.apache.tinkerpop.shaded.jackson.databind.ObjectMapper;
+
 import p4query.ontology.Dom;
 import p4query.ontology.Status;
+import p4query.ontology.analyses.SyntaxTree;
+import p4query.ontology.providers.AppUI;
+import p4query.ontology.providers.Application;
+import p4query.ontology.providers.P4FileProvider.InputP4File;
 
 public class App implements Application {
 

### 2021-03-29 experts-tz-task6/src/test/java/p4query/applications/AppTest.java

@@ -2,14 +2,11 @@ package p4query.applications;
 
 import static org.junit.Assert.assertTrue;
 
-import java.io.IOException;
 import java.util.Map;
 
-import org.apache.tinkerpop.gremlin.tinkergraph.structure.TinkerGraph;
-import org.apache.tinkerpop.shaded.jackson.core.JsonProcessingException;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
-
+import org.apache.tinkerpop.gremlin.tinkergraph.structure.TinkerGraph;
 import org.junit.Test;
 
 import p4query.ontology.Dom;

### 2021-03-29 experts-visualisation/src/main/java/p4query/applications/visualisation/GraphUtils.java

@@ -16,6 +16,22 @@
  */
 package p4query.applications.visualisation;
 
+import java.awt.Desktop;
+import java.io.File;
+import java.io.IOException;
+import java.io.InputStream;
+import java.nio.file.Files;
+import java.nio.file.Path;
+import java.nio.file.Paths;
+import java.nio.file.StandardCopyOption;
+import java.util.Arrays;
+import java.util.Collections;
+import java.util.HashMap;
+import java.util.LinkedHashSet;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+
 import javax.xml.transform.Source;
 import javax.xml.transform.Transformer;
 import javax.xml.transform.TransformerException;
@@ -34,27 +50,7 @@ import org.apache.tinkerpop.gremlin.structure.Graph;
 import org.apache.tinkerpop.gremlin.structure.Property;
 import org.apache.tinkerpop.gremlin.structure.T;
 import org.apache.tinkerpop.gremlin.structure.Vertex;
-import org.apache.tinkerpop.gremlin.structure.VertexProperty;
 import org.apache.tinkerpop.gremlin.tinkergraph.structure.TinkerGraph;
-
-import java.awt.Desktop;
-import java.io.File;
-import java.io.IOException;
-import java.nio.file.Files;
-import java.nio.file.Path;
-import java.nio.file.Paths;
-import java.util.ArrayList;
-import java.util.Arrays;
-import java.util.Collections;
-import java.util.HashMap;
-import java.util.Iterator;
-import java.util.LinkedHashSet;
-import java.util.List;
-import java.util.Map;
-import java.util.Set;
-import java.util.stream.Stream;
-import java.nio.file.StandardCopyOption;
-import java.io.InputStream;
 
 
 

### 2021-03-29 experts-visualisation/src/main/java/p4query/applications/visualisation/Printer.java

@@ -23,24 +23,15 @@ import java.util.Collection;
 import java.util.HashMap;
 import java.util.Map;
 import java.util.Set;
-import java.util.function.Function;
 import java.util.stream.Collectors;
 
 import javax.inject.Inject;
 import javax.inject.Provider;
-import javax.inject.Singleton;
-import javax.xml.parsers.ParserConfigurationException;
 import javax.xml.transform.TransformerException;
 
-import org.apache.tinkerpop.gremlin.driver.remote.DriverRemoteConnection;
-import org.apache.tinkerpop.gremlin.process.traversal.AnonymousTraversalSource;
 import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
 import org.reflections.Reflections;
-import org.codejargon.feather.Provides;
 
-import p4query.ontology.providers.AppUI;
-import p4query.ontology.providers.Application;
-import p4query.ontology.providers.CLIArgs;
 import p4query.applications.visualisation.GraphUtils.Label;
 import p4query.ontology.Status;
 import p4query.ontology.analyses.AbstractSyntaxTree;
@@ -49,6 +40,9 @@ import p4query.ontology.analyses.CallSites;
 import p4query.ontology.analyses.ControlFlow;
 import p4query.ontology.analyses.SymbolTable;
 import p4query.ontology.analyses.SyntaxTree;
+import p4query.ontology.providers.AppUI;
+import p4query.ontology.providers.Application;
+import p4query.ontology.providers.CLIArgs;
 
 public class Printer implements Application {
 

### 2021-03-29 publications/The_tool_intro/paper.tex
tool_intro: minor changes

@@
 	\subsection{Testing}
-	There are two main goals with the testing: to test if the analysers work well; and because it is a quite new tool, it will go through a lot of changes, therefore the possible spoils of the analysers during changes need to be detected.
-This version of the tool contains unit tests and integration tests to check the functional correctness.
+	The framework has a specific testing module, which has two main goals: to test if the analysers work well; and to test the possible spoils of the analysers during changes.
+So the tool contains unit tests and integration tests to check the functional correctness.
 
-	With the unit tests, our main goal is to check if the analysers work well.
 	Unit tests need to be fast, therefore they work with smallest part of the analysers ie.
@@
 One of them executes all of the defined tests -- i.e.
-it goes through all of the P4 sources and executes the necessary analysers and tests the their results -- which is useful to test the whole program and identify regression errors.
+it goes through all of the P4 sources and executes the necessary analysers and tests their results -- which is useful to test the whole program and identify regression errors.
 The other focuses only one analyser and it is useful, when someone actually develop that analyser.

### 2021-03-29 publications/The_tool_intro/paper.tex
tool_intro: minor changes

@@
 When one analyser needs to be tested, it uses the P4 file, and executes every analyser, that it is based on and the tests will check the result of this running.
-The tests are predefined, therefore we use a file to store the information of the tested sources and analyser -- which file tests which analysers and with which test classes.
 
@@
 
-  The approach of the checking is defined in our previous paper \cite{ownCheck}, but in short, it calculates the pre- and post-condition of the various blocks -- i.e the control apply functions, the tables and actions --, the parser and the deparser of the program.
+  The approach of the checking is defined in our previous paper \cite{ownCheck}, but in short, it calculates the pre- and post-condition of the various blocks -- i.e the applied functions, the tables and the actions of the control --, the parser and the deparser of the program.
 Based on these condition pairs it can detect improper usage of the fields and headers.
@@
 
-  In Figure \ref{code:cond}, there is an example condition for the MyIngress.
+  In Figure \ref{code:cond}, there is an example condition for MyIngress control.
 We can see 4 pairs of conditions because it has 4 possible execution paths - there are three where the condition of the branch is true, and the table executes one of the possible actions i.e.
@@
 Implementations of P4 externals such as extern calls and lookup tables (e.g.
-\texttt{packet.extract} and \texttt{ipv4\_lpm} and in Figure~\ref{code:P4}) can also be passed to the tool in the form of these primitive instructions with known costs.
+\texttt{packet.extract} and \texttt{ipv4\_lpm} in Figure~\ref{code:P4}) can also be passed to the tool in the form of these primitive instructions with known costs.
 
@@
 	In the future, we would like to extend the tool with new analyses to give some other useful information for the developers about their P4 source.
-Our nearest idea is to supplement it with the dependency graph and def-use graph with which we will be able to give report, which are based on the connection between the statements.
+Our nearest idea is to supplement it with the dependency graph and def-use graph with which we will be able to give report based on the connection between the statements.
 

### 2021-03-30 broker/src/main/java/p4query/broker/App.java
add tests

@@ -89,6 +89,7 @@ public class App {
         try {
             App broker = new App(args);
             broker.run();
+            broker.close();
         } catch (IllegalUserInputException e) {
             System.out.println(e.getMessage());
         } // otherwise: crash
@@ -97,7 +98,7 @@ public class App {
     }
 
 
-    private App(String[] args) throws DiscoveryException, IOException, LocalGremlinServerException,
+    public App(String[] args) throws DiscoveryException, IOException, LocalGremlinServerException,
             ClassNotFoundException, ReflectionException, IllegalUserInputException {
 
         analysers = App.discoverAnalysers();
@@ -117,7 +118,7 @@ public class App {
         feather = initDI(cli, pfs, analysers, server);
     }
 
-    private void run() throws Exception {
+    public void run() throws Exception {
 
         AppUI ui = cli.getInvokedAppUI();
 
@@ -134,7 +135,14 @@ public class App {
                 System.out.println("--readonly argument found, modifications are not saved");
         }
 
-        server.close();
+    }
+
+    public void close() throws Exception {
+      server.close();
+    }
+
+    public GraphTraversalSource getGraphTraversalSource() throws Exception {
+      return server.provideConnection();
     }
 
     private static String contentsToTempFile(InputStream is, String fileName) throws IOException {

### 2021-03-30 broker/src/test/java/p4query/applications/tests/TCommand.java

@@ -1,0 +1,35 @@
+/**
+ * Copyright 2020, Eötvös Loránd University.
+ * All rights reserved.
+ */
+package p4query.applications.tests;
+
+import java.util.List;
+
+import com.beust.jcommander.Parameter;
+import com.beust.jcommander.Parameters;
+
+import p4query.ontology.providers.AppUI;
+
+@Parameters(commandDescription = "Launch the graph drawing application")
+public class TCommand extends AppUI {
+
+
+    @Override
+    public String getCommandName() {
+        return "test";
+    }
+
+    @Parameter(names = { "-A", "--analysers"}, description = "<descriptors of analysers who will be needed for the tests>", validateWith = OptionCannotBeValueValidator.class, variableArity = true)
+    public List<String> names;
+
+    @Override
+    public String[] getCommandNameAliases() {
+        return new String[]{};
+    }
+
+    @Override
+    public String toString() {
+        return "TCommand [super= " + super.toString()+ ", help=" + help + ", names=" + names + "]";
+    }
+}

### 2021-03-30 broker/src/test/java/p4query/broker/BaseITClass.java

@@ -1,0 +1,44 @@
+/**
+ * Copyright 2020, Eötvös Loránd University.
+ * All rights reserved.
+ */
+package p4query.broker;
+
+import java.util.List;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+
+public class BaseITClass {
+
+    public  GraphTraversalSource g;
+    private List<String> analysesNames;
+    private static Boolean open; 
+    private App broker;
+
+    public void preTests(String file, List<String> inApps) {
+        analysesNames = inApps; 
+
+        String[] args = new String[analysesNames.size() + 3];
+        args[0] = "test"; args[1] = file; args[2] = "-A";
+        for (int i = 0; i < analysesNames.size(); i++) {
+           args[i+3] = analysesNames.get(i);
+       }
+
+      try {
+         broker = new App(args);
+         broker.run();
+         open = true;
+      } catch (Exception e) {
+        System.out.println(e.getMessage());
+      }
+    }
+      
+  public void postTest() throws Exception {
+      if (open)
+        broker.close();
+    }
+
+    public GraphTraversalSource getTraversalSource() throws Exception {
+      return broker.getGraphTraversalSource(); 
+    }
+
+  }

### 2021-03-30 blackboard/src/main/java/p4query/blackboard/P4KnowledgeGraphMutationListener.java
Initial commit

@@ -1,0 +1,120 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.blackboard;
+
+import org.apache.tinkerpop.gremlin.process.traversal.P;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
+import org.apache.tinkerpop.gremlin.process.traversal.step.util.event.MutationListener;
+import org.apache.tinkerpop.gremlin.structure.Edge;
+import org.apache.tinkerpop.gremlin.structure.Property;
+import org.apache.tinkerpop.gremlin.structure.T;
+import org.apache.tinkerpop.gremlin.structure.Vertex;
+import org.apache.tinkerpop.gremlin.structure.VertexProperty;
+import org.apache.tinkerpop.gremlin.structure.Graph;
+
+import java.util.HashMap;
+import java.util.Map;
+// example MutationListener:
+// import org.apache.tinkerpop.gremlin.process.traversal.step.util.event.ConsoleMutationListener;
+
+// IMPORTANT: this is not thread-safe!
+public class P4KnowledgeGraphMutationListener implements MutationListener {
+
+    private Map<String, Long> m = new HashMap<>();
+
+    private Graph graph;
+
+    private P4KnowledgeGraphMutationListener(Graph graph) {
+        this.graph = graph;
+    }
+
+    @Override
+    public void vertexAdded(Vertex vertex) {
+        String label = vertex.label();
+        Long n = m.get(label);
+        if(n == null){
+            n = 0L;
+        }
+        graph.traversal().V(vertex).property("nodeId", n).iterate();
+        m.put(label, n+1);
+    }
+
+    @Override
+    public void vertexRemoved(Vertex vertex) {
+        // TODO Auto-generated method stub
+
+    }
+
+    @Override
+    public void vertexPropertyChanged(Vertex element, VertexProperty oldValue, Object setValue,
[…]

### 2021-03-30 broker/src/main/java/p4query/broker/App.java

@@ -1,0 +1,361 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.broker;
+
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.FileNotFoundException;
+import java.io.FileOutputStream;
+import java.io.IOException;
+import java.io.InputStream;
+import java.io.ObjectInputStream;
+import java.io.ObjectOutputStream;
+import java.lang.annotation.Annotation;
+import java.lang.reflect.Field;
+import java.lang.reflect.InvocationTargetException;
+import java.lang.reflect.Method;
+import java.nio.file.Files;
+import java.nio.file.Path;
+import java.nio.file.Paths;
+import java.nio.file.StandardCopyOption;
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.Collection;
+import java.util.HashMap;
+import java.util.Map;
+import java.util.Set;
+import java.util.stream.Collectors;
+
+import com.thoughtworks.xstream.XStream;
+
+import org.codejargon.feather.Feather;
+import org.codejargon.feather.Key;
+import org.reflections.Reflections;
+import org.reflections.scanners.MethodAnnotationsScanner;
+
+import p4query.ontology.IllegalUserInputException;
+import p4query.ontology.providers.AppUI;
+import p4query.ontology.providers.Application;
+
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+
+public class App {
+
+    // used for default includes and input file
+    public static final String CORE_P4_PATH = "core.p4";
+    public static final String V1MODEL_P4_PATH = "v1model.p4";
+    public static final String BASIC_P4_PATH = "basic.p4";
+
+    // used for implementation discovery
+    private static final String EXPERTS_PACKAGE = "p4query.experts";
[…]

### 2021-03-30 broker/src/test/java/p4query/applications/tests/TApp.java

@@ -1,0 +1,92 @@
+/**
+ * Copyright 2020, Eötvös Loránd University.
+ * All rights reserved.
+ */
+package p4query.applications.tests;
+
+import java.io.IOException;
+import java.lang.annotation.Annotation;
+import java.util.HashMap;
+import java.util.Map;
+import java.util.Set;
+import java.util.stream.Collectors;
+
+import javax.inject.Inject;
+import javax.inject.Provider;
+import javax.xml.transform.TransformerException;
+
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.reflections.Reflections;
+
+import p4query.ontology.providers.AppUI;
+import p4query.ontology.providers.Application;
+import p4query.ontology.providers.CLIArgs;
+import p4query.applications.visualisation.GraphUtils.Label;
+import p4query.ontology.Status;
+import p4query.ontology.analyses.AbstractSyntaxTree;
+import p4query.ontology.analyses.CallGraph;
+import p4query.ontology.analyses.CallSites;
+import p4query.ontology.analyses.ControlFlow;
+import p4query.ontology.analyses.SymbolTable;
+import p4query.ontology.analyses.SyntaxTree;
+
+
+public class TApp implements Application {
+
+    TCommand cmd = new TCommand();
+
+    @Inject                      private GraphTraversalSource g; 
+    @Inject @SyntaxTree          private Provider<Status> st;
+    @Inject @AbstractSyntaxTree  private Provider<Status> ast;
+    @Inject @SymbolTable         private Provider<Status> symtab;
+    @Inject @CallGraph           private Provider<Status> cg;
+    @Inject @ControlFlow         private Provider<Status> cfg;
+    @Inject @CallSites           private Provider<Status> cs;
+    @Inject @CLIArgs             private AppUI cli;
+
+    @Override
+    public TCommand getUI(){
+        return cmd;
+    }   
+    
+    public GraphTraversalSource getGraphTraversalSource() {
+        return g;
+    }
+
+    @Override
+    public Status run() throws IOException, TransformerException, InterruptedException {
+        Map<Class<? extends Annotation>, Provider<Status>> providers = new HashMap<>();
+        providers.put(SyntaxTree.class, st);
+        providers.put(AbstractSyntaxTree.class, ast);
+        providers.put(SymbolTable.class, symtab);
+        providers.put(CallGraph.class, cg);
+        providers.put(ControlFlow.class, cfg);
[…]

### 2021-03-30 broker/src/test/java/p4query/broker/tests/basicP4/BasicP4CallGraph.java

@@ -1,0 +1,89 @@
+/**
+ * Copyright 2020, Eötvös Loránd University.
+ * All rights reserved.
+ */
+package p4query.broker.tests.basicP4;
+
+import org.junit.Test;
+
+import static org.junit.Assert.assertEquals;
+
+import org.apache.tinkerpop.gremlin.groovy.jsr223.dsl.credential.__;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.junit.BeforeClass;
+import java.util.Arrays;
+import java.util.List;
+import p4query.broker.P4Resource;
+
+import p4query.ontology.Dom;
+
+public class BasicP4CallGraph {
+
+    private static String fileName = "src/main/resources/basic.p4";
+    private static List<String> analyses = Arrays.asList("CallGraph");
+    private static GraphTraversalSource g;
+
+    @BeforeClass
+    public static void preTest() {
+        P4Resource source = P4Resource.getP4Resource(fileName, analyses);
+        System.out.println("test1");
+        try {
+          g = source.getGraphTravSource();
+        } catch (Exception e) {
+          System.out.println(e.getMessage());
+        }
+    }
+    
+    @Test
+    public void testEdgeNumber() {
+        assertEquals(18, g.E().has(Dom.Call.ROLE, Dom.Call.Role.CALLS).count().next().intValue());
+    }
+
+    @Test
+    public void testTableCallActionNumber() {
+        assertEquals(3, g.V().has(Dom.Syn.V.CLASS , "TableDeclarationContext")
+                    .outE().has(Dom.Call.ROLE, Dom.Call.Role.CALLS)
+                    .inV().has(Dom.Syn.V.CLASS, "ActionDeclarationContext")
+                    .count().next().intValue());
+    }
+
+    @Test
+    public void testControlCallTableNumber() {
+        assertEquals(1, g.V().has(Dom.Syn.V.CLASS , "ControlDeclarationContext")
+                    .outE().has(Dom.Call.ROLE, Dom.Call.Role.CALLS)
+                    .inV().has(Dom.Syn.V.CLASS, "TableDeclarationContext")
+                    .count().next().intValue());
+    }
+
+    @Test
+    public void testParserEdgeNumber1() {
+        assertEquals(3, g.V().has(Dom.Syn.V.CLASS , "ParserDeclarationContext")
[…]

### 2021-03-30 broker/src/test/java/p4query/broker/tests/testP4/TP4CallGraph.java

@@ -1,0 +1,86 @@
+/**
+ * Copyright 2020, Eötvös Loránd University.
+ * All rights reserved.
+ */
+package p4query.broker.tests.testP4;
+
+import org.junit.Test;
+
+import static org.junit.Assert.assertEquals;
+
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.junit.BeforeClass;
+import java.util.Arrays;
+import java.util.List;
+import p4query.broker.P4Resource;
+
+import p4query.ontology.Dom;
+
+public class TP4CallGraph {
+
+    private static String fileName = "src/main/resources/test.p4";
+    private static List<String> analyses = Arrays.asList("CallGraph");
+    private static GraphTraversalSource g;
+
+    @BeforeClass
+    public static void preTest() {
+        P4Resource source = P4Resource.getP4Resource(fileName, analyses);
+        try {
+          g = source.getGraphTravSource();
+        } catch (Exception e) {
+          System.out.println(e.getMessage());
+        }    }
+    
+    @Test
+    public void testEdgeNumber() {
+        assertEquals(18, g.E().has(Dom.Call.ROLE, Dom.Call.Role.CALLS).count().next().intValue());
+    }
+
+    @Test
+    public void testTableCallActionNumber() {
+        assertEquals(4, g.V().has(Dom.Syn.V.CLASS , "TableDeclarationContext")
+                    .outE().has(Dom.Call.ROLE, Dom.Call.Role.CALLS)
+                    .inV().has(Dom.Syn.V.CLASS, "ActionDeclarationContext")
+                    .count().next().intValue());
+    }
+
+    @Test
+    public void testControlCallTableNumber() {
+        assertEquals(1, g.V().has(Dom.Syn.V.CLASS , "ControlDeclarationContext")
+                    .outE().has(Dom.Call.ROLE, Dom.Call.Role.CALLS)
+                    .inV().has(Dom.Syn.V.CLASS, "TableDeclarationContext")
+                    .count().next().intValue());
+    }
+
+    @Test
+    public void testParserEdgeNumber1() {
+        assertEquals(3, g.V().has(Dom.Syn.V.CLASS , "ParserDeclarationContext")
+                    .outE().has(Dom.Call.ROLE, Dom.Call.Role.CALLS)
+                    .inV().has(Dom.Syn.V.CLASS, "ParserStateContext")
[…]

### 2021-03-30 experts-call-graph/src/main/java/p4query/experts/callgraph/CallGraphGenerator.java

@@ -1,0 +1,125 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.experts.callgraph;
+
+import javax.inject.Singleton;
+
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
+import org.codejargon.feather.Provides;
+
+import p4query.ontology.Dom;
+import p4query.ontology.Status;
+import p4query.ontology.analyses.AbstractSyntaxTree;
+import p4query.ontology.analyses.CallGraph;
+import p4query.ontology.analyses.SymbolTable;
+import p4query.ontology.analyses.SyntaxTree;
+
+/**
+ * Hello world!
+ *
+ */
+public class CallGraphGenerator {
+
+    @Provides
+    @Singleton
+    @CallGraph
+    public Status analyse(GraphTraversalSource g, @SyntaxTree Status s, @AbstractSyntaxTree Status a, @SymbolTable Status t){
+        System.out.println(CallGraph.class.getSimpleName() +" started.");
+
+        whoCallsAction(g);
+        whoCallsTable(g);
+        whoCallsFunctionPrototype(g);
+        whoCallsParserState(g);
+        whoInvokesParsersAndControls(g);
+
+        System.out.println(CallGraph.class.getSimpleName() +" complete.");
+
+        return new Status();
+    }
+    public static void whoCallsTable(GraphTraversalSource g){
+            g.V().hasLabel(Dom.SYN).has(Dom.Syn.V.CLASS, "TableDeclarationContext").as("decl")
+                .flatMap(
[…]

### 2021-03-30 experts-control-flow/src/main/java/p4query/experts/controlflow/ControlFlowAnalysis.java

@@ -1,0 +1,345 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.experts.controlflow;
+
+import java.util.Collection;
+import java.util.Iterator;
+import java.util.List;
+import java.util.Map;
+
+import javax.inject.Singleton;
+
+import org.apache.tinkerpop.gremlin.process.traversal.Order;
+import org.apache.tinkerpop.gremlin.process.traversal.P;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
+import org.apache.tinkerpop.gremlin.structure.Vertex;
+import org.apache.tinkerpop.gremlin.util.function.Lambda;
+
+import p4query.ontology.Dom;
+import p4query.ontology.Status;
+
+import org.codejargon.feather.Provides;
+
+import p4query.ontology.analyses.AbstractSyntaxTree;
+import p4query.ontology.analyses.ControlFlow;
+import p4query.ontology.analyses.SymbolTable;
+import p4query.ontology.analyses.SyntaxTree;
+
+public class ControlFlowAnalysis {
+
+
+    // NOTE: parsers are not structured language elements, we don't add return edges between parser states
+    // NOTE: parser control flow is complicated, but it is because of the grammar
+    // TODO: test on 1-way conditionals
+        @Provides
+        @Singleton
+        @ControlFlow
+        public Status analyse(GraphTraversalSource g, 
+                            @SyntaxTree Status st, 
+                            @AbstractSyntaxTree Status ast, 
+                            @SymbolTable Status sym) {
+
+        // // query printing
[…]

### 2021-03-30 experts-control-flow/src/main/java/p4query/experts/controlflow/GremlinLatex.java

@@ -1,0 +1,426 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.experts.controlflow;
+
+// import java.util.List;
+// import java.util.Map;
+// import java.util.Map.Entry;
+// import java.util.function.Function;
+// import java.util.function.Supplier;
+// 
+// import javax.lang.model.util.ElementScanner6;
+// 
+// import org.apache.tinkerpop.gremlin.process.traversal.P;
+// import org.apache.tinkerpop.gremlin.process.traversal.Pop;
+// import org.apache.tinkerpop.gremlin.process.traversal.Step;
+// import org.apache.tinkerpop.gremlin.process.traversal.Traversal;
+// import org.apache.tinkerpop.gremlin.process.traversal.Traversal.Admin;
+// import org.apache.tinkerpop.gremlin.process.traversal.lambda.ElementValueTraversal;
+// import org.apache.tinkerpop.gremlin.process.traversal.lambda.TokenTraversal;
+// import org.apache.tinkerpop.gremlin.process.traversal.step.ComparatorHolder;
+// import org.apache.tinkerpop.gremlin.process.traversal.step.filter.HasStep;
+// import org.apache.tinkerpop.gremlin.process.traversal.step.filter.NoneStep;
+// import org.apache.tinkerpop.gremlin.process.traversal.step.filter.TailGlobalStep;
+// import org.apache.tinkerpop.gremlin.process.traversal.step.filter.WherePredicateStep;
+// import org.apache.tinkerpop.gremlin.process.traversal.step.filter.RangeGlobalStep.RangeBiOperator;
+// import org.apache.tinkerpop.gremlin.process.traversal.step.map.AddEdgeStep;
+// import org.apache.tinkerpop.gremlin.process.traversal.step.map.AddVertexStep;
+// import org.apache.tinkerpop.gremlin.process.traversal.step.map.CoalesceStep;
[…]

### 2021-03-30 experts-nr-task4/src/main/java/p4query/applications/Task4AppUI.java

@@ -1,0 +1,22 @@
+package p4query.applications;
+
+import com.beust.jcommander.Parameter;
+import com.beust.jcommander.Parameters;
+
+import p4query.ontology.providers.AppUI;
+
+@Parameters(commandDescription = "Launch task4")
+public class Task4AppUI extends AppUI {
+
+    @Override
+    public String getCommandName() { return "task4"; }
+
+    @Override
+    public String[] getCommandNameAliases() {
+        return new String[]{};
+    }
+
+    @Parameter(names = { "-st", "--syntax-tree" },
+               description = "Triggers syntax tree analysis") Boolean synTree;
+
+}

### 2021-03-30 experts-smc/src/main/java/p4query/applications/smc/hir/ProcedureDefinition.java

@@ -1,0 +1,154 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.applications.smc.hir;
+
+import java.util.Collections;
+import java.util.LinkedHashMap;
+import java.util.LinkedList;
+import java.util.List;
+import java.util.Map;
+
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
+import org.apache.tinkerpop.gremlin.structure.Vertex;
+
+import p4query.applications.smc.hir.iset.Instruction;
+import p4query.applications.smc.hir.typing.IRType;
+import p4query.applications.smc.hir.typing.LocalStruct;
+import p4query.applications.smc.lir.iset.Comment;
+import p4query.applications.smc.lir.iset.StackInstruction;
+import p4query.ontology.Dom;
+
+// TODO namespace
+public class ProcedureDefinition implements Definition {
+    private String name;
+    private String namespace;
+    private String origClass;
+    // private final LinkedHashMap<String, IRType> locals = new LinkedHashMap<>();
+    // // stored in input order
+    private final LocalStruct local = new LocalStruct(this);
+
+    private InstructionList body;
+    private GraphTraversalSource g;
+    private Vertex src;
+    private IRType.SingletonFactory typeFactory;
+    private InstructionLayout.Builder instLayout;
+
+    ProcedureDefinition(GraphTraversalSource g, Vertex src, IRType.SingletonFactory typeFactory) {
+        this.g = g;
+        this.src = src;
+        this.typeFactory = typeFactory;
+        this.origClass = (String) g.V(src).values("class").next();
[…]

### 2021-03-30 experts-smc/src/main/java/p4query/applications/smc/hir/exprs/Expression.java

@@ -1,0 +1,121 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.applications.smc.hir.exprs;
+
+import java.util.List;
+
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
+import org.apache.tinkerpop.gremlin.structure.Vertex;
+
+import p4query.applications.smc.hir.Definition;
+import p4query.applications.smc.hir.GlobalMemoryLayout;
+import p4query.applications.smc.hir.LocalMemoryLayout;
+import p4query.applications.smc.hir.typing.IRType;
+import p4query.applications.smc.lir.iset.StackInstruction;
+import p4query.ontology.Dom;
+
+public interface Expression {
+
+    public String toP4Syntax();
+
+    public StorageReference getStorageReference();
+
+    // compileToLIR is expected to push (or load) the value (or address) of the expression on the stack.  
+    public List<StackInstruction> compileToLIR(LocalMemoryLayout local, GlobalMemoryLayout global );
+    public int getSizeHint();
+
+    public static class Factory {
+        private Factory() {
+        }
+
+        public static Expression create(GraphTraversalSource g, Vertex v, IRType.SingletonFactory typeFactory, Definition parentDef, int sizeHint) {
+            if (g.V(v).outE(Dom.SYN).has(Dom.Syn.E.RULE, "expressionList").hasNext()) {
+                System.err.println("Warning: Expression lists are not implemented");
+                return null;
+            }
+
+            if (g.V(v).outE(Dom.SYN).has(Dom.Syn.E.RULE, "keysetExpression").hasNext()){
+                return new SelectKeyExpression(g, v, typeFactory, parentDef);
[…]

### 2021-03-30 experts-smc/src/main/java/p4query/applications/smc/hir/exprs/P4StorageReference.java

@@ -1,0 +1,187 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.applications.smc.hir.exprs;
+
+import java.util.Collections;
+import java.util.HashMap;
+import java.util.Iterator;
+import java.util.LinkedList;
+import java.util.List;
+import java.util.Map;
+import java.util.NoSuchElementException;
+
+import com.beust.jcommander.Strings;
+
+import org.apache.tinkerpop.gremlin.process.traversal.Order;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
+import org.apache.tinkerpop.gremlin.structure.Vertex;
+
+import p4query.applications.smc.hir.typing.Composite;
+import p4query.applications.smc.hir.typing.IRType;
+import p4query.ontology.Dom;
+
+public class P4StorageReference extends StorageReference {
+    private Vertex src;
+    private GraphTraversalSource g;
+    private LinkedList<String> fieldList = new LinkedList<>();
+    private Map<String, IRType> fieldTypes = new HashMap<>();
+    private IRType.SingletonFactory typeFactory;
+
+    P4StorageReference(GraphTraversalSource g, Vertex src, IRType.SingletonFactory typeFactory) {
+        this.g = g;
+        this.src = src;
+        this.typeFactory = typeFactory;
+
+        String typeType = (String) g.V(src).values(Dom.Syn.V.CLASS).next();
+
+        if(!(typeType.equals("LvalueContext") || typeType.equals("ExpressionContext")) )
+            throw new IllegalArgumentException(
+                String.format("Store reference cannot be initilized on %s vertex %s.", typeType, src));
+
+        fillFields();
+
+    }
+
+
+    @Override
[…]

### 2021-03-30 experts-smc/src/main/java/p4query/applications/smc/hir/exprs/SelectKeyExpression.java

@@ -1,0 +1,170 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.applications.smc.hir.exprs;
+
+import java.util.LinkedList;
+import java.util.List;
+import java.util.Map;
+import java.util.NoSuchElementException;
+
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
+import org.apache.tinkerpop.gremlin.structure.Vertex;
+
+import p4query.applications.smc.hir.Definition;
+import p4query.applications.smc.hir.GlobalMemoryLayout;
+import p4query.applications.smc.hir.LocalMemoryLayout;
+import p4query.applications.smc.hir.iset.SelectHead;
+import p4query.applications.smc.hir.typing.IRType;
+import p4query.applications.smc.hir.typing.IRType.SingletonFactory;
+import p4query.applications.smc.lir.iset.Comment;
+import p4query.applications.smc.lir.iset.Const;
+import p4query.applications.smc.lir.iset.IfEq;
+import p4query.applications.smc.lir.iset.Invoke;
+import p4query.applications.smc.lir.iset.Pop;
+import p4query.applications.smc.lir.iset.StackInstruction;
+import p4query.applications.smc.lir.typing.Size;
+import p4query.applications.smc.lir.typing.UnresolvedNameLabel;
+import p4query.applications.smc.lir.typing.UnresolvedVertexLabel;
+import p4query.ontology.Dom;
+
+public class SelectKeyExpression implements Expression {
+
+    private Vertex patternVert;
+    // TODO make this an enum
+    private String patternType;
+    private Definition procDef;
+    private SingletonFactory typeFactory;
+    private GraphTraversalSource g;
+    private Expression patternExpr;
+    private Expression headExpr;
[…]

### 2021-03-30 experts-smc/src/main/java/p4query/applications/smc/hir/externs/ReceivePacket.java

@@ -1,0 +1,71 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.applications.smc.hir.externs;
+
+import java.util.LinkedList;
+import java.util.List;
+
+import p4query.applications.smc.hir.GlobalMemoryLayout;
+import p4query.applications.smc.hir.InstructionLayout;
+import p4query.applications.smc.hir.InstructionLayout.Builder;
+import p4query.applications.smc.lir.iset.Comment;
+import p4query.applications.smc.lir.iset.Const;
+import p4query.applications.smc.lir.iset.Return;
+import p4query.applications.smc.lir.iset.StackInstruction;
+import p4query.applications.smc.lir.typing.Int;
+import p4query.applications.smc.lir.typing.LocalAddress;
+import p4query.applications.smc.lir.typing.Size;
+
+public class ReceivePacket extends ExternDefinition {
+
+    private Builder instLayout;
+
+    public ReceivePacket(InstructionLayout.Builder instLayout) {
+        super("receive_packet", null);
+        this.instLayout = instLayout;
+
+//        for (Object obj : names) {
+//            body.add(new Invoke(new UnresolvedNameLabel("", (String) obj, ""), new Size(0, "")));
+//        }
+    }
+
+
+    // TODO this will need a new unresolvedlabel, for jumping to instructions
+
+    @Override
+    public List<StackInstruction> compileToLIR(GlobalMemoryLayout global) {
+        LinkedList<StackInstruction> insts = new LinkedList<>();
+        insts.add(new Comment("define " + name + "()"));
+
+        insts.add(new Comment("TODO"));
+
+        // TODO delete this
+//        for (int i = 0; i < 1500; i++) {
+//            insts.add(new Const(new Int(10, "")));
+//            insts.add(new Pop());
+//        }
+
[…]

### 2021-03-30 experts-smc/src/main/java/p4query/applications/smc/hir/externs/Subtract.java

@@ -1,0 +1,65 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.applications.smc.hir.externs;
+
+import java.util.LinkedList;
+import java.util.List;
+
+import p4query.applications.smc.hir.GlobalMemoryLayout;
+import p4query.applications.smc.hir.InstructionLayout;
+import p4query.applications.smc.hir.InstructionLayout.Builder;
+import p4query.applications.smc.lir.iset.Comment;
+import p4query.applications.smc.lir.iset.Const;
+import p4query.applications.smc.lir.iset.Return;
+import p4query.applications.smc.lir.iset.StackInstruction;
+import p4query.applications.smc.lir.typing.Int;
+import p4query.applications.smc.lir.typing.LocalAddress;
+import p4query.applications.smc.lir.typing.Size;
+
+public class Subtract extends ExternDefinition {
+
+    private Builder instLayout;
+
+    public Subtract(InstructionLayout.Builder instLayout) {
+        super("subtract", null);
+        this.instLayout = instLayout;
+
+//        for (Object obj : names) {
+//            body.add(new Invoke(new UnresolvedNameLabel("", (String) obj, ""), new Size(0, "")));
+//        }
+    }
+
+
+    // TODO this will need a new unresolvedlabel, for jumping to instructions
+
+    @Override
+    public List<StackInstruction> compileToLIR(GlobalMemoryLayout global) {
+        LinkedList<StackInstruction> insts = new LinkedList<>();
+        insts.add(new Comment("define " + name + "()"));
+
+        insts.add(new Comment("TODO"));
+
+        insts.add(new Const(new Int(0, getName() + " terminates with status OK")));
+        insts.add(new Return(new LocalAddress(0, ""), new Size(1, "") ));
+        insts.add(new Comment(" "));
+        
[…]

### 2021-03-30 experts-smc/src/main/java/p4query/applications/smc/hir/externs/UpdateChecksum.java

@@ -1,0 +1,66 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.applications.smc.hir.externs;
+
+import java.util.LinkedList;
+import java.util.List;
+
+import p4query.applications.smc.hir.GlobalMemoryLayout;
+import p4query.applications.smc.hir.InstructionLayout;
+import p4query.applications.smc.hir.InstructionLayout.Builder;
+import p4query.applications.smc.lir.iset.Comment;
+import p4query.applications.smc.lir.iset.Const;
+import p4query.applications.smc.lir.iset.Return;
+import p4query.applications.smc.lir.iset.StackInstruction;
+import p4query.applications.smc.lir.typing.Int;
+import p4query.applications.smc.lir.typing.LocalAddress;
+import p4query.applications.smc.lir.typing.Size;
+
+public class UpdateChecksum extends ExternDefinition {
+
+    private Builder instLayout;
+
+    public UpdateChecksum(InstructionLayout.Builder instLayout) {
+        super("update_checksum", null);
+        this.instLayout = instLayout;
+
+//        for (Object obj : names) {
+//            body.add(new Invoke(new UnresolvedNameLabel("", (String) obj, ""), new Size(0, "")));
+//        }
+    }
+
+
+    // TODO this will need a new unresolvedlabel, for jumping to instructions
+
+    @Override
+    public List<StackInstruction> compileToLIR(GlobalMemoryLayout global) {
+        LinkedList<StackInstruction> insts = new LinkedList<>();
+        insts.add(new Comment("define " + name + "()"));
+
+        insts.add(new Comment("TODO"));
+
+        insts.add(new Const(new Int(0, getName() + " terminates with status OK")));
+        insts.add(new Return(new LocalAddress(0, ""), new Size(1, "") ));
+        insts.add(new Comment(" "));
[…]

### 2021-03-30 experts-smc/src/main/java/p4query/applications/smc/hir/iset/ConditionalHead.java

@@ -1,0 +1,76 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.applications.smc.hir.iset;
+
+import java.util.LinkedList;
+import java.util.List;
+
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.structure.Vertex;
+
+import p4query.applications.smc.hir.GlobalMemoryLayout;
+import p4query.applications.smc.hir.LocalMemoryLayout;
+import p4query.applications.smc.hir.ProcedureDefinition;
+import p4query.applications.smc.hir.exprs.CustomStorageReference;
+import p4query.applications.smc.hir.exprs.Expression;
+import p4query.applications.smc.hir.typing.IRType;
+import p4query.applications.smc.lir.iset.Comment;
+import p4query.applications.smc.lir.iset.IfEq;
+import p4query.applications.smc.lir.iset.StackInstruction;
+import p4query.applications.smc.lir.typing.UnresolvedVertexLabel;
+import p4query.ontology.Dom;
+
+public class ConditionalHead implements Instruction {
+
+    private CustomStorageReference boolStore;
+    private Expression head;
+    private Vertex src;
+
+    public ConditionalHead(GraphTraversalSource g, Vertex v, String vClass,
+			IRType.SingletonFactory typeFactory, ProcedureDefinition procDef) {
+
+        this.src = v;
+
+        Vertex cond = g.V(v).outE(Dom.SYN)
+                            .has(Dom.Syn.E.RULE, "expression").inV()
+                            .next();
+
+        this.head = Expression.Factory.create(g, cond, typeFactory, procDef, 1);
+
+//      no need for extra store, functions should just push the boolean on the stack
+//        IRType type = typeFactory.create("BOOLEAN", 1, head);
[…]

### 2021-03-30 experts-smc/src/main/java/p4query/applications/smc/hir/typing/GlobalStruct.java

@@ -1,0 +1,91 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.applications.smc.hir.typing;
+
+import java.util.LinkedHashMap;
+import java.util.List;
+import java.util.Map;
+
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
+import org.apache.tinkerpop.gremlin.structure.Vertex;
+
+import p4query.ontology.Dom;
+
+public class GlobalStruct implements Composite {
+
+    private final LinkedHashMap<String, IRType> fields = new LinkedHashMap<>(); // stored in input order
+    private final GraphTraversalSource g;
+    private final IRType.SingletonFactory typeFactory;
+    private final int size;
+
+    public GlobalStruct(GraphTraversalSource g, IRType.SingletonFactory factory) {
+        this.g = g;
+        this.typeFactory = factory;
+        fillFields();
+        this.size = calcSize();
+    }
+    
+    private void fillFields() {
+        List<Map<String, Object>> ms = 
+            g.V().has(Dom.Syn.V.CLASS, "ConstantDeclarationContext")
+                .project("name", "type")
+                .by(__.outE(Dom.SYMBOL)
+                    .has(Dom.Symbol.ROLE, Dom.Symbol.Role.DECLARES_NAME)
+                    .inV()
+                    .values("value"))
+                .by(__.outE(Dom.SYMBOL)
+                    .has(Dom.Symbol.ROLE, Dom.Symbol.Role.HAS_TYPE)
+                    .inV())
+                .toList();
+
+        for (Map<String,Object> m : ms) {
+            String name = (String) m.get("name");
+            Vertex type = (Vertex) m.get("type");
+
[…]

### 2021-03-30 experts-smc/src/main/java/p4query/applications/smc/lir/iset/ProbabilisticInstruction.java

@@ -1,0 +1,87 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.applications.smc.lir.iset;
+
+import java.util.LinkedHashMap;
+import java.util.LinkedList;
+import java.util.List;
+import java.util.Map;
+
+import org.apache.commons.lang.math.Fraction;
+
+// A probalistic instruction is a group of instructions that share the same label. 
+// When execution reaches that label, one of the instructions is randomly selected (according to the given distribution).
+// To handle groups of instructions, use probabilistic GOTOs.
+public class ProbabilisticInstruction implements StackInstruction {
+
+    private LinkedHashMap<StackInstruction, Fraction> probabilities = new LinkedHashMap<>();
+
+    private ProbabilisticInstruction() {
+    }
+
+    public static class Builder {
+        ProbabilisticInstruction pinst = new ProbabilisticInstruction();
+
+        public Builder() {
+
+        }
+
+        public void addInstruction(Fraction probability, StackInstruction inst) {
+            pinst.probabilities.put(inst, probability);
+        }
+
+        // TODO this should make a deep copy
+        public ProbabilisticInstruction build() {
+            Fraction sumProb = Fraction.ZERO;
+            for (Fraction p : pinst.probabilities.values()) {
+                sumProb = sumProb.add(p);
+            }
+            if(!sumProb.equals(Fraction.ONE)){
+                throw 
+                    new IllegalArgumentException(
+                        String.format(
+                            "Cannot build %s, the probabilitites don't sum up to 1. (sum(%s) == %s)",
+                            ProbabilisticInstruction.class,
+                            pinst.probabilities.values(),
+                            sumProb));
+            }
+            return pinst;
+        }
+    }
+
+    @Override
+    public String toHumanReadable() {
[…]

### 2021-03-30 experts-smc/src/main/java/p4query/applications/smc/lir/iset/Return.java

@@ -1,0 +1,41 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.applications.smc.lir.iset;
+
+import p4query.applications.smc.lir.typing.LocalAddress;
+import p4query.applications.smc.lir.typing.Size;
+
+public class Return implements StackInstruction {
+    private LocalAddress retVal;
+    private Size retValLen;
+
+    public Return(LocalAddress retVal, Size retValLen) {
+        this.retVal = retVal;
+        this.retValLen = retValLen;
+    }
+
+    @Override
+    public String toString() {
+        return "Return("+ retValLen + ")";
+    }
+
+    @Override
+    public String toHumanReadable() {
+        return "return "; 
+    }
+
+}

### 2021-03-30 experts-smc/src/main/java/p4query/applications/smc/lir/typing/UnresolvedInstructionLabel.java

@@ -1,0 +1,44 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.applications.smc.lir.typing;
+
+import p4query.applications.smc.lir.iset.StackInstruction;
+
+public class UnresolvedInstructionLabel extends Label {
+
+    private StackInstruction inst;
+
+    public UnresolvedInstructionLabel(StackInstruction inst, String comment) {
+        super(-1, comment);
+        this.inst = inst;
+    }
+
+    public StackInstruction getTarget(){
+        return inst;
+    }
+
+
+    @Override
+    public String toString() {
+        return String.format("UnresolvedInstructionLabel[%s, '%s']", inst, comment);
+    }
+    
+    @Override
+    public String toHumanReadable() {
+        return integer + ": unresolved label to " + comment;
+    }
+}

### 2021-03-30 experts-symbol-table/src/main/java/p4query/experts/symboltable/SymbolTableImpl.java

@@ -1,0 +1,759 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.experts.symboltable;
+
+import java.util.Collections;
+import java.util.HashMap;
+import java.util.Iterator;
+import java.util.LinkedList;
+import java.util.List;
+import java.util.Map;
+
+import javax.inject.Singleton;
+
+import org.apache.tinkerpop.gremlin.process.traversal.Order;
+import org.apache.tinkerpop.gremlin.process.traversal.P;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
+import org.apache.tinkerpop.gremlin.structure.Vertex;
+import org.apache.tinkerpop.gremlin.util.function.Lambda;
+import org.codejargon.feather.Provides;
+
+import p4query.ontology.Dom;
+import p4query.ontology.Status;
+import p4query.ontology.analyses.AbstractSyntaxTree;
+import p4query.ontology.analyses.SymbolTable;
+import p4query.ontology.analyses.SyntaxTree;
+
+
+// TODO this module should be rewritten, espec. w.r.t. the "fix" prefixed methods 
+public class SymbolTableImpl 
+{
+
+    // NOTE syntax maybe too permissive with expressions: (~ (13 >> true) . etherType) is a syntactically valid expression, even though '~', '>>', and '.' are reserved tokens. for this reason I decided to handle case-by-case
+
+    @Provides
+    @Singleton
+    @SymbolTable
+    public Status analyse(GraphTraversalSource g, @SyntaxTree Status s, @AbstractSyntaxTree Status a){
[…]

### 2021-03-30 experts-syntax-tree/src/main/java/p4query/experts/syntaxtree/TinkerGraphParseTree.java

@@ -1,0 +1,119 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.experts.syntaxtree;
+
+import java.util.HashMap;
+import java.util.Map;
+
+import org.antlr.v4.runtime.ParserRuleContext;
+import org.antlr.v4.runtime.Vocabulary;
+import org.antlr.v4.runtime.tree.ParseTree;
+import org.antlr.v4.runtime.tree.ParseTreeWalker;
+import org.antlr.v4.runtime.tree.TerminalNode;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.structure.Vertex;
+
+import p4query.experts.syntaxtree.p4.P4BaseListener;
+import p4query.ontology.Dom;
+
+public class TinkerGraphParseTree {
+    public static void fromParseTree(GraphTraversalSource g, ParseTree tree, Vocabulary vocab, String[] ruleNames) {
+//            g.getGraph().configuration().setProperty(Dom.Syn.V.NODE_ID, null);
+
+//            GraphCreatorVisitor v = new GraphCreatorVisitor();
+//            Element root = tree.accept(v);
+//            v.doc.appendChild(root);
+//            return v.doc;
+            new ParseTreeWalker().walk(new GraphCreatorListener(g, vocab, ruleNames), tree);
+    }
+
+    static class GraphCreatorListener extends P4BaseListener {
+        private GraphTraversalSource g;
+        private Map<ParseTree, Vertex> ids = new HashMap<>();
+        private Vocabulary vocab;
+        private String[] ruleNames;
+        public GraphCreatorListener(GraphTraversalSource g, Vocabulary vocab, String[] ruleNames) {
+            this.g = g;
+            this.vocab = vocab;
[…]

### 2021-03-30 experts-tz-task6/src/main/java/p4query/applications/TableData.java

@@ -1,0 +1,10 @@
+package p4query.applications;
+
+import java.util.List;
+import java.util.Map;
+
+public class TableData {
+    String TableName;
+    String LookUp;
+    Map<Long, List<String>> Keys;
+}

### 2021-03-30 experts-verification/src/main/java/p4query/experts/verification/pipeline_checking/PreCalculations.java

@@ -1,0 +1,307 @@
+/**
+ * Copyright 2020-2021, Eötvös Loránd University.
+ * All rights reserved.
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+package p4query.experts.verification.pipeline_checking;
+
+import p4query.ontology.Dom;
+
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.GraphTraversalSource;
+import org.apache.tinkerpop.gremlin.process.traversal.dsl.graph.__;
+
+import java.util.HashSet;
+import java.util.Map;
+import java.util.List;
+
+public class PreCalculations {
+
+    private static String headerStructInst = "hdr";
+    
+    public static void analyse (GraphTraversalSource g) {
+        setReadEdges(g);
+        setWriteEdges(g);
+        setTableKeys(g);
+        setMethodEdges(g);
+        addDirectApptoTable(g);    
+        addParserHeaderEdge(g);
+        setActionName(g);
+        setTableName(g);
+        headers(g);
+    }
+
+    private static void setReadEdges (GraphTraversalSource g) {
+        g.V().hasLabel(Dom.SYN)
+        .has(Dom.Syn.V.CLASS, "AssignmentOrMethodCallStatementContext")
+        .outE().has(Dom.Syn.E.RULE, "ASSIGN").outV().as("assignments")
+        .flatMap(__.outE().has(Dom.Syn.E.RULE, "expression").inV()
+        .until(__.has(Dom.Syn.V.CLASS, "ExpressionContext").outE(Dom.SYN).has(Dom.Syn.E.RULE, "DOT").outV())
+        .repeat(__.out(Dom.SYN))
+        .order().by("nodeId"))
[…]
